% =============================================================================
% Appendix A (More on Empirical Facts) + Appendix B (Proofs) stubs
% Insert with: \appendix \input{appendix_empirical} before \end{document} in model.tex.
% User will relocate proofs into Appendix B manually.
% =============================================================================

\appendix
\renewcommand{\thesection}{\Alph{section}}
\renewcommand{\thesubsection}{\Alph{section}.\arabic{subsection}}

\section{More on Empirical Facts} \label{app:more_empirical_facts}

\subsection{Data Sources} \label{app:data_sources}

\autoref{tab:data_sources} catalogues every dataset used in
Section~\ref{sec:empirical_facts}, together with the unit of observation,
coverage window, and retrieval date.

\subsection{Composite Ban-Intensity Index} \label{app:ban_intensity}

The composite ban intensity for state~$s$ in year $t$ is
\begin{equation*}
\text{BanIntensity}_{s,t}
\;=\;\sum_{b\in\mathcal{B}} \max\!\big(t-\tau_{s,b},\,0\big),
\end{equation*}
where $\mathcal{B}=\{\text{cow slaughter, bull slaughter, bullock slaughter,
buffalo slaughter, beef possession, beef sales}\}$ is the set of six ban
types and $\tau_{s,b}$ is the year in which state~$s$ first enacted a ban of
type~$b$. A state that never enacts ban~$b$ has $\tau_{s,b}=\infty$ and the
corresponding term is zero. The cumulative map uses the
1990--2020 annual average of this panel.

The underlying policy panel was constructed from state-level legislative
records compiled in the Cattle Slaughter Policy Excel file and maintained in
\texttt{policy\_clean.csv}. Because a handful of states --- Bihar, Chandigarh,
Punjab --- had early, near-contemporaneous adoption of multiple ban types
before~1990, their 1990--2020 average is bounded near the theoretical
maximum; the index compresses cross-state variation at the top end. Results
are qualitatively identical with a binary indicator or with a
count-of-ban-types-in-force metric; see \texttt{scripts/policy\_describe.py}.

\subsection{Narrative Classification Methodology} \label{app:narrative_classification}

\textbf{Corpus.} The majority-side corpus comprises three stacked sources
totalling $3{,}328$ rows: (i)~$2{,}066$ BJP-leadership speeches from
\texttt{bjp.org/speeches} ($2000$--$2025$), filtered to post-2014 dates for
the main-text figure; (ii)~$1{,}500$ Prime-Ministerial speeches harvested
from \texttt{pmindia.gov.in/en/news\_updates} (Nov~$2020$--Apr~$2026$), used
as a supplement during the pmindia fallback window (the primary target
\texttt{narendramodi.in} was unreachable); (iii)~$406$ BJP Lok Sabha floor
speeches and~$9$ AIMIM floor speeches harvested from the official DSpace
backend at \texttt{elibrary.sansad.in} ($1996$--$2024$), filtered to
single-speaker debate items with word-count $\geq 50$. The Lok Sabha
supplement fills the pre-$2014$ period in which the party-website archive
is sparse (fewer than~$35$ items $1996$--$2013$) and introduces
parliamentary-register content alongside the campaign-register bjp.org
corpus. AIMIM Lok Sabha speeches (Asaduddin~Owaisi, Imtiaz~Jaleel) are
assigned to the minority-side corpus. Speakers in the main corpus include
the Prime Minister and the four BJP National Presidents of the period; the
top seven speakers in the parliamentary supplement are Arun~Jaitley,
Sushma~Swaraj, Rajnath~Singh, Narendra~Modi, Nitin~Gadkari,
Asaduddin~Owaisi, and Amit~Shah. The minority-side corpus comprises
$3{,}792$ items ($3{,}783$~news-outlet snippets and~$9$~AIMIM Lok~Sabha
floor speeches) from a $65$-query Google News RSS harvest, $2010$--$2025$.
Queries cover AIMIM/Owaisi, Jamiat Ulama-i-Hind, AIMPLB, cow-related
lynchings (Akhlaq~2015, Pehlu~Khan~2017, Junaid~2017, Tabrez~2019), Shaheen
Bagh/CAA/NRC, hijab, Waqf, Uniform Civil Code, Gyanvapi, Babri~Masjid,
Bilkis~Bano, and Kashmir Muslim leadership. Outlets include The~Hindu, The
Times of India, NDTV, India~Today, Indian Express, Scroll, The~Wire,
Maktoob, SabrangIndia, Muslim Mirror, Al~Jazeera, and the BBC.

\textbf{Asymmetry in primary-source availability.} A primary-source Muslim
corpus analogous to \texttt{bjp.org/speeches} was not feasible: as of
April~2026, \texttt{aimim.in} fails to resolve; \texttt{jamiatulama.org}
resolves to a parked lander; \texttt{aimplboard.in} retains a static
early-2000s site whose press-release endpoint returns HTTP~500. The
minority-side corpus is therefore a curated press proxy rather than a
like-for-like speech archive. This asymmetry is documented in the main text
(\S\ref{subsec:d_narrative}) and treated as a data fact rather than a
nuisance.

\textbf{Classification.} Each text is classified by Claude Haiku~4.5
(\texttt{claude-haiku-4-5}) into one of four (majority) or five (minority)
mutually exclusive categories using a structured system prompt pinned to the
theoretical primitives. The full prompt, including category definitions and
disambiguation rules --- most importantly that a lynching story is
\textsc{identity\_contested} even when the victim's occupation is mentioned,
and that anti-Pakistan framing is \textsc{identity\_policy} only when
explicitly identity-laden and \textsc{security\_foreign} otherwise --- is
reproduced in \texttt{scripts/classify\_with\_haiku.py}. Majority categories
are \textsc{identity\_policy}, \textsc{economic\_provision},
\textsc{security\_foreign}, and \textsc{residual}; minority categories add
\textsc{counter\_mobilization} to capture collective-response content
distinct from threat-and-event content. Texts are truncated to the first
$500$ words to bound per-call input tokens; the pinned system prompt is
cached via Anthropic's ephemeral prompt cache so that each call pays cache-read
rates on the prompt and full rates only on the unique text. A keyword-lexicon
fallback is maintained in \texttt{scripts/build\_narrative\_timeseries.py}
for robustness; the lexicon overlaps the Haiku category boundaries on the
high-$d$ cases and diverges on polysemous tokens (e.g., ``conversion,''
``dharma,'' ``border'') on which Haiku is substantially sharper. On the
$2{,}330$ rows Haiku classified at the time of the main-text figure, the
category distributions are:
\begin{center}
\footnotesize
\begin{tabular}{lcc}
\toprule
Category & Majority & Minority \\
\midrule
Identity-coded / contested & $14.5\%$ & $63.3\%$ \\
Counter-mobilisation & --- & $22.8\%$ \\
Economic-programmatic & $33.7\%$ & $0.7\%$ \\
Security-and-foreign & $10.3\%$ & $2.7\%$ \\
Residual & $40.6\%$ & $10.7\%$ \\
Unparseable / error & $0.8\%$ & $0.0\%$ \\
\bottomrule
\end{tabular}
\end{center}

\textbf{Outputs and validation.} The per-text classification results are
preserved in \texttt{classified\_majority.csv} and
\texttt{classified\_minority.csv} for inspection. Aggregate monthly shares
underlying \autoref{fig:narrative_timeseries} are computed as the count of
rows in the numerator category divided by the total rows in the corpus that
month, with a six-month centred rolling mean applied for display and
monthly totals below two items set to missing. A validation audit against
$200$ hand-coded sample items is planned for the next revision.

\subsection{Minority Corpus Construction} \label{app:minority_corpus}

The $3{,}783$-item Muslim-voice proxy corpus is constructed from Google News
RSS feeds, one per query, retrieved at 1 request per second with a custom
user agent and cached locally. Queries span five categories: (i)~Muslim
political representation (Owaisi, AIMIM, MIM, Muslim MP, Muslim
chief~minister); (ii)~religious leadership (Jamiat Ulama-i-Hind, Deoband,
AIMPLB); (iii)~cow-related violence (Akhlaq, Pehlu Khan, Junaid, Tabrez,
cow~vigilante lynching, gau~rakshak); (iv)~legislative episodes (CAA,
NRC, NPR, triple talaq, hijab, waqf, UCC); (v)~locational flashpoints
(Shaheen~Bagh, Babri~Masjid, Gyanvapi, Bilkis~Bano, Kashmir). Each retrieved
item is deduplicated by URL, enriched with outlet name parsed from the RSS
source field, and stored with the item's title, description (first $\sim$30
words), publication date, and URL. The 2025 share of items is
disproportionately high ($31\%$) because of the Waqf Amendment and
freshness-weighted indexing in Google News RSS; the main-text figure
controls for this with monthly-share normalisation rather than raw counts.

\subsection{Intergenerational Welfare Consequences} \label{app:intergenerational}

The main text's focus on the contemporaneous Security Premium leaves open the
question of the durable welfare consequences of repeated symbolic-policy
shocks. In prior work on the same India beef-ban setting, I estimate a series
of generation-specific consequences using the IHDS-II micro-panel and an
intensity measure \textit{Un-Hinduism~$\times$~Ban} that interacts household
religious identity with exposure to the ban window. The results span three
generations and four domains: (i)~birth history and early-life growth
deficiency (induced abortion, premature death, infant Ponderal Index, minor
BMI); (ii)~short- and long-term poverty (absolute, relative, and subjective
cutoffs); (iii)~first-generation segregation and second-generation
discrimination (electoral and ethnic segregation, political acquaintance,
religious trust; school inaccessibility, teacher unfairness, communal
prejudice); (iv)~first-generation utility and protest (net income, life
satisfaction, demonstration and boycott participation). The full tables,
specifications, and robustness checks are preserved in
\texttt{empirical\_writing/PE\_of\_India/temp\_for\_discussion.tex} and will
be migrated into this appendix in a subsequent revision.

\subsection{Paradox-of-Competence Regression}\label{app:paradox_regression}

\autoref{fig:paradox_of_competence} reports a linear-probability model of
BJP retention at the next Assembly election on tenure-average annual count
of Hindu--Muslim violent events. The sample is every state-election pair in
which the BJP was the state government in the year prior to the election
($N=42$, fifteen states, $1984$--$2024$). GDELT Hindu--Muslim violent
events $1980$--$2024$ is the primary conflict series, with
Varshney--Wilkinson incidents as a pre-1995 supplement.

The primary specification regresses the retention indicator on
tenure-average annual event count, with state-clustered standard
errors. The coefficient is~$+0.0103$~(SE~$0.0042$, $p=0.015$): one
additional violent Hindu--Muslim event per tenure year raises the BJP
retention probability by approximately one percentage point. Quintile
means of the retention rate rise monotonically from~$33\%$ in the lowest
tenure-conflict quintile to~$78\%$ in the highest.

Robustness: the sign is stable and the magnitude broadly comparable under a
log-conflict specification ($p=0.063$), under the addition of decade fixed
effects ($p=0.089$), and under an average-marginal-effect logit
($p=0.11$). Splitting the sample at 2014 returns similar positive
coefficients in both the pre-2014 ($N=23$, $p=0.061$) and post-2014
($N=19$, $p=0.085$) subsamples, so the pattern is not a Modi-era
artefact. The effect operates at the retention margin rather than on a
smoother vote-share metric: the coefficient on the continuous BJP
vote-share change is right-signed but insignificant ($p=0.36$), consistent
with the seat-winning margin being the discretely-decided object.

The state-FE specification is not estimable with this sample size:
within-state outcome variation is thin in $10$ of the $15$ states and the
fixed-effects design absorbs much of the relevant variation mechanically.
The primary specification should therefore be read as combining
within-state and cross-state identification. Script:
\texttt{scripts/paradox\_of\_competence.py}.

\subsection{Ban-and-Conflict Event Studies} \label{app:event_studies}

A parallel line of analysis estimates the effect of each of the six
cattle-slaughter-ban types on Hindu-Muslim violence at the state-year level,
using staggered difference-in-differences with two-way fixed effects and
event-study leads and lags. The full set of event-study figures ---
$2~\text{timespans}\times2~\text{control specifications}\times
(6~\text{GDELT outcomes}+6~\text{VW outcomes})\times6~\text{policy types}$
--- is preserved at \texttt{PE\_of\_Cattle\_Shared/india\_beef\_and\_religion/
python\_results/figures/regression/event\_studies/} and replicated in Stata at
\texttt{stata\_results/figures/event\_studies/}. A selected four-panel
summary for the four ban types operating on the bovine family (cow, bull,
bullock, buffalo) is reported as~\autoref{fig:event_studies}.

\subsection{State-Level Population Panel} \label{app:population}

Annual state-level population 2000--2024 is interpolated from
Census~2001 and Census~2011 enumerations. The 2011 state shares of the
national total are carried forward annually by rescaling to the World Bank
\texttt{SP.POP.TOTL} India series. The resulting panel is stored at
\texttt{data/input/control/state\_population\_annual.csv} and is used to
normalize the Hindu--Muslim violence intensity in Map~B
(\autoref{fig:map_conflict_intensity}).

\subsection{Supplementary Maps} \label{app:supplementary_maps}

The six policy-specific maps (one per ban type) and the seven decade-specific
conflict maps are preserved in
\texttt{python\_results/figures/\{policy,conflict\_describe\}} and are
reproducible from \texttt{scripts/policy\_describe.py} and
\texttt{scripts/conflict\_describe.py} respectively. They are not reproduced
in this appendix.

\section{Proofs} \label{app:proofs}

\noindent \textit{[Proofs to be relocated here from
\autoref{sec:dynamic} and the static analysis sections. User will perform
the migration manually.]}

% End of Appendix.
