% =============================================================================
% Empirical Facts section for model.tex
% Insert with: \input{empirical_facts} between \section{Introduction} and
% \section{The Model}, i.e. around line 268 of model.tex.
% =============================================================================

\section{Empirical Facts} \label{sec:empirical_facts}

This section documents four empirical patterns that motivate the model
developed in the remainder of the paper. I first trace the rise of
identity-coded regulation in India's cow-slaughter legislation and the
parallel evolution of identity-coded political speech by majority and
minority actors (\S\ref{subsec:d_narrative}). I then characterise the long-run
political geography that these legislative and rhetorical patterns have
produced: some Indian states have become durably Hindu-nationalist, others
cycle between the BJP and non-BJP blocs, and a third set has remained
consistently non-BJP (\S\ref{subsec:cycles}). I place states in the
two-dimensional space of relative economic welfare and political dominance to
examine how symbolic-policy intensity correlates with each
(\S\ref{subsec:voter_space}). I close with three scope cases --- the United
States, Colombia, and Iran --- that illustrate the same pattern under
different institutional architectures (\S\ref{subsec:other_democracies}). The
full set of data sources, variable constructions, and supplementary results
is deferred to Appendix~\ref{app:more_empirical_facts}. All four
subsections are descriptive; the formal model in Section~\ref{sec:model}
offers an explanation of the joint pattern that readers can map back to
these facts.

\subsection{Rise of Identity-Coded Policy and Parallel Rhetoric}
\label{subsec:d_narrative}

Independent India inherited a constitutional encouragement of cow protection
(Article~48) but no national prohibition. For four post-independence decades
beef regulation was a state-level matter: Congress-governed states tolerated
buffalo and low-yield cattle slaughter and a handful of Jan Sangh- or
BJP-governed states pushed stricter enforcement. The legal landscape changed
discontinuously after the BJP's 2014 national victory. Between 2015 and
2017, a wave of state-level legislation extended bans from cows to the
entire bovine family, reversed the burden of proof, and raised maximum
penalties to ten years' imprisonment.\footnote{Maharashtra Animal
Preservation (Amendment) Act, 2015, and Haryana Gauvansh Sanrakshan Act,
2015, are the benchmark cases; analogous amendments followed in Gujarat,
Jharkhand, Uttar Pradesh, Madhya Pradesh, and Uttarakhand. A 2017 Ministry
of Environment notification sought to restrict cattle sales nationally but
was stayed by the Supreme Court before enforcement. Map~A in
\autoref{fig:maps} shows the resulting spatial concentration as of~2020.}
\autoref{fig:ban_adoption} plots the cumulative count of state-years under
each of the six cattle-slaughter bans and makes the post-2014 discontinuity
visible at a glance.

A natural question is whether the rise of identity-coded \emph{legislation}
was accompanied by a rise of identity-coded \emph{political speech}, both
from the governing party that enacted the bans and from the minority
community that bore their enforcement. I pursue this in two parallel
corpora. On the majority side I assemble $3{,}328$ BJP-leadership texts from
three archives: the party's official speech archive
(\href{https://www.bjp.org/speeches}{bjp.org/speeches}, 1996--2025), the
Prime Minister's office
(\href{https://www.pmindia.gov.in}{pmindia.gov.in}, 2020--2026), and BJP
Members' floor speeches in the Lok Sabha, harvested from
\href{https://elibrary.sansad.in}{elibrary.sansad.in}
(1996--2024).\footnote{Speakers include the Prime Minister, the four BJP
National Presidents of the period --- Amit~Shah, Rajnath~Singh, J.~P.~Nadda,
Narendra~Modi --- and senior front-benchers such as Arun~Jaitley,
Sushma~Swaraj, and Nitin~Gadkari. The Lok~Sabha supplement fills the
pre-2014 gap in the party website's online archive and captures
parliamentary, as distinct from campaign, register. Full speaker-level
counts are in Appendix~\ref{app:narrative_classification}.} On the minority
side the three major Muslim umbrella organisations do not operate crawlable
online speech archives, so I construct a proxy corpus of $3{,}792$ dated
items --- $3{,}783$~news-outlet snippets on Muslim political, legal, and
protest events plus nine AIMIM Lok~Sabha floor speeches --- from a
$65$-query harvest over 2010--2025.\footnote{As of April~$2026$,
\texttt{aimim.in} fails to resolve; \texttt{jamiatulama.org} resolves to a
parked lander; \texttt{aimplboard.in} retains a static early-2000s site
whose press-release endpoint returns HTTP~$500$. Owaisi's public speeches
persist on social-media platforms but are not catalogued with dates. The
asymmetry between majority-side archive density and minority-side
infrastructure is itself striking: it says that the majority party's
narrative supply is the margin that can be observed directly, while the
minority's has to be proxied through press coverage. Outlet composition and
the full query list are reported in Appendix~\ref{app:minority_corpus}.}
Each text is classified by Claude Haiku~4.5 into one of four (majority) or
five (minority) mutually exclusive categories, tracking whether the item is
identity-coded, economic-programmatic, security-and-foreign, a
counter-mobilisation or protest call (minority only), or residual. The
classification prompt and category definitions are in
Appendix~\ref{app:narrative_classification}.

\autoref{fig:narrative_timeseries} reports the monthly \emph{share} of
content that is identity-coded on the majority side and the share of
content that is counter-mobilisation on the minority side, smoothed over a
six-month centred window, over $2018$--$2025$.\footnote{Reporting shares
rather than counts means that neither series can be inflated by the simple
expedient of adding more speakers or outlets to the corpus: both
numerators are normalised by their own corpus-level totals in the same
month. On the minority side the news-proxy corpus is keyword-curated for
Muslim-identity topics, so its identity share is mechanically near one and
non-informative; I therefore use the narrower counter-mobilisation
category (roughly $23\%$ of the corpus, with genuine month-to-month
variation) as the minority signal. This choice is conservative: it picks
the minority category that fluctuates naturally rather than the
saturated one.} Two features stand out. First, the 2019--20 episode --- the
passage of the Citizenship (Amendment) Act in December 2019 and the
Shaheen Bagh protest movement that followed --- is the largest joint
spike in the sample: the majority identity share rose from near $5\%$ to
above $30\%$ and the minority counter-mobilisation share from near zero to
above $70\%$. Second, majority identity content appears to lead minority
counter-mobilisation: the cross-correlation peaks at a three-month lag
with $r = 0.55$.\footnote{Peak Pearson correlation of $0.55$ at a $+3$-month
lag (majority leading); the correlation at contemporaneous lag is $0.42$
and declines symmetrically to $\approx 0$ at~$\pm 6$ months. The sign and
direction are robust to varying the rolling window between three and nine
months.} The $2022$ hijab-ban cycle and the $2024$ Waqf~Bill are visible as
smaller secondary spikes in the same pattern. Pre-2019 activity on both
sides is low, which reflects both the lower visibility of identity-coded
legislation before the post-Modi wave and the sparsity of the speech
archive in those years.

\subsection{Cycles and Persistence in India's Political Competition}
\label{subsec:cycles}

Indian states differ sharply in the durability of BJP incumbency. Some,
like Gujarat, have seen uninterrupted BJP rule for three decades. Others,
like Himachal~Pradesh, Rajasthan, or Haryana, rotate between the BJP and
non-BJP blocs every one or two election cycles. A third set, concentrated
in the south and east, has remained consistently non-BJP across the entire
panel. This subsection maps the distribution of these patterns across the
$30$~major Indian states from $1984$ to $2024$ and documents that the
coexistence of persistence and turnover within the same federation is the
modal Indian pattern, not an aberration.

I construct a state-year panel of Vidhan Sabha (state legislative assembly)
outcomes by combining the Bhavnani India Election Dataset v2.0
(1977--2015) with supplementary records I compiled from the Election
Commission of India and Wikipedia for the $51$ Vidhan~Sabha elections and
the $2019$ and $2024$ Lok Sabha elections held in the
extension window. The panel is forward-filled between elections, so each
state-year is assigned the incumbent party of the preceding Assembly
result. I classify each state-year into one of three categories. A state-year
is \emph{BJP-dominant} if the BJP rules with either a seat-share majority
or a vote-share margin of at least~$10$~percentage points;
\emph{non-BJP-dominant} if a non-BJP party rules with a margin of at
least~$10$~percentage points; and \emph{competitive} otherwise.

\autoref{fig:cycles_four_panel} presents four panels derived from the panel.
Panel~(A) plots the national BJP vote and seat shares in Lok Sabha elections
from~1984 to~2024; two step increases stand out, the 1999--2004 NDA years
and the post-2014 Modi wave, with a peak of~$55.8\%$ of seats in~2019 on a
$37.4\%$ vote share. Panel~(B) plots the fraction of state Assemblies
governed by the BJP across time; the share rises from near-zero before~1990
to~$0.55$ after~2017. Panel~(C) plots the distribution of uninterrupted
incumbency tenure at the state level by party group. The BJP distribution
carries a pronounced right tail, with five spells of at least~$11$
consecutive years.\footnote{Gujarat~1995--2024 (30~years),
Madhya~Pradesh~2003--2018 (15~years), Chhattisgarh~2003--2018 (15~years),
Haryana~2014--2024 (11~years), and Uttar~Pradesh~1991--2001 (11~years). The
INC and regional-party tenure distributions are centred on shorter spells.}
Panel~(D) plots the state-year regime heatmap, which reveals three spatial
patterns: a Hindi-Belt cluster of long BJP-dominant spells, a southern and
eastern cluster of persistent non-BJP dominance, and an intermediate
cluster of states that alternate between categories.\footnote{The Hindi
Belt cluster --- Uttar~Pradesh, Madhya~Pradesh, Rajasthan, Chhattisgarh,
Gujarat, Haryana, and Jharkhand --- shows few transitions. The southern and
eastern cluster --- Tamil~Nadu, Kerala, West~Bengal, Andhra~Pradesh,
Telangana --- is non-BJP throughout the panel. The alternating cluster is
led by Himachal~Pradesh (seven regime transitions), Rajasthan~(6),
Haryana~(5), and Karnataka~(4). The three patterns are distinct enough to
suggest that the same institutional environment can sustain very different
political trajectories.}

The coexistence of long BJP spells and intermediate-state alternation within
the same federal system is noteworthy on its own. Gujarat's
uninterrupted thirty-year BJP incumbency spans the $2002$ communal
violence, three Lok Sabha electoral cycles, and at least one episode of
sharp economic contraction; Himachal~Pradesh has turned over seven times
over the same window. That these paths coexist inside one federation means
that any explanation of one pattern has to be consistent with the other as
a corollary of the same mechanism operating under different local
parameters. The model of Section~\ref{sec:model} is designed to deliver
exactly this feature: the same primitives can generate durable incumbency
or recurrent alternation depending on voter time-horizons, the strength of
moderate-voter pushback, and the incumbent's relative organisational
capacity.

\textbf{A second pattern: incumbency tracks conflict.} A surprising feature of
Indian state politics is that BJP state governments are \emph{more} likely
to survive re-election when they preside over high Hindu--Muslim conflict.
\autoref{fig:paradox_of_competence} plots the BJP retention rate at the
next Assembly election against the average intensity of Hindu--Muslim
conflict during the incumbent's tenure, for the $42$ state-election pairs
in which the BJP was the incumbent going into the contest, $1984$--$2024$.
Retention rises monotonically across tenure-conflict quintiles, from
$33\%$ in the lowest quintile to $78\%$ in the highest; a linear
probability model gives a positive slope significant at the $5\%$
level.\footnote{Sample: every (state, election-year) pair in which the BJP
was the state-government party in the year prior to the election; $N=42$
defense elections across $15$ states, $1984$--$2024$. Primary
specification: LPM of an indicator for the BJP retaining power at the
election on tenure-average annual count of violent Hindu--Muslim events
(GDELT, with Varshney--Wilkinson as pre-1995 supplement), no controls,
state-clustered standard errors. Coefficient~$+0.0103$ per event/year
(SE~$0.0042$, $p=0.015$). The pattern is robust to a log specification
($p=0.063$), to adding decade fixed effects ($p=0.089$), and to a pre-2014
subsample ($N=23$, $p=0.061$); the effect is therefore not driven by the
Modi-era subsample. The effect operates on the retention margin rather than
on the continuous vote share: the coefficient on vote-share change is
right-signed but insignificant ($p=0.36$), consistent with the
seat-winning margin being the discretely-decided object.} The direction
runs opposite to a naive retrospective-voting story in which better
economic and security outcomes help the incumbent: here, \emph{more}
realised disorder under the BJP correlates with \emph{higher} retention,
not with punishment. Section~\ref{sec:model} provides one candidate
explanation for this pattern, and the paradox re-enters as a corollary of
the dynamic extension in Section~\ref{sec:dynamic}.

\subsection{Welfare, Political Dominance, and Symbolic Policy}
\label{subsec:voter_space}

The subsections so far have documented a rise in identity-coded policy and
rhetoric and a cross-state pattern of BJP entrenchment versus alternation.
A natural next question is whether these two patterns are empirically
linked at the state level --- that is, whether states with heavier
symbolic-policy use are the same states in which political dominance has
decoupled from economic performance. I examine this by placing states in the
two-dimensional space defined by (i)~relative economic welfare and
(ii)~political dominance of the BJP, and overlaying the intensity of
cumulative cattle-slaughter regulation.

\textbf{Measurement.} I proxy relative welfare by each state's share of
national GDP divided by its share of national population, yielding a
measure of state GDP per capita relative to the national average ($1.0$
denotes the national average in the year). Series is taken from the Reserve
Bank of India's state-GDP-share tables at $1990$, $2000$, $2010$, $2020$
and~$2023$ anchor years, combined with the Census-interpolated population
panel of Appendix~\ref{app:population}. I proxy political dominance by the
BJP's Vidhan Sabha seat share in the state-year, computed from the
election panel of \S\ref{subsec:cycles}. Composite ban intensity is the
state-level index of \S\ref{subsec:d_narrative} carried forward
through~$2020$; its construction is in Appendix~\ref{app:ban_intensity}.

\textbf{Three-map cross-section.} \autoref{fig:maps} visualises the
cross-sectional co-location of the three objects. Map~A plots composite ban
intensity as of~2020; it concentrates on the northern and western states.
Map~B plots Hindu--Muslim violence intensity per capita, pooling
Varshney--Wilkinson and GDELT Hindu--Muslim events, normalised by state
population.\footnote{State population is interpolated annually from
Census~2011 shares rescaled by the World~Bank national-population series;
Appendix~\ref{app:population}.} Map~C plots the change in BJP state-Assembly
vote share between the 2009-anchor and the 2019-anchor Vidhan Sabha
elections. The three maps co-locate along the Hindi Belt and Gujarat: states
with early and broad ban adoption also carry the legacy of Hindu--Muslim
violence and registered the largest post-2014 BJP vote-share gains. Appendix~\ref{app:supplementary_maps} reports the six policy-type-specific maps and a decade-resolution conflict map.

\textbf{The welfare-dominance cloud.}
\autoref{fig:voter_space_2d} places the $15$~largest Indian states in the
welfare-dominance plane at two snapshots, $2000$ and $2020$, with point
size rendering composite ban intensity as of~$2020$.\footnote{The plotted
states are Andhra~Pradesh, Assam, Bihar, Gujarat, Haryana, Karnataka,
Kerala, Madhya~Pradesh, Maharashtra, Odisha, Punjab, Rajasthan, Tamil~Nadu,
Uttar~Pradesh, and West~Bengal. Small states and union territories
(Chandigarh, Delhi, Goa, the northeast states except Assam) are excluded
because their very small populations or special administrative status push
their per-capita welfare far out in the right tail and make visual
comparison noisier without adding substantive information.} Two features
are visible from the panel pair alone. First, the $2000$ cloud is compact
in the lower half of the vertical axis: almost no state had a BJP seat
share above $50\%$, and the handful of states with early ban adoption
(Gujarat, Madhya~Pradesh) sit in the upper-middle of the welfare
distribution. Second, the $2020$ cloud expands vertically, with Gujarat
and Uttar~Pradesh pushing the BJP seat share above $70$--$80\%$ while the
underlying welfare position of high-ban states drifts toward the middle
of the distribution. Low-ban states (southern and eastern India) remain
close to zero on the dominance axis throughout the panel, consistent with
the fact that symbolic policy is an instrument that is used, not one that
is accidentally switched on. The pattern says that high-ban states stayed
politically dominant even as their relative welfare moved downward, while
low-ban states did not see a comparable consolidation.

\textbf{The electoral return to conflict is bounded.}
\autoref{fig:security_premium_empirical} shifts to a different state-level
cut: right-wing (BJP and allied NDA parties) vote share in Indian state
Assembly elections against the percentile rank of within-state
Hindu--Muslim conflict intensity in the pre-election window. The shape is
inverted-U: vote share rises over the low-to-moderate range of conflict
and flattens --- and slightly declines --- at the highest conflict levels.
The pattern cuts against the simple reading that conflict always helps
the hawkish party; rather, the electoral return to observed disorder
appears to be disciplined by a ceiling.

\textbf{Bans raise conflict.} A separate empirical question is what
happens to Hindu--Muslim violence after a state adopts a slaughter ban.
\autoref{fig:rent_dissipation_event_study} reports a staggered
difference-in-differences event study of log Hindu--Muslim violent events
on leads and lags of state-level cow-slaughter-ban adoption. Pre-adoption
leads are flat; post-adoption lags are positive and persistent for several
years. Symbolic policy and communal violence therefore move together on
impact, in the direction that the legislation appears to cause (or at
minimum accompany) an increase in observable conflict rather than to
suppress it.

\textbf{Durable welfare costs to affected households.} The contemporaneous
rise in conflict carries longer-run consequences for the households whose
identity is the target of the legislation. Using the India Human
Development Survey (Wave~II, IHDS-II), \autoref{tab:birth_history}
estimates whether Muslim households in state-cohorts exposed to the violent
aftermath of a cow-slaughter ban experience worse birth outcomes and
early-life growth. The interaction between the non-Hindu household
indicator and ban exposure carries statistically significant coefficients
on neonatal and under-eight mortality (columns 3--4) and on the Ponderal
Index of surviving infants (column~5). \autoref{tab:economic} extends the
same design to short- and long-term household poverty measures and finds
persistent, if modest, long-run reductions in relative
welfare.\footnote{The intensity measure in
\autoref{tab:birth_history} interacts the non-Hindu household indicator
with an exposure window defined as the overlap between the respondent's
(or child's) formative years and the eight years following a state's first
ban enactment; \autoref{tab:economic} uses a parallel household-level
intensity variable. The two tables are replicated from earlier
author-generated empirical work; construction details, variable definitions,
and robustness exercises are in Appendix~\ref{app:intergenerational}.} The
direction of the estimates matches the empirical claim that identity-coded
legislation imposes real welfare costs on the targeted minority that do not
dissipate within a single electoral cycle.

\subsection{Three Scope Cases: the United States, Colombia, and Iran}
\label{subsec:other_democracies}

The India-centric analysis of the previous subsections is not the only
place where the joint pattern of identity-coded policy, minority
counter-mobilisation, and persistent incumbency appears. Three further
cases illustrate the same configuration under different institutional
architectures.

\emph{The United States, post-2015.} The Republican Party's post-2015 turn
to immigration enforcement and culturally coded domestic security is a
sequence of identity-marked policies --- the entry restrictions under
Executive Order~13769, border-wall construction, family separations at the
Southern border, and the federalisation of culture-war education policy
--- enacted against a Democratic Party whose comparative advantage is in
universalist economic provision.\footnote{Democratic programmatic platform:
Affordable Care Act (2010), American Rescue Plan (2021), Inflation Reduction
Act (2022). Republican symbolic-policy platform: Executive Order~13769
restricting entry from Muslim-majority countries (2017); border-wall
construction and the family-separation policy at the Southern border
(2018); state-level prohibitions on ``critical race theory'' and
transgender rights (2021--24).} The 2018 midterms, held immediately after
the family-separation episode, returned a Democratic House majority ---
consistent with the inverted-U pattern of
\autoref{fig:security_premium_empirical}, in which the moderate-voter
backlash eventually outruns the identity-based consolidation. The 2016,
2020, and 2024 presidential alternations place the US closer to the
cyclical Indian states than to Gujarat's long durable incumbency, and the
difference plausibly tracks the absence, in the US, of the
candidacy-gatekeeping that stabilises hawkish incumbency in Iran (below).

\emph{Colombia, the 2016 peace plebiscite.} Colombia's post-2002 Uribista
period is a case in which the out-group that sustains identity-coded
politics is an ideologically coded armed organisation (the FARC) rather
than an ethnic or religious domestic minority. The \emph{Democratic
Security} doctrine of Álvaro Uribe (2002--2010) and its continuation in
the Centro Democrático after~2014 promised visible coercive capacity
against FARC, imposed fiscal costs, and activated a visibly two-sided
contest in which paramilitary mobilisation rose alongside state
enforcement. The 2016 plebiscite on the Santos--FARC peace accord is a
striking negative case: when the non-hawkish side attempted to move the
country to a post-conflict political settlement, the \textsc{No} campaign,
led by the Uribista bloc, narrowly blocked ratification. That the
successor administration subsequently implemented substantial portions of
the same accord suggests the binding constraint was electoral rather than
substantive.

\emph{Iran, morality policing and the 2022 Amini episode.} Iran's hybrid
regime holds competitive elections within a system that filters candidates
through the Guardian Council.\footnote{The hard-line bloc is anchored in
the Islamic Revolutionary Guard Corps and its paramilitary extension, the
Basij. Reformist-pragmatist administrations under Khatami (1997--2005) and
Rouhani (2013--21) opened brief economic windows but did not shift the
morality-policy margin.} The hard-line bloc's most visible symbolic
instrument is the regulation of women's public conduct --- compulsory
hijab, the \emph{gasht-e ershad} morality police, and periodic ``bad
hijab'' campaigns. The Mahsa Amini episode of September~2022 and the
\emph{Woman, Life, Freedom} protests were an acute, visibly two-sided
confrontation whose subsequent re-intensification of morality-police
enforcement closed the brief opening. Iran is the case in which the
persistence of hawkish incumbency is underwritten not by voter preferences
over continuity but by the institutional filter on candidacies, which
arguably plays the same role that deep voter commitment to security
capacity plays in the Hindi~Belt.

Together, the three cases make it less likely that the Indian pattern is a
country-specific artefact, and they previsage the three scope conditions
under which the mechanism should be expected to operate: a standing
identity-coded policy instrument, a two-sided response triggered by its
use, and an institutional environment in which the electoral (or
quasi-electoral) discipline on moderate-voter backlash is the relevant
binding constraint.

% End of \section{Empirical Facts}
