\documentclass[11pt,twoside]{extarticle}
\usepackage{floatrow}   
\usepackage{etex}
%\reserveinserts{18}
\usepackage[english]{babel}
\usepackage{url} % break the too-long url
\def\UrlBreaks{\do\/\do-}
\usepackage[breaklinks]{hyperref}
\usepackage{comment}
 
\usepackage[figuresright]{rotating}
%\newcommand*{\Appendixautorefname}{Appendix} % allowing autoref to show "Appendix"
%\usepackage{xr}  % cross reference
%\externaldocument{Appendix}
\usepackage[margin=1.2in]{geometry}  % margin
\usepackage{setspace}  % single or double spacing
\renewcommand{\baselinestretch}{1.3}
\usepackage{booktabs, multicol}   % \toprule[1.25pt] in Table//.
\usepackage{threeparttable}   % add Table notes
%\usepackage{lscape}
\usepackage{pdflscape}
\usepackage{xcolor}
\usepackage{amstext}
\usepackage{pgfplots}
\usepackage{color}
\usepackage{soul}
\usetikzlibrary{shapes,positioning,matrix,calc,shapes,shapes.multipart,shapes.misc,arrows,chains,fit,plotmarks}
\usetikzlibrary{decorations.text}
%\pgfplotsset{width=23cm,height = 18cm, compat=1.10}

\usepackage{eurosym}
\usepackage{amssymb}
\usepackage{amsfonts}

\usepackage{afterpage}
%Avoid horizontal figure to generate a blank page

\usepackage{epsfig}
\usepackage{upgreek}
\usepackage{commath}
\usepackage{enumitem}
\usepackage{subfigure}
\usepackage{indentfirst}
\usepackage{xr}  
\usepackage{dsfont}
\usepackage{cleveref}
\usepackage{titlesec}
\usepackage{titling}
\usepackage{multibib}
\usepackage{makecell}
\usepackage{soul}
\usepackage{arydshln}
\usepackage{mathrsfs}
\usepackage{ragged2e}
\newcites{online}{References} %% online appendix
% \usepackage{amsfonts}
\allowdisplaybreaks % pagebreak aligned equations

\usepackage[normalem]{ulem} % to highlight changes between versions

\setcounter{MaxMatrixCols}{10}
%TCIDATA{OutputFilter=LATEX.DLL}
%TCIDATA{Version=5.50.0.2953}
%TCIDATA{Codepage=932}
%TCIDATA{<META NAME="SaveForMode" CONTENT="1">}
%TCIDATA{BibliographyScheme=Manual}
%TCIDATA{LastRevised=Saturday, October 22, 2016 13:04:05}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
%TCIDATA{Language=American English}
%TCIDATA{CSTFile=LaTeX article (bright).cst}

\newtheorem{theorem}{Theorem}
\newtheorem{acknowledgement}{Acknowledgement}
\newtheorem{algorithm}{Algorithm}
\newtheorem{assumption}{Assumption}
\newtheorem{axiom}{Axiom}
\newtheorem{case}{Case}
\newtheorem{claim}{Claim}
\newtheorem{conclusion}{Conclusion}
\newtheorem{condition}{Condition}
\newtheorem{conjecture}{Conjecture}
\newtheorem{corollary}{Corollary}
\newtheorem{criterion}{Criterion}
\newtheorem{definition}{Definition}
\newtheorem{example}{Example}
\newtheorem{observation}{Observation}
\newtheorem{exercise}{Exercise}
\newtheorem{lemma}{Lemma}
\newtheorem{notation}{Notation}
\newtheorem{problem}{Problem}
\newtheorem{proposition}{Proposition}
\newtheorem{remark}{Remark}
\newtheorem{solution}{Solution}
\newtheorem{summary}{Summary}
\providecommand*{\theoremautorefname}{Theorem}
\providecommand*{\lemmaautorefname}{Lemma}
\providecommand*{\propositionautorefname}{Proposition}
\providecommand*{\corollaryautorefname}{Corollary}
\providecommand*{\definitionautorefname}{Definition}
\providecommand*{\remarkautorefname}{Remark}
\providecommand*{\subfigureautorefname}{Subfigure}
\providecommand*{\algorithmautorefname}{Algorithm}
\providecommand*{\assumptionautorefname}{Assumption}
\newenvironment{proof}[1][Proof]{\noindent \textbf{#1.} }{\ \rule{0.5em}{0.5em}}
\geometry{left=1.2in,right=1.2in,top=1.3in,bottom=1.3in}
\renewcommand{\baselinestretch}{1.3}
\newcommand{\newln}{\\&\quad\quad{}}
\newcommand{\parenthnewln}{\right.\\&\left.\quad\quad{}}
% \newcommand{\cn}[1]{\citet*{#1}}
% \newcommand{\cnp}[1]{(\citealt{#1})}  % (Jones 2002)
\usepackage{bbm}

\usepackage{longtable}
\usepackage[para]{threeparttablex} % for "ThreePartTable" environment

\usepackage{float}
\usepackage[titletoc,title]{appendix} % enable appendix environment
\raggedbottom % better manage spaces between paragraphs

\usepackage{amsmath}
\usepackage{bm}
\usepackage{lineno} % add line number to pdf

\usepackage[T1]{fontenc}
\usepackage{palatino}

\usepackage{graphicx}

\hypersetup{
   colorlinks=true,linkcolor=blue,citecolor=blue, filecolor=magenta, citebordercolor=yellow,
   linkbordercolor = magenta
}

\usepackage{graphicx}
\graphicspath{{../output/figures/}}
\usepackage{subfigure}
\floatsetup[figure]{font=footnotesize}

\floatsetup[table]{capposition=top} % Table title at the top
\floatsetup[table]{font=footnotesize}

\floatsetup{style=plain,footposition=bottom}
\floatsetup[figure]{capposition=bottom}

\usepackage{multirow} % multiple lines per cell
\newcommand{\specialcell}[2][c]{% \specialcell[t]{} % aligned with top rule
        \begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}

\makeatletter
\renewcommand\@makefntext[1]{% footnoot 1. style
    \parindent 1em%
    \@thefnmark.~#1$\qquad$}
\makeatother

\usepackage{tabularx}
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}
\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\newcolumntype{C}{>{\centering\arraybackslash}X}

\usepackage[figuresright]{rotating}

% caption styling
\usepackage[font=normalsize,format=plain,labelfont=bf,up,textfont=up,justification=centering]{caption}
\captionsetup[table]{labelsep=space}   % no : in caption
\captionsetup[figure]{labelsep=space}
\addto\captionsenglish{%
\renewcommand{\figurename}{FIGURE}
\renewcommand{\tablename}{TABLE}}
\renewcommand{\thesubfigure}{(\Alph{subfigure})} 

\usepackage{natbib} % references author-year display
\newcommand{\cites}[1]{\citeauthor{#1}'s (\citeyear{#1})} % author's (2010) style

\usepackage{pdflscape} % \begin{landscape}
\newcommand{\jw}[1]{\textcolor{cyan}{[JW: #1]}}
\newcommand{\yy}[1]{\textcolor{orange}{[YY: #1]}}
\newcommand{\zz}[1]{\textcolor{red}{[ZZ: #1]}}

\usepackage[titletoc]{appendix}
\usepackage{titletoc}

\title{Manufacturing Enemies in Political Contests}
\author{Haotian (George) Bai\thanks{I thank to conference/seminar participants at Oxford. I extend special thank to Prof. Jean-Paul Carvalho (Oxford).}}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}
Why do political groups enact identity-related policies (i.e., symbolic policies) against out-groups in political contests? I model symbolic policy as an instrument that activates a dormant two-sided security contest between a majority and a domestic minority. By manufacturing a visible threat, a security-advantaged \emph{hawkish} party relaxes majority free-riding in decentralized enforcement, makes its state-capacity advantage electorally salient, and substitutes identity politics for economic competence.
The minority's response to symbolic policy accumulates into a slow-decaying mobilisation stock that shapes future contest stakes, so the same primitive generates two long-run regimes. With forward-looking voters, conflict produces a self-sustaining trap in which the hawk can survive through severe economic shocks. With myopic retrospective voters, the mechanism generates recurrent regime cycles, whereby successful suppression of disorder raises the hawk's risk of turnover. These theoretical predictions are distinct from Barro-Ferejohn models. Evidence from India's cattle-slaughter legislation, along with cases on the United States, Colombia, and Iran, is consistent with each prediction.

\emph{JEL Codes: D72, D74, P16, Z18}.

\end{abstract}
\clearpage

\begin{quote}
\textit{``Only one thing is worse than communal war --- and that is when your government exploits communal differences, stokes ethnic and religious fears, all in the pursuit of power.''}

\hfill --- A. Sivanandan, \textit{``Ethnic Cleansing in Sri Lanka''}
\end{quote}

\section{Introduction}

% Paragraph 1 — Opening: the phenomenon

There has been a widespread rise in identity-coded policies (symbolic policies) targeting domestic minority groups in electoral democracies. By symbolic policies, I mean deliberate control over cultural, religious, and ethnic identities on minority groups. These policies include restrictions on diet, dress, marriage, or language regulations, chosen by an elected majority party and directed at a visible domestic out-group. In the last decade, legislative waves in major Indian states have criminalised cow-slaughtering with penalties of up to ten years' imprisonment.\footnote{The cumulative state-by-state rollout of all six ban types is shown in \autoref{fig:policy_cumulative_rollout}, with the year-by-year coverage tabulated in Appendix~\autoref{tab:policy_timing}. Following \citet*{dasguptaNutritionalCostBeef2023}, I tracked policy-enactment dates across state legislative records.} Between 2012-2018, over forty cow-related deaths were documented, whose victims were mostly Muslim.\footnote{\href{https://www.hrw.org/report/2019/02/19/violent-cow-protection-india/vigilante-groups-attack-minorities}{Human Rights Watch (2019), last access Apr 17\textsuperscript{th}, 2026}.} The pattern has been repeated across electoral democracies, from the post-2016 anti-immigration turn in the United States, to the Uribista policies under Álvaro Uribe Vélez. Such polices are also seen in non-democracies with political competition.\footnote{Iranian principalists deploy hijab enforcement and morality-policing campaigns to combat economics reformists when they gain popularity \citep*{bajoghliIranReframedAnxieties2020}. Chinese Communist Party (CCP) has divergent policies on ethnic groups as Politburo faction shifts \citep*{leiboldEthnicPolicyChina2013}. \citet*{francoisFactionsNondemocraciesTheory2023} introduces CCP factions, policies, and welfare in China. \citet*{francoisHowPowerShared2015} documents ethnic-political contests in Africa.} These features also defy economic theories of political accountability in political contests \citep*{barroControlPoliticiansEconomic1973,ferejohnIncumbentPerformanceElectoral1986}. Why does a rising number of political groups obtain power through a non-pivotal minority group?

% Paragraph 2 — Consequently: policy and scholarly interest, and the gap

Consequently, using domestic minorities as a political tool had become the centre of debate on the democratic process and economic development. In 2019, India's Citizenship Amendment Act ignited the largest sustain urban protest since independence \citep{jaffrelotModisIndiaHindu2021}.\footnote{The \emph{Woman, Life, Freedom} protests in Iran after the 2022 death of Mahsa Amini and by wide-spread anti-immigrants Republican campaigns before 2024 United States presidential election show similar patterns.} However, political economists have not fully understood why majority parties choose such policies in the first place, why voters reward them, and why the same mechanism produces durable one-party dominance in some polities and recurrent turnovers in others.

% Paragraph 3 — Placing the paper, stating the aim, and the toolkit

This article introduces the manufacturing of enemies in political contests to the economics of identity and electoral competition \citep*{shayoModelSocialIdentity2009,glaeserPoliticalEconomyHatred2005,gennaioliIdentityPolitics2023}.\footnote{A large literature have captured electoral mobilization of communal violence by majority parties in divided democracies.} My aim is to explain why elected majority parties choose symbolic policies against domestic minorities. I also aim to characterize the long-run consequences of doing so for political competition and social conflict. In attempting to do so, I draw on developments in contest theory and the political economy of electoral accountability.

% Paragraph 4 — The model

In my model of collective mobilization and electoral competition, symbolic policies activates a two-sided contest over public security (in identity) between a majority group and a domestic minority. Following \citet*{baligaStrategyManipulatingConflict2012}, two parties compete for the majority's vote: one with a comparative advantage in delivering economic public goods, with the other in coercive and organizational capacity. The minority is consisted of agents sensitive to their minority identities (eg., Muslim groups in India). They mobilize for preserving their identity from the majority group (eg., protest or violence actions). However, subjected to the collective action problem, mobilization only occurs when grievance among their members is large enough. The majority base faces the symmetric problem. Importantly, the greater the intensity of symbolic policy, the larger the grievance that minority mobilization averts, and the more the majority's free-riding is relaxed by the visible threat its own counter-mobilization creates. Therefore, the electoral return to symbolic policy is highest when the security-oriented party (\emph{Hawk}) has organizational advantage however unobserved in peaceful conditions; or when the economic potential of its opponents (\emph{Dove}) is sufficiently large when it cannot be offset on the consumption dimension alone.

% Paragraph 5 — Linking the model to observed patterns

This enables me to link the manufacturing of enemies to the economic and political transformations that have accompanied its recent electoral democracies. The most important changes were the rise of redistributive politics after the Cold War, the widening of the electoral franchise through liberalizing the minority in post-colonial areas, and the emergence of parties whose organizational base lies in religious, paramilitary, or coercive associations. I show manufacturing enemies by making the security dimension of contest electorally salient is at the cost of real economic and social disruption. Therefore, I aim to develop a unified framework for understanding the contemporary use of symbolic policy in otherwise disparate settings: India's cow-slaughter bans under the BJP \citep{jaffrelotModisIndiaHindu2021}, the Republican Party's post-2015 pivot to immigration and domestic-security framing in the United States \citep{sidesIdentityCrisis20162019,mutzStatusThreatNot2018}, the persistence of morality-police enforcement in Iran \citep{bajoghliIranReframedAnxieties2020}, and the consolidation of Uribismo in Colombia \citep*{acemogluMonopolyViolenceEvidence2013}. It suggests one possible explanation for the prominent role that security-coded mobilization plays during periods of economic liberalization, when the non-hawkish coalition's comparative advantage in economic delivery is at its greatest.

% Paragraph 6 — Dynamic extension, main result

To study the long-run political consequences of manufactured enemies, I develop a dynamic extension of the model, in which voters form expectations about future security capacity under each party and receive noisy signals of current economic and security performance. I build on political-agency models with retrospective accountability and on work on the persistence of political regimes. The incumbent's symbolic policy shapes both current electoral outcomes and future voters' beliefs about the permanence of each party's security capacity, which in turn feeds back into the next period's politically optimal level of policy choice. I show that, when voters are sufficiently patient and forward-looking, the security-coded party becomes an absorbing state of the political system. Voters rationally retain the hawkish incumbent (through even severe economic shocks) to avoid a durable reduction in the polity's capacity to contain future identity threats. The same applies to polities in which candidacy-gatekeeping institutions (rather than voter patience itself) supply the intertemporal commitment to security capacity. For example, Iran under the Guardian Council.

% Paragraph 7 — Dynamic extension, scope condition and opposite result

When voters are myopic and evaluate incumbents retrospectively on the basis of current performance signals, the opposite can occur. The same mechanism generates recurrent cycles between hawkish and economically competent incumbents. If the economic realization is adverse and the perceived threat environment is contained, voters unseat the hawkish party in favor of the economic alternative. This allows the contest to go dormant and the minority's immediate grievance to recede from salience. On the other hand, if the perceived threat environment is severe mobilization, voters swing back to the hawkish alternative, which reopens the cycle. Admittedly, the institutional response to manufactured enemies is a broader matter of constitutional design that lies beyond the scope of this article. But my framework does suggest that interventions that would break a conflict trap by strengthening retrospective accountability can, in a polity already on a cyclical path, amplify the very oscillations they were intended to dampen.

% Paragraph 8 — Ethnic Contest

I point out the relationship to and my departures from existing work. This paper first contributes to the theoretical literature on the economics of intergroup conflict and contest design. 
Canonical formal approach models intergroup conflict as a contest where the salient cleavage (class, religion, or ethnic identities) and the intensity of confrontation are determined by exogenous parameters such as group size, group budget, within-group inequality, or shocks on economic capacity \citep*{estebanConflictDistribution1999, estebanSalienceEthnicConflict2008, caselliTheoryEthnicConflict2006, acharyaElectoralCampaignsDynamic2024}.\footnote{Empirical literature corresponds to these theoretical advances \citep{dalbóWORKERSWARRIORSCRIMINALS2011, rohnerWarSignalsTheory2013, dubeCommodityPriceShocks2013}.} A large group of literature also formalizes how incumbents initiate conflict to divert attention from economic underperformance \citep*{hessWarDemocracy2001}. However, the contest environment itself remains largely isolated from the political process. My theoretical departure is to embed a two-sided Tullock contest \citep*{skaperdasContestSuccessFunctions1996,jiaStochasticDerivationRatio2008} with endogenous collective action into a political agency framework. Therefore, incumbent strategically designs the contest's prize. Unlike a standard neutral principal optimizing rules to maximize joint effort \citep*{barutSymmetricMultiplePrize1998,fangTurningHeatDiscouraging2020}, political principal (i.e., parties) is biased in my model. By manufacturing a visible threat, the majority relaxes its free-rider problem. I formalize a novel mechanism of conflict as an endogenous electoral instrument \citep{iyerReligiousRiotsElectoral2018, mitraImplicationsEconomicTheory2014}. 

% I point out the relationship to and my departures from existing work. I build on the economics of ethnic conflict and minority mobilization \citep{estebanConflictDistribution1999}. The literature identifies what conditions make ethnicity rather than economics the salient cleavage of social contention. \citet{estebanSalienceEthnicConflict2008} argues \emph{ex-ante} economic inequality \emph{within} an ethnic group tends to make the ethnic partition focal over the class partition.\footnote{Intra-ethnic inequality creates cooperation between the rich (offering resources) and the poor (offering effort) for collective mobilization.} Ethnic identities are also selected because ethnic identities are hard to fake \emph{ex-post} of mobilization, ensuring the inclusion of losers after conflict \citep{caselliTheoryEthnicConflict2006}.\footnote{\citet{estebanLinkingConflictInequality2011,estebanEthnicityConflictEmpirical2012} show that equilibrium conflict are determined non-linearly by \emph{intra-} and \emph{inter-} levels of group inequality.} The literature also identifies broader social-economic landscape that determines ethnic conflict, including sectoral choice between production and predation \citep{dalbóWORKERSWARRIORSCRIMINALS2011} or the informational role of inter-group trade \citep*{rohnerWarSignalsTheory2013}. A parallel body of theoretical and empirical work on mobilization asks how aggrieved members of a disadvantaged group overcome their collective-action problem. \citet{carvalhoRadicalisation2024} show that a forward-looking identity-based organisation optimally screens on commitment intensity, and that cultural purification shrinking the club is the starting point of deeper radicalisation. \citet{dubeCommodityPriceShocks2013} argues shocks to sectorial composition shift the directions of insurgent activities. \citet{bo’EconomicSocialOutsiders2023} documents economically and socially marginals mobilise radical populist groups. My departure is to endogeneize the ethnic contest within the electoral game. Ethnic mobilization is a subgame where the elected majority incumbent chooses the policy which shapes the minority's payoff. Effort levels are solved jointly as an equilibrium of two within-group Nash equilibria.

% I point out the relationship to and departures from existing work. First, this paper builds on the economics of ethnic contest and minority mobilization, a programme whose canonical structure was laid down by \citet{estebanConflictDistribution1999} and has since developed along three lines that share a common move: the contest's parameters — ethnic composition, within- and between-group inequality, sectoral prices, trade exposure — are read off the social environment, and the political process, where it enters at all, responds to rather than designs the intensity of confrontation. The first line asks when the salient cleavage is ethnic rather than economic; \citet{estebanSalienceEthnicConflict2008} identify the central result that it is economic inequality *within* an ethnic group — a "perverse synergy" — that tends to make the ethnic partition focal over the class partition, with \citet{caselliTheoryEthnicConflict2006} offering the complementary technological rationale that ethnic markers are selected because they are hard to fake and therefore cheapen the post-conflict exclusion of losers. The second line closes the empirical loop: \citet{estebanLinkingConflictInequality2011,estebanEthnicityConflictEmpirical2012} show that equilibrium conflict can be proxied by a linear combination of Gini, fractionalisation, and Esteban–Ray polarisation, a result whose cross-country validation remains the strongest distributional restriction the programme has produced. The third line nests the contest inside a larger economic system — sectoral choice between production and predation \citep{dalbóWORKERSWARRIORSCRIMINALS2011}, or the informational role of inter-group trade \citep{rohnerWarSignalsTheory2013} — which extends the exogenous-environment reading rather than breaking with it.

% A parallel minority-mobilization literature asks how aggrieved members of a disadvantaged group overcome their collective-action problem: \citet{carvalhoRadicalisation2024} show that a forward-looking identity-based organisation optimally screens on commitment intensity, and that cultural purification shrinking the club is the starting point of deeper radicalisation;

% \citet{dubeCommodityPriceShocks2013} argues shocks to sectorial composition shift the directions of insurgent activities. \citet{bo’EconomicSocialOutsiders2023} documents economically and socially marginals mobilise radical populist groups.

% discipline the economic margin of mobilisation by showing that price shocks to labour-intensive versus capital-intensive sectors move insurgent activity in opposite directions; and \citet{bo’EconomicSocialOutsiders2023} document the mirror-image logic on the majority side, where the politicians and voters of a major populist-radical-right party are disproportionately drawn from the economically and socially marginal.

% What is absent from this entire programme is a political principal who chooses the prize.

% My departure is to endogeneize the ethnic contest within the electoral game. Ethnic contest is a subgame where the elected majority incumbent chooses the policy which shapes the minority's payoff. Effort levels are solved jointly as an equilibrium of two within-group Nash equilibria.

% , so the comparative statics of either side's effort with respect to the incumbent's policy and to the incumbent's own coercive endowment are equilibrium objects rather than primitives.
% // Synthesis

% Paragraph 9 — Identity Politics

Second, I advance the formal literature on the political economy of identity and issue salience. Existing theories model the political usage of identity either as a demand-side expressive distortion of standard redistributive preferences \citep{shayoModelSocialIdentity2009, besleyRiseIdentityPolitics2019, gennaioliIdentityPolitics2023}, or as a supply-side informational problem where elites manipulate beliefs or supply hatred to split voter coalitions \citep*{glaeserPoliticalEconomyHatred2005, baligaStrategyManipulatingConflict2012, izzoIdeologicalCompetition2023, callanderCauseEffectPolitical2022}.
Recent models also how elites strategically substitute identity cleavages for economic redistribution to maintain power \citep*{acemogluKleptocracyDivideandRuleModel2004,padróimiquelControlPoliticiansDivided2007,mukandPoliticalEconomyLiberal2020}. While classic divide-and-rule mechanisms typically rely on elite coordination failure or cheap-talk manipulation. 
By contrast, my mechanism does not rely on behavioral biases, asymmetric information about the state of the world, or cheap-talk coordination. Symbolic policy functions as a technology that shifts the constraints of a collective action subgame. The incumbent alters the policy space by forcing voters into a second-best environment where security capacity becomes an unavoidable necessity. This provides a clean structural micro-foundation for the \emph{politics of fear} through endogenous manufacturing of that threat to offset a structural deficit in economic competence.\footnote{instead of the expropriation of rents under the shadow of an exogenous out-group threat.}


%Second, this model sits within the economics of identity politics. Voter's demand for identity is driven by status and distance from a group prototype \citep{shayoModelSocialIdentity2009}. \citet{besleyRiseIdentityPolitics2019} and \citet{gennaioliIdentityPolitics2023} study the trade-off between cultural and economic platform content inside a voter's self-image. On the demand side, \citet{izzoIdeologicalCompetition2023} and \citet{callanderCauseEffectPolitical2022} treat identity as a \emph{model of the world} that parties develop to organise voters' interpretation of their experience. \citet{glaeserPoliticalEconomyHatred2005} models elite production of anti-minority hatred as an electoral-supply decision. Identity-based clubs produce collective reputations and sustain oppositional identities through visible commitment practices, and therefore shapres political interaction among groups \citep{carvalhoIdentityBasedOrganizations2016,carvalhoEconomicsReligiousCommunities2021,carvalhoVeiling2013}. Finally, \citet{padróimiquelControlPoliticiansDivided2007} shows that in divided societies the fear of being ruled by the out-group attenuates voters' control of their own co-ethnic incumbent, so the incumbent can substitute group rents for performance. In my model, identity is determined by the policy action on the out-group, chosen by the incumbent as a primitive instrument. The electoral return operates through a two-sided contest with endogeneous identity formation within each group facing collective action problem.

% // Synthesis
% Second, this paper sits within the economics of identity politics, which over the past two decades has developed along three partly independent strands whose common blind spot is the absence of a policy lever operating directly on the out-group. The first, demand-side, strand begins with \citet{shayoModelSocialIdentity2009}, whose central result — a robust negative cross-country relationship between national identification and redistribution, driven by status and distance from a group prototype — establishes the template that later work generalises: \citet{besleyRiseIdentityPolitics2019,gennaioliIdentityPolitics2023} study the trade-off between cultural and economic platform content inside a voter's self-image, while \citet{izzoIdeologicalCompetition2023,callanderCauseEffectPolitical2022} treat ideology itself as a *model of the world* that parties develop to organise voters' interpretation of their experience and that, in equilibrium, always diverges across parties. In this strand identities and ideologies are the relevant strategic objects; policy is derivative. The second, supply-side, strand asks who produces identity content and how: \citet{glaeserPoliticalEconomyHatred2005} models elite production of anti-minority hatred as an electoral-supply decision operating through a specific informational technology, while the Carvalho programme — \citet{carvalhoIdentityBasedOrganizations2016,carvalhoEconomicsReligiousCommunities2021,carvalhoVeiling2013} — shows that identity-based clubs produce collective reputations and sustain oppositional identities through visible commitment practices that, as the veiling case illustrates, can expand rather than restrict engagement with the outside economy. Here the producer is the organisation or the ideologue, and the electoral return enters only indirectly. The third strand bridges demand and supply through political agency: \citet{padróimiquelControlPoliticiansDivided2007} shows that in divided societies the fear of being ruled by the out-group attenuates voters' control of their own co-ethnic incumbent, so the incumbent can substitute group rents for performance — but the mechanism runs through voter beliefs, not through the incumbent's policy action on the out-group. On the empirical side, \citet{mutzStatusThreatNot2018} documents that perceived group-status loss, rather than economic dislocation, predicts the 2016 US realignment — a finding the demand-side strand can rationalise but has no mechanism to generate. My departure is threefold. Identity in this paper is neither a preference primitive nor a supplied ideological content: it is a policy action on the out-group, chosen by the incumbent as a primitive instrument. The electoral return operates through a two-sided contest technology whose effectiveness depends on the incumbent's coercive endowment, so identity politics becomes a policy margin whose electoral weight a security-advantaged incumbent can actively manufacture rather than a preference dimension voters exogenously carry into the booth. And the within-group free-riding problem the Carvalho programme studies as a club problem becomes here one blade of the majority's electoral equilibrium, with the symmetric problem on the minority side forming the other — the two clubs are solved simultaneously inside a single electorally-mediated fixed point.
% //Synthesis

% Paragraph 10 — Conflict as Electoral Strategy

Finally, my dynamic extension contributes to the political-agency theory of electoral accountability. Canonical retrospective-voting models \citep*{barroControlPoliticiansEconomic1973,ferejohnIncumbentPerformanceElectoral1986} have been extended to capture information design \citep*{banksRepeatedElectionsModel1993,przeworskiDemocracyAccountabilityRepresentation1999,sandroniWhenConfrontRole2018a,acharyaPoliticalAccountabilityMoral2025} and behavioral responses \citep*{levyCorrelationNeglectVoting2015,ortolevaOverconfidencePoliticalBehavior2015,liElectoralAccountabilitySelection2023,vaethVoterLearningUnidimensional2023}. I combine three established technical ingredients of this literature in a manufactured-grievance contest setting that has not previously been studied in this combination. From \citet{coatePolicyPersistence1999} I take the hysteresis-interval structure on retention thresholds: the same inherited state supports retention of either incumbent depending on which party currently holds office, opening a generic gap between the two thresholds whose width is proportional to the persistence of the underlying state variable. From \citet{acharyaPoliticalAccountabilityMoral2025}, building on the recursive-contract formulation of \citet{spearOnRepeatedMoralHazard1987}, I take the promised-utility-as-state Bellman recursion, which lets the voter's value function be defined directly on the payoff-relevant state and makes forward-looking retention incentives tractable without explicit belief tracking. From \citet{padróimiquelControlPoliticiansDivided2007} I take the fear-of-exclusion wedge that compares the voter's continuation values across regimes and pins down the cutoff retention rule. Combining these three ingredients in a setting where the state variable is the adversary's mobilisation response to the agent's own policy choice yields what I call \emph{manufactured persistence}: the strategic agent's action accumulates a state that locks in her preferred regime, but the state is the response of a separate group whose mobilisation is microfounded as a Tullock contest stake.

The dynamic equilibrium concept is Markov Perfect Equilibrium in the sense of \citet{maskinMarkovPerfectEquilibrium2001}, and the unified phase-transition characterisation of trap and cycles draws conceptually on the stochastic-stability programme of \citet{youngEvolutionConventions1993,youngIndividualStrategySocial1998} and \citet{kandoriLearningMutationLong1993}, who select among multiple deterministic equilibria via the invariant distribution of a perturbed Markov process and use the depth of the deterministic basin of attraction as the selection criterion. Because my state space is continuous and the persistent shocks have fixed support rather than vanishing amplitude, the technical machinery is the Foster--Lyapunov drift theory of \citet{meynMarkovChainsStochastic2009} rather than the resistance graphs of Young (1993); the substantive mapping is nonetheless tight, with the bifurcation parameter $\rho$ playing the role of an effective noise scale even though the primitive shock distribution is held fixed. In this framework the conflict trap appears as an absorbing state of a dynamically rational electorate, not as an institutional failure of the state apparatus, while the cycles regime appears as the unique invariant distribution of the same perturbed chain when the deterministic basin is shallow. By doing so I also extend existing theories of redistribution politics and state capacity in electoral polities \citep*{alesinaPoliticsBusinessCycles1989,besleyOriginsStateCapacity2009,besleyStateCapacityConflict2010}.






%electoral accountability, state capacity, and regime persistence. By bridging retrospective voting models with the literature on the political economics of state capacity \citep*{besleyOriginsStateCapacity2009,besleyStateCapacityConflict2010}, 
%While existing work on the dismantling of institutional constraints shows how voters might rationally concentrate power to facilitate desirable redistribution \citep*{alesinaPoliticsBusinessCycles1989,coatePolicyPersistence1999}, I show how voters can be trapped in a \emph{low-welfare, high-conflict} regime precisely because the incumbent's provocations in the history have rendered their coercive capacity indispensable. In my model, I trace the dynamic feedback between the inherited grievance environment and the forward-looking value of state capacity. I reveal the \emph{conflict trap} but can be the absorbing state of a dynamically rational electorate instead of an institutional failure of state apparatus (eg., constitution). Conversely, under myopic retrospective voting, the same mechanism generates recurrent political cycles between economic competence and security provision. Therefore, I provide a unified structural explanation for the empirical oscillation between redistributive and hawkish regimes in divided democracies.

% Third, this paper joins the literature on the strategic use of conflict for electoral ends. The closest theoretical antecedent is \citet{baligaStrategyManipulatingConflict2012}, who study an extremist manipulating a two-sided hawk-dove conflict through public cheap-talk messaging. \citet{desaiTheoryElectoralCompetition2025} extends the electoral-competition logic to developing democracies, where voters' choice between a security-oriented and an economically oriented platform turns on the credibility of each.
% Conflict between groups rises from shifts in party politics and economic powers \citep{iyerReligiousRiotsElectoral2018,mitraImplicationsEconomicTheory2014}.\footnote{\citet{blakesleeRathYatraEffect2018} and \citet{blakesleePoliticsPublicGoods2018} trace the electoral returns of specific symbolic campaigns and leadership shocks. My framework delivers two sharp quantitative objects, a provocation cutoff below which no symbolic policy is taken and a technological-endowment ceiling beyond which provocation is self-defeating, that sharpen the positive-returns pattern of the empirical literature into a testable non-monotonicity.} The common limitation across this body of work is that the political lever is either a cheap-talk message \citep{baligaStrategyManipulatingConflict2012} or a realised riot whose intensity is read off the economic environment \citep{iyerReligiousRiotsElectoral2018,mitraImplicationsEconomicTheory2014}. I treat it as a primitive policy choice for the political principal's to shift the prize of contest and an endogenous mobilisation response.


%===================================================================================
% V2 REVISION: empirical facts (input from existing file)
%===================================================================================

\input{empirical_facts}


\section{The Model with Mobilisation Stock} \label{sec:model_v2}

Two Majority parties compete for office in discrete time $t=0,1,2,\dots$ over an infinite horizon: a \emph{Dove} ($B$) with a comparative advantage in economic public-good provision and a \emph{Hawk} ($A$) with a comparative advantage in security technology (state capacity). Security in this economy is not delivered by fiat but produced by a Tullock contest between decentralised Majority enforcement and Minority mobilisation. In peaceful environments, Minority mobilisation is dormant, the contest is inactive, and realised security is high under either party; elections then turn on economic performance, where the Hawk is structurally disadvantaged. The Hawk can overturn this disadvantage by enacting provocative symbolic policy ($d>0$) that manufactures a visible threat and triggers Minority mobilisation. The activated threat reduces Majority free-riding, raises decentralised enforcement, and translates the Hawk's superior state capacity into a Security Premium at the ballot box. Symbolic provocation is therefore an electoral substitute for economic competence, but it is disciplined by an inverted-U: beyond a peak threat level, additional mobilisation overwhelms Majority enforcement and the electoral return falls. The mechanism implies strictly positive rent dissipation whenever provocation is used. The novelty of this paper relative to a static benchmark is that today's mobilisation does not vanish at the end of the period: it accumulates into a \emph{mobilisation stock} $M_t$ that depreciates only slowly, enters the next period's contest as an additional stake, and converts the within-period game into a Markov Perfect Equilibrium on the state $(M_t,k_t)$. Two long-run regimes emerge as parameter regions of the same primitive: a \emph{conflict trap} in which the Hawk is retained indefinitely by the persistence of the stock she manufactured, and a \emph{political cycles} regime in which fast decay and stochastic shocks generate recurrent regime turnover.

\subsection{Environment}

The economy is populated by a measure-one continuum of citizens divided into two ethnic or religious groups: a Majority $\mathsf{M}$ of population share $n_M>1/2$ and a Minority $\mathsf{m}$ of share $n_m=1-n_M$. The Majority is represented by two competing political parties, the Hawk ($A$) and the Dove ($B$), who compete for the support of the Majority representative voter. The Minority does not vote, so symbolic policy is an unconstrained strategic margin in the Majority's electoral game.

In every period the incumbent party $k\in\{A,B\}$ selects a policy vector $\mathbf{q}_k=(d_k,g_k)\in\mathbb{R}_+^2$. The first instrument, $d$, is the intensity of identity-based regulation (cattle-slaughter bans, dress codes, citizenship registers, language laws); it enters payoffs because it imposes a stake on the Minority that triggers mobilisation. The second instrument, $g$, is the level of consumption-relevant public good provision. Parties differ in a two-dimensional technological endowment $(S_k,\bar g_k)$:
\begin{equation}\label{eq:party_endowment_v2}
    S_A \;>\; S_B \quad\text{and}\quad \bar g_A \;<\; \bar g_B,
\end{equation}
so the Hawk has a higher security-and-coercion competence (which scales the productivity of decentralised Majority enforcement in the Tullock contest below) and the Dove a higher public-goods ceiling. The endowments are taken as primitives of party type rather than choices: they reflect the human capital, bureaucratic expertise, and coalition partners that each party brings into office, all of which are slow-moving relative to a single electoral cycle. Because voters' utility is strictly increasing in $g$ and the ceiling $\bar g_k$ is the only constraint on the economic-policy margin, every incumbent finds it optimal to exhaust the technological frontier:
\begin{equation}\label{eq:g_corner_v2}
    g_k^*\;=\;\bar g_k\quad\text{for }k\in\{A,B\},
\end{equation}
so $g$ carries no strategic content in equilibrium. The economic deficit that drives the Hawk's electoral handicap is the primitive
\begin{equation}\label{eq:du_v2}
    \Delta u\;\equiv\;u(\bar g_B)-u(\bar g_A)\;>\;0,
\end{equation}
that is, the gap is no longer an \emph{ad hoc} preference assumption but the other face of the same comparative-advantage tradeoff that gives the Hawk its higher security competence.

The dynamic state of this economy is a single scalar, the \emph{mobilisation stock} $M_t\in\mathbb{R}_+$, augmented by the incumbent's identity $k_t\in\{A,B\}$. The stock captures Minority grievance and organisational capital that persist beyond a single period of contest activation; it admits two complementary interpretations that yield identical algebra. First, $M_t$ measures accumulated organisational commitment by the Minority: each period of activated contest builds up identity-based networks — protest infrastructure, communal media, legal-advocacy organisations, vigil committees — that depreciate slowly when symbolic policy recedes. Second, $M_t$ measures the Minority's posterior on the Hawk's manufactured-threat policy: each period of $d_t>0$ raises the Minority's expectation that future symbolic policy will continue, which raises its current willingness to mobilise. We adopt the organisational reading as the working narrative and let the stock evolve according to
\begin{equation}\label{eq:M_evolution_v2}
    M_{t+1}\;=\;(1-\rho)\,M_t\;+\;\rho\,E_m^*(d_t,S_{k_t};M_t),
\end{equation}
where $\rho\in(0,1)$ is the depreciation rate, $E_m^*(\cdot)$ is the within-period equilibrium Minority effort characterised in \autoref{lem:contest_v2} below, and $M_0\ge 0$ is exogenous. The persistence parameter $1-\rho$ is the central comparative-static dimension of the dynamic analysis: when $\rho$ is small, current provocation has long-lasting electoral consequences and even a Hawk-to-Dove transition leaves an active stock for many periods; when $\rho$ is close to one, the inherited stock decays rapidly and the dynamic problem collapses to a sequence of within-period games.

The political interaction in each period is a four-stage game solved by backward induction. In Stage 1, the incumbent $k_t$ selects $d_t\ge 0$ (the corner $g_{k_t}^*=\bar g_{k_t}$ is mechanical). In Stage 2, given $(d_t,S_{k_t},M_t)$, the Majority and Minority simultaneously choose enforcement and resistance effort; the symmetric Nash equilibrium $(E_M^*,E_m^*)$ of \autoref{lem:contest_v2} below realises, and equilibrium security $\Pi_{k_t}^*$ obtains. In Stage 3, the Majority electorate observes noisy performance signals and elects $k_{t+1}\in\{A,B\}$. In Stage 4, the stock updates according to \autoref{eq:M_evolution_v2}. The solution concept is Markov Perfect Equilibrium on the payoff-relevant state $(M_t,k_t)$, with within-period contest equilibria restricted to the symmetric Nash equilibrium of the two within-group games. The static benchmark obtains as the special case $M_t=0,\xi=0$, in which the dynamic decoration is inactive and the analysis reduces to the within-period game.

\section{Micro-foundations of Conflict and Collective Action}\label{sec:contest_v2}

Conflict in this economy is modelled as a contest over political dominance. Unlike standard contest models in which groups act as unitary actors, I explicitly model the collective-action problem within \emph{both} groups and solve for the joint Nash equilibrium of mobilisation. The Majority faces a free-rider problem in decentralised enforcement; the Minority faces the symmetric free-rider problem in decentralised resistance. Each individual best-responds to aggregate effort on the other side, and the primitive policy lever $d$ enters the joint problem only through its effect on the Minority's stake. The novelty of the present specification relative to a static benchmark is that the Minority's stake is not the current symbolic policy alone but the \emph{stock-augmented} stake $\hat d^\sigma\equiv d^\sigma+\xi M$ — current provocation plus inherited grievance — so that yesterday's contest activation continues to discipline today's Majority free-riding through the persistence of $M$. Throughout this section the within-period symbolic policy $d$ and the inherited stock $M$ are held fixed; effort on both sides is determined in Stage 2 by the simultaneous-move subgame.

Each within-group collective-action problem in the next two subsections is a population game in the sense of \citet{sandholmPopulationGames2010}: a continuum of citizens choose effort, and the symmetric Nash equilibrium I characterise is the rest point of the standard replicator dynamic --- the population-level outcome to which best-response, imitation-of-success, and reinforcement-learning revision protocols converge. Within each group, the equilibrium collapses to a single per-capita effort level, and the comparative statics that follow describe how this aggregate response moves with the policy lever $d$ and the inherited stock $M$.

\subsection{The Majority's collective-action problem}

While both economic stability and security are public goods, they differ in production technology. Economic goods are provided top-down by the state, whereas security (dominance) requires decentralised participation by Majority citizens. Each Majority citizen benefits from dominance but individually under-provides enforcement effort. Fix an incumbent $k$ and suppose the Majority consists of $N_M$ identical citizens indexed by $i=1,\dots,N_M$. Citizen $i$ chooses enforcement effort $e_i\ge 0$ at private cost $\tfrac{1}{2}e_i^2$. Aggregate Majority effort is $E_M\equiv\sum_i e_i$, and aggregate Minority effort $E_m$ is determined symmetrically below.

Security is produced by a stochastic contest between a state-amplified Majority and an oppositional Minority. The incumbent's security competence $S_k>0$ acts as a force multiplier on Majority effort, and the probability that the Majority prevails is given by the Tullock contest success function\footnote{One micro-foundation \citep{skaperdasContestSuccessFunctions1996,jiaStochasticDerivationRatio2008} assumes performance levels $Y_M=\ln(S_kE_M)+\varepsilon_M$ and $Y_m=\ln(E_m)+\varepsilon_m$ with i.i.d.\ Gumbel errors; the probability of Majority dominance simplifies to \autoref{eq:CSF_v2}.}
\begin{equation}\label{eq:CSF_v2}
    \Pi_k(E_M,E_m)\;=\;\frac{S_k\,E_M}{S_k\,E_M+E_m}.
\end{equation}
This formulation captures the model's central asymmetry: holding office grants access to $S_k$, which scales the productivity of decentralised Majority effort and therefore makes security competence electorally salient when the opposition is mobilised. Citizen $i$ derives public benefit $\Lambda\cdot\Pi_k(E_M,E_m)$, where $\Lambda>0$ is the per-capita Majority valuation of security, and chooses $e_i$ to maximise $\Lambda\Pi_k-\tfrac{1}{2}e_i^2$. The interior first-order condition and the symmetric Nash imposition $e_i=e$ deliver the Majority best-response
\begin{equation}\label{eq:EM_BR_v2}
    \frac{E_M}{N_M}\;=\;\Lambda\,\frac{S_k\,E_m}{(S_k E_M+E_m)^2},
\end{equation}
which is one half of a simultaneous-move Nash problem in which $E_m$ must also be determined.

\subsection{The Minority's collective-action problem with stock-augmented stake}

Minority mobilisation is the outcome of a collective-action problem structurally symmetric to the Majority's. The intensity of grievance — and hence the Minority's stake in the contest — is generated jointly by the incumbent's current symbolic policy $d$ and by the inherited mobilisation stock $M$. Citizen $j=1,\dots,N_m$ chooses resistance effort $e_j\ge 0$ at private cost $\tfrac{1}{2\kappa}e_j^2$, where $\kappa>0$ denotes the group's organisational capacity (or social capital): a higher $\kappa$ reduces the marginal cost of effort, reflecting stronger internal coordination networks. Aggregate Minority effort is $E_m\equiv\sum_j e_j$. If the Majority prevails ($\Pi_k=1$), symbolic oppression is enforced and the Minority suffers a grievance loss $\phi(d^\sigma+\xi M)$, where $\phi>0$ is the group's sensitivity to grievance, $\sigma>0$ governs the elasticity of grievance to current symbolic policy, and $\xi\ge 0$ is the \emph{stock-stake elasticity} that converts inherited organisational capital into a current-period stake. If the Minority prevails ($\Pi_k=0$), the loss is avoided. Citizen $j$ therefore solves
\begin{equation}\label{eq:V_minority_v2}
    \max_{e_j\ge 0}\;V_j\;=\;\phi\,\big(d^\sigma+\xi M\big)\,\bigl(1-\Pi_k(E_M,E_m)\bigr)\;-\;\frac{1}{2\kappa}\,e_j^2.
\end{equation}
The interior first-order condition and symmetric Nash imposition give the Minority best-response
\begin{equation}\label{eq:Em_BR_v2}
    \frac{E_m}{N_m}\;=\;\kappa\phi\,(d^\sigma+\xi M)\,\frac{S_k\,E_M}{(S_k E_M+E_m)^2}.
\end{equation}
The two best-responses \autoref{eq:EM_BR_v2} and \autoref{eq:Em_BR_v2} are structurally identical up to a relabelling of stakes: the Majority mobilises at rate $\Lambda\cdot(-\partial\Pi_k/\partial E_M)$ and the Minority at rate $\phi(d^\sigma+\xi M)\kappa\cdot(-\partial\Pi_k/\partial E_m)$. The Tullock contest is therefore a genuine two-sided Nash equilibrium, not the composition of an expressive reaction with a Majority best-response, and the Minority's effort is no longer independent of the incumbent's technology: a stronger $S_k$ reshapes the joint best-response system through the Minority's own optimisation.

The bracketed term $d^\sigma+\xi M$ is the only place in the entire micro-foundation where the inherited stock enters. As derived in \autoref{lem:bayes_v2} below, it is the Bayesian posterior expectation of regime grievance intensity rescaled by the signal weight, so all subsequent equilibrium objects can be obtained from the static benchmark by the substitution $d^\sigma\mapsto\hat d^\sigma\equiv d^\sigma+\xi M$. The static benchmark without grievance accumulation is the special case $\xi=0$ (or, equivalently, $M=0$), which corresponds to a fully diffuse prior $\tau_M\to 0$. Even at $d=0$, the Minority's stake is positive whenever $M>0$, because past mobilisation has built organisational and identity-salience capital --- and a sharp prior on regime hostility --- that current peace does not immediately undo. This is the structural source of the persistence that drives the dynamic results below.

\subsubsection*{Microfoundation: Bayesian updating of grievance intensity}

The additive specification $\hat d^\sigma=d^\sigma+\xi M$ is not an algebraic convenience but the closed-form posterior expectation of regime grievance intensity under standard Normal--Normal Bayesian updating, with $M$ playing the role of the prior anchor and $d^\sigma$ playing the role of the public-signal mean. The Minority is uncertain about the regime's true grievance intensity in the current period, denoted $\theta_t\in\mathbb R$, and forms a posterior on $\theta_t$ by combining its prior --- anchored in accumulated experience of past mobilisation episodes --- with a noisy public signal generated by the incumbent's symbolic policy. This places the within-period information environment squarely inside the Bayesian-persuasion framework of \citet{kamenicaGentzkowBayesianPersuasion2011} and the older signalling antecedent of \citet{crawfordSobelStrategicInformation1982}, with the distinguishing feature that the prior is itself an endogenous summary of past play through the mobilisation stock $M_t$.

Concretely, the Minority's prior on regime intent is $\theta_t\mid M_t\sim\mathcal{N}(M_t,\tau_M^{-1})$, where $M_t\ge 0$ is the inherited mobilisation stock and $\tau_M>0$ is the prior precision; a long history of activated grievance episodes both raises the prior mean (more past hostility) and sharpens the prior precision (less residual uncertainty about the regime's type). The current symbolic policy $d_t$ generates a noisy public signal of regime intent $s_t=d_t^\sigma+\epsilon_t$ with $\epsilon_t\sim\mathcal{N}(0,\tau_d^{-1})$ i.i.d.\ across $t$ and signal precision $\tau_d>0$; the elasticity $\sigma>0$ is the same parameter that governs the perceived-grievance scaling everywhere else in the model. Because $\epsilon_t$ has expectation zero, the signal $s_t$ is replaced by its mean $d_t^\sigma$ in the posterior expectation we now derive.

\begin{lemma}[\emph{Bayesian microfoundation of the stock-augmented stake}]\label{lem:bayes_v2}
\emph{The additive specification $\hat d^\sigma = d^\sigma + \xi M$ is the Minority's Bayesian posterior expectation of regime grievance intensity, rescaled by the signal weight, with $\xi = \tau_M/\tau_d$ given a structural interpretation as the ratio of prior precision to signal precision.}

Suppose the Minority's prior on regime grievance intensity is $\theta_t\mid M_t\sim\mathcal{N}(M_t,\tau_M^{-1})$ with $\tau_M>0$, and the public signal is $s_t = d_t^\sigma + \epsilon_t$ with $\epsilon_t\sim\mathcal{N}(0,\tau_d^{-1})$ i.i.d.\ and $\tau_d>0$. Then the posterior expectation is
\begin{equation}\label{eq:bayes_post_v2}
    E[\theta_t\mid s_t,M_t]\;=\;(1-\omega)\,M_t+\omega\,d_t^\sigma,\qquad\omega=\tfrac{\tau_d}{\tau_M+\tau_d}\in(0,1),
\end{equation}
and the Minority's effective stake $\hat d_t^\sigma:=E[\theta_t\mid s_t,M_t]/\omega$ satisfies
\begin{equation}\label{eq:bayes_form_v2}
    \hat d_t^\sigma\;=\;d_t^\sigma+\xi\,M_t,\qquad\xi:=\tfrac{1-\omega}{\omega}=\tfrac{\tau_M}{\tau_d}.
\end{equation}
The Minority's expected loss in the within-period collective-action problem reduces to $\phi\,\omega\,\hat d_t^\sigma(1-\Pi_k)$, recovering \autoref{eq:V_minority_v2} after absorbing $\omega$ into the calibration of $\phi$.
\end{lemma}

The polity-level interpretation of $\xi$ that follows treats $\phi\omega$ as a recalibrated grievance-sensitivity that is held fixed across polities, with $\xi=\tau_M/\tau_d$ varying as primitives; if $\phi$, $\tau_M$, and $\tau_d$ are all varied independently as primitives, the substantive comparative statics need to track the joint movement of $\phi\omega$ alongside $\xi$.

We treat $M_t$ as the prior anchor in reduced form. Under specific conjugate-history assumptions (e.g., Gaussian signals across all $\tau<t$), $M_t$ would coincide with the precision-weighted average of past public signals; the substantive content of the lemma is the additive form $\hat d^\sigma=d^\sigma+\xi M$, which is what the rest of the model uses, not the literal Bayesian derivation of $M_t$.

The result is a standard Normal--Normal conjugate-updating argument (see, e.g., DeGroot 1970): the posterior is Normal with mean given by the precision-weighted average of the prior mean and the signal, and rescaling by $1/\omega$ delivers the additive form. The formal proof is in \autoref{app:proof:bayes_v2}.

The structural-precision interpretation of $\xi=\tau_M/\tau_d$ is the substantive payoff of this microfoundation. High $\xi$ corresponds to long-memory polities in which the Minority's prior is sharp relative to the current signal: historical experience anchors current beliefs strongly and any single period of provocation moves the posterior only slightly. India, with its century-long communal record, and Iran and Hungary, with their deep templates of regime hostility, are the empirical archetypes. Low $\xi$ describes short-memory polities in which the prior is diffuse and current policy dominates the posterior, as in the post-2016 United States or post-Uribe Colombia, where fresh ethnicising policy moves Minority beliefs rapidly because the prior is weakly anchored. This polity-level mapping has a deeper consequence: the two parameters that drive the unified phase-transition result of \autoref{prop:phase_transition} --- $\xi$ governing the within-period equilibrium and $\rho$ governing the deterministic drift of the stock --- have a common informational origin. A polity with high prior precision $\tau_M$ exhibits both long-memory beliefs (high $\xi$) and a slow-decaying empirical mobilisation stock (low $\rho$), because the same information-flow regime that lets historical episodes anchor today's beliefs also lets organisational and identity-salience capital persist across periods. The depth-of-trap parameter $\rho$ and the stake-amplification parameter $\xi$ are therefore not independent primitives but structural reflections of the same underlying information-flow regime, which tightens the polity-level mapping that the dynamic analysis below exploits.

\subsection{Joint contest equilibrium and comparative statics}

Define the technology-independent stakes ratio $\alpha\equiv\sqrt{\Lambda N_M/(\kappa\phi N_m)}$ and the scale constant $\beta\equiv(\kappa\phi N_m\Lambda N_M)^{1/4}$. The joint contest equilibrium conditional on $(d,S_k,M)$ is the pair $(E_M^*,E_m^*)$ that simultaneously satisfies \autoref{eq:EM_BR_v2} and \autoref{eq:Em_BR_v2}. The following lemma characterises this equilibrium in closed form.

\begin{lemma}[\emph{Joint contest equilibrium with stock}]\label{lem:contest_v2}\label{lem:contest_equilibrium}
\emph{For every $(d,S_k,M)$, the within-period subgame admits a unique symmetric Nash equilibrium, and the inherited stock $M$ enters this equilibrium only through the augmented stake $\hat d^\sigma\equiv d^\sigma+\xi M$.}
Fix $(d,S_k,M)\in[0,\infty)\times(0,\infty)\times[0,\infty)$ and define
\begin{equation}\label{eq:dhat_v2}
    \hat d^\sigma\;\equiv\;d^\sigma+\xi M.
\end{equation}
If $\hat d^\sigma=0$ (equivalently, both $d=0$ and $M=0$), the contest is dormant: $E_M^*=E_m^*=0$ and $\lim_{\hat d\downarrow 0}\Pi_k^*=1$. If $\hat d^\sigma>0$, the unique equilibrium is
\begin{equation}\label{eq:Em_Sk_explicit}
    E_m^*(d,S_k;M)\;=\;\frac{\beta^2\,S_k^{1/2}\,\hat d^{\,3\sigma/4}}{S_k\alpha+\hat d^{\,\sigma/2}},
    \qquad
    E_M^*(d,S_k;M)\;=\;\alpha\,\beta^2\,\frac{S_k^{1/2}\,\hat d^{\,\sigma/4}}{S_k\alpha+\hat d^{\,\sigma/2}},
\end{equation}
with effort ratio $E_M^*/E_m^*=\alpha\,\hat d^{-\sigma/2}$, and equilibrium security
\begin{equation}\label{eq:Pi_v2}
    \Pi_k^*(d,S_k;M)\;=\;\frac{S_k\alpha}{S_k\alpha+\hat d^{\,\sigma/2}}.
\end{equation}
$\Pi_k^*$ is strictly increasing in $S_k$ and strictly decreasing in $\hat d$ (hence in both $d$ and $M$), with $\lim_{\hat d\downarrow 0}\Pi_k^*=1$ and $\lim_{\hat d\uparrow\infty}\Pi_k^*=0$.
\end{lemma}

\autoref{lem:contest_v2} contains four results that organise the rest of the paper. First, the joint contest has a closed form, so the analysis that follows is calculus on \autoref{eq:Pi_v2} rather than a sequence of implicit-function arguments. Second, the Majority-to-Minority effort ratio $\alpha\hat d^{-\sigma/2}$ does not depend on $S_k$: the incumbent's state capacity shifts the level of both efforts but not their ratio. Third, security is monotone in both arguments — increasing in $S_k$, decreasing in $\hat d$ — and the Hawk's higher $S_A$ dominates the level of effective enforcement throughout. Fourth, the contest is dormant in peacetime in the precise sense that $\hat d^\sigma=0$ collapses both efforts to zero and delivers full dominance under either party. The crucial difference from the static benchmark is that dormancy now requires both $d=0$ \emph{and} $M=0$: the inherited stock alone can keep the contest active even after a Hawk-to-Dove transition. The proof is in \autoref{app:proof:contest_v2}.

I now read off the two comparative statics that the electoral analysis requires. The first concerns how the joint equilibrium responds to state capacity at fixed stake.

\begin{lemma}[\emph{State capacity, mobilisation, and effective enforcement}]\label{lem:Sk_v2}\label{lem:Sk_statics}
\emph{Holding the augmented stake fixed, raw mobilisation is inverted-U in state capacity while effective enforcement and equilibrium security rise monotonically: a stronger state first crowds in street-level enforcement, then progressively substitutes its own coercive apparatus for it.}
Fix $\hat d>0$. Both $E_M^*$ and $E_m^*$ are continuously differentiable and strictly positive on $S_k\in(0,\infty)$, and both are single-peaked in $S_k$ with common unique maximiser
\begin{equation}\label{eq:Sk_threshold}
    \overline S(\hat d)\;\equiv\;\frac{\hat d^{\sigma/2}}{\alpha}.
\end{equation}
Effective Majority enforcement $Z_k^*\equiv S_k E_M^*$ and equilibrium security $\Pi_k^*$ are strictly increasing in $S_k$ on $(0,\infty)$.
\end{lemma}

\begin{corollary}[\emph{Contest balance at the mobilisation peak}]\label{cor:peak_v2}\label{cor:Sk_threshold}
\emph{At the mobilisation peak the contest is exactly balanced --- the Majority and Minority each win with probability one-half --- and peak mobilisation depends only on stakes primitives.}
At $S_k=\overline S(\hat d)$, $\Pi_k^*=1-\Pi_k^*=\tfrac{1}{2}$, i.e., the contest is symmetric across the two sides, and the peak Majority mobilisation is the primitive-only constant
\begin{equation}\label{eq:EM_peak_v2}
    E_M^*\big(\hat d,\overline S(\hat d)\big)\;=\;\tfrac{1}{2}(\Lambda N_M)^{3/4}(\kappa\phi N_m)^{1/4},
\end{equation}
independent of $\hat d$.
\end{corollary}

These two results clarify why a Hawk regime need not coincide with visibly higher Majority street violence. When $S_k$ is low, decentralised enforcement has little leverage in the contest, so free-riding dominates and mobilisation is weak. As $S_k$ rises into an intermediate range, each unit of citizen effort becomes more effective and the private return to participation rises; in this region a Hawk that is stronger than the Dove but not overwhelmingly strong relies on grass-roots enforcement, and state capacity \emph{complements} citizen mobilisation. Once $S_k$ exceeds the threshold $\overline S(\hat d)$, the state's coercive apparatus is sufficiently effective that dominance can be maintained with less decentralised effort, the private return to participation falls, and citizens withdraw. Aggregate mobilisation $E_M^*$ then declines even as effective enforcement $Z_k^*=S_k E_M^*$ and equilibrium security $\Pi_k^*$ continue to rise. Thus only a relatively weaker Hawk induces visible mass participation; a sufficiently strong Hawk secures order from above, through state capacity rather than street-level mobilisation. The closed-form characterisation in \autoref{eq:Sk_threshold}--\autoref{eq:EM_peak_v2} sharpens this story: the switch from complementarity to substitution happens exactly where the contest is balanced, and the peak level of street mobilisation depends only on the stakes primitives, not on the symbolic policy or the inherited stock that triggered it. \autoref{fig:Sk_statics} plots both panels of \autoref{lem:Sk_v2}, and matches the spatial heterogeneity in cattle-ban mobilisation visible in \autoref{fig:maps}: the most intense ground-level enforcement appears in states with intermediate, not maximal, BJP institutional capacity.

\subsection{Symbolic policy, the migrating Security Premium, and rent dissipation}

The substantively interesting comparative static for the electoral analysis is how the closed-form security $\Pi_k^*(d,S_k;M)$ varies with current symbolic policy when the two parties are evaluated at a common environment $(d,M)$. Since $\Pi_k^*$ is strictly decreasing in $\hat d$, more provocation lowers realised security under \emph{either} party. The Hawk's electoral rationale therefore hinges not on the absolute security level but on the gap between the two parties' equilibrium securities. Following \citet{barutSymmetricMultiplePrize1998}, define the Security Premium
\begin{equation}\label{eq:security_premium_d}
    \Delta\Pi(d;M)\;\equiv\;\Pi_A^*(d,S_A;M)-\Pi_B^*(d,S_B;M)
    \;=\;\frac{S_A\alpha}{S_A\alpha+\hat d^{\,\sigma/2}}-\frac{S_B\alpha}{S_B\alpha+\hat d^{\,\sigma/2}}.
\end{equation}
The next lemma shows that $\Delta\Pi$ is inverted-U in current $d$ for each fixed $M$, with a sharp closed-form ceiling that depends only on the technology ratio $S_A/S_B$, and — crucially — that the location of the peak \emph{migrates leftward} as inherited grievance rises.

\begin{lemma}[\emph{Inverted-U Security Premium with migrating peak}]\label{lem:invU_v2}\label{lem:reaction_invertedU}
\emph{The Security Premium is single-peaked in current $d$, hits a ceiling that depends only on the technology ratio, and the location of the peak migrates leftward as the inherited stock rises until, in the deep regime, it reaches the corner $d=0$.}
Suppose $S_A>S_B>0$. Then $\Delta\Pi(\,\cdot\,;M)$ is single-peaked on $[0,\infty)$ for each $M\ge 0$, with maximiser
\begin{equation}\label{eq:dpeak_v2}
    d^{\mathrm{peak}}(M)\;=\;\begin{cases}
        \big(\alpha^2 S_A S_B-\xi M\big)^{1/\sigma} & \text{if }M<\alpha^2 S_A S_B/\xi,\\
        0 & \text{if }M\ge\alpha^2 S_A S_B/\xi.
    \end{cases}
\end{equation}
For $M<\alpha^2 S_A S_B/\xi$, the unconstrained peak attains
\begin{equation}\label{eq:DPi_peak_v2}
    \max_{d\ge 0}\Delta\Pi(d;M)\;=\;\frac{\sqrt{S_A}-\sqrt{S_B}}{\sqrt{S_A}+\sqrt{S_B}}\;\in\;(0,1),
\end{equation}
the same algebraic form as in the static benchmark. For $M\ge\alpha^2 S_A S_B/\xi$, $\Delta\Pi(\cdot;M)$ is strictly decreasing in $d$ on $[0,\infty)$, the constrained maximum is attained at $d=0$ with value $\Delta\Pi(0;M)<(\sqrt{S_A}-\sqrt{S_B})/(\sqrt{S_A}+\sqrt{S_B})$, and $\Delta\Pi(0;M)>0$ for all $M>0$.
\end{lemma}

\autoref{lem:invU_v2} contains the central new prediction generated by the dynamic decoration. At $M=0$, the peak sits at $d^{\mathrm{peak}}(0)=(\alpha^2 S_A S_B)^{1/\sigma}$ and \autoref{eq:DPi_peak_v2} reproduces the static-benchmark ceiling: for any technology pair, the Hawk's contest-based electoral advantage is bounded above by $(\sqrt{S_A}-\sqrt{S_B})/(\sqrt{S_A}+\sqrt{S_B})$, which depends only on the ratio $S_A/S_B$ and is structurally independent of how grievance-elastic the Minority is, how large the two populations are, or how the Majority's collective-action problem scales. As the inherited stock $M$ grows toward the threshold $\alpha^2 S_A S_B/\xi$, the peak slides leftward along the $d$-axis: every unit of inherited grievance has substituted one-for-one for a unit of $\sigma$-scaled current provocation, so the Hawk needs less new $d$ to reach the same contest activation. For $M$ above this threshold, the inherited stock alone has pushed the contest past its peak, and any current $d>0$ moves the system into the decreasing branch of the inverted-U. The Hawk's optimum is then the corner $d=0$. This is the technical foundation of the \emph{paradox of restraint} that we encounter again in \autoref{prop:trap_v2}: a sufficiently entrenched Hawk regime governs without enacting visibly new symbolic policy precisely because the stock she manufactured in earlier periods is doing the contest-activation work for her.

A second consequence of \autoref{lem:invU_v2} is that the within-period security gap is strictly positive even at $d=0$ whenever $M>0$. This is the technical micro-foundation for the ``sticky-environment'' reading of the swing-voter equation in \autoref{sec:voter_v2} below.\footnote{The migration of the peak past which further provocation \emph{reduces} the Hawk's advantage has a structural parallel to the cultural-backlash result of \citet{carvalhoKoyamaWilliamsResistingEducation2024}, where increasing top-down institutional transmission of a mainstream cultural trait beyond a threshold can shrink rather than expand the trait's share through compensating bottom-up counter-socialisation. The technical channel differs --- their backlash operates through parental socialisation in a Bisin--Verdier dynamic, ours through Minority resistance effort in a Tullock contest --- but the contested-norm logic is the same.} Even if the Dove takes office and chooses $d_B=0$, the Hawk's $S_A$-advantage remains electorally salient through the inherited stock — a counterfactual that has no analogue in the static benchmark and that rationalises the post-2014 BJP's continued electoral resilience even in periods (e.g.\ around demonetisation) when no headline cattle-ban legislation was being enacted. \autoref{fig:reaction_functions} plots $\Delta\Pi(d;M)$ for several values of $M$, showing the leftward-migrating peak; \autoref{fig:security_premium_empirical} shows the corresponding empirical inverted-U mapping ban intensity to BJP vote share. The proof is in \autoref{app:proof:invU_v2}.

The contest is costly. Following the contest-theory tradition of measuring resource waste by the sum of equilibrium efforts (rent dissipation), define
\begin{equation}\label{eq:RD_closed_form}
    RD(d,S_k;M)\;\equiv\;E_M^*(d,S_k;M)+E_m^*(d,S_k;M)\;=\;\big(1+\alpha\,\hat d^{-\sigma/2}\big)\,E_m^*(d,S_k;M).
\end{equation}

\begin{proposition}[\emph{Rent dissipation with stock}]\label{prop:RD_v2}
\emph{Equilibrium rent dissipation is strictly positive whenever the augmented stake is positive, so contest waste persists even after a Hawk-to-Dove transition through the stock channel alone.}
For any $S_k>0$, $RD(d,S_k;M)>0$ whenever $\hat d^\sigma>0$, i.e.\ whenever either $d>0$ or $M>0$. In particular, even Dove-incumbent regimes ($d_B=0$) at $M>0$ generate strictly positive contest dissipation.
\end{proposition}

\autoref{prop:RD_v2} sharpens the welfare reading of the model. In the static benchmark, switching from Hawk to Dove instantly eliminates the contest's resource cost because $d_B^*=0$ collapses both efforts to zero. With the stock, that immediate cleansing no longer holds: a Dove inheriting $M>0$ continues to bear positive enforcement and resistance effort costs until the stock decays, and \autoref{fig:rent_dissipation_event_study} shows precisely this lagged dissipation pattern in the data. The proposition therefore provides the model-level explanation for the empirically observed persistence of communal violence and economic disruption following political transitions away from Hawkish regimes.

\section{Voter Preferences and Within-Period Election}\label{sec:voter_v2}

Preferences in the Majority electorate are heterogeneous. Voter $i$ derives utility from a weighted combination of physical security and economic consumption, augmented by an idiosyncratic partisan bias. Let $(d,M)$ denote the symbolic-policy environment currently in place: $d$ is fixed by the incumbent at Stage 1 and $M$ is inherited from Stage 4 of the previous period. Together they pin down the joint contest equilibrium that the electorate observes at Stage 3. Within the current election the Minority's accumulated grievance and the resulting equilibrium mobilisation are sticky in $(d,M)$, so voters evaluate each party's security competence at the incumbent's current environment rather than at the policy the challenger would hypothetically choose upon election. The static benchmark assumed this stickiness; the dynamic model micro-founds it through $M$, which is a payoff-relevant state.

The per-period utility from electing party $k\in\{A,B\}$ at the environment $(d,M)$ is
\begin{equation}\label{eq:utility_v2}
    U^k(d;M)\;=\;\lambda\,\Pi_k^*(d,S_k;M)\;+\;(1-\lambda)\,u(\bar g_k)\;-\;\chi_{\mathrm{econ}}(d)\;+\;\mathbb{1}[k=A]\,\xi_i,
\end{equation}
where $\lambda\in(0,1)$ is the fixed weight on security, $u(\cdot)$ is strictly increasing, and $\xi_i$ is an idiosyncratic Hawk-bias drawn from a CDF $\Phi(\cdot)$ with median zero. I decompose the cost of symbolic policy into two economically distinct channels. The \emph{economic-disruption cost} $\chi_{\mathrm{econ}}(d)\ge 0$ captures the real resource cost of identity-based regulation (lost productivity from communal segmentation, trade disruption, misallocation of enforcement capacity) and is borne by every Majority citizen regardless of who wins the next election, because the present environment is what realises the output cost. The \emph{moderate-defection cost} $\chi_{\mathrm{mod}}(d)\ge 0$ captures backlash from moderate Majority voters, lost coalition support, and international-reputation costs. It is treated as a \emph{private} coalition-management cost on the incumbent who provokes --- paid whenever the incumbent chooses $d>0$, regardless of party --- and therefore does not enter voter utility directly. This is the cleanest interpretation of the moderate-defection cost given that in equilibrium only the Hawk provokes ($d_B^\star=0$); on-path the convention is equivalent to specifying the cost on Hawk-incumbency only, but it makes the off-path Dove deviation analysis well-defined. Both functions are continuously differentiable, strictly increasing, strictly convex in $d$, and satisfy $\chi_{\mathrm{econ}}(0)=\chi_{\mathrm{mod}}(0)=0$ with $\lim_{d\uparrow\infty}\chi_{\mathrm{mod}}(d)=\infty$. Crucially, both costs depend only on \emph{current} $d$ and not on inherited $M$: they are direct policy costs, not stock-channel costs.

In the baseline scenario of interest the Hawk is the incumbent and both parties are evaluated at the common environment $(d,M)$. Substituting \autoref{eq:utility_v2}, the indifference condition for the swing voter $\hat\xi(d,M)$ is
\begin{equation}\label{eq:swing_v2}
    \hat\xi(d,M)\;=\;\underbrace{(1-\lambda)\,\Delta u}_{\text{economic deficit}}\;-\;\underbrace{\lambda\,\Delta\Pi(d;M)}_{\text{Security Premium}},
\end{equation}
with $\Delta\Pi(d;M)$ as in \autoref{eq:security_premium_d}. The economic-disruption cost $\chi_{\mathrm{econ}}(d)$ is borne under either continuation as a voter cost and therefore cancels in the comparison; the moderate-defection cost $\chi_{\mathrm{mod}}(d)$ now enters only the incumbent's own value function as a private coalition-management cost and so does not appear in the voter's swing index. This is why the Hawk's strategic margin operates through the swing-voter index $\hat\xi$ rather than through $U^A$ directly. Party $A$ wins if $\Phi(-\hat\xi(d,M))>1/2$.

\begin{remark}[\emph{Microfoundation of the sticky environment}]\label{rem:microfound_v2}
\autoref{lem:invU_v2} delivers the microfoundation of the common-environment reading. At $d=0$ and $M=0$, both parties achieve $\Pi^*=1$, so $\Delta\Pi=0$, the security dimension is electorally invisible, and the voter elects on the economic dimension; the Dove wins whenever $\Delta u>0$. At $d=0$ and $M>0$, $\Delta\Pi(0;M)>0$: the Hawk's $S_A$-advantage is electorally salient \emph{even when no current provocation is enacted}, purely because of inherited grievance. The common-environment reading is therefore not an assumption imposed on the model; it is the within-period equilibrium given inherited $M_{t-1}$, and the inherited stock plays the role of an irreversible regime-locking investment in the sense of \citet{coatePolicyPersistence1999}.
\end{remark}

\section{Baseline Within-Period Analysis}\label{sec:baseline_v2}

The within-period political equilibrium is the subgame-perfect equilibrium of the Stage 1--3 game described above, conditional on the inherited stock $M$ that Stage 4 of the previous period delivered. In the policy stage, the incumbent chooses $d\ge 0$ taking $(S_k,\bar g_k)$ as given party-type characteristics. In the contest stage, joint mobilisation and equilibrium security are determined by \autoref{lem:contest_v2}. In the election stage, the Majority electorate votes on the basis of indirect utilities at the current environment $(d,M)$: the swing-voter threshold \autoref{eq:swing_v2} pins down the re-election probability through the Security Premium of \autoref{lem:invU_v2}. I solve by backward induction, first establishing the Dove's continuation behaviour and then characterising the Hawk's provocation incentive at inherited stock $M$.

\subsubsection*{The Dove's dominant strategy}

The Dove faces a particularly simple optimisation problem. Under the common-environment reading, a positive $d$ simultaneously raises the Security Premium $\Delta\Pi(d;M)$ — which benefits only the Hawk because $S_A>S_B$ — and imposes the moderate-defection cost $\chi_{\mathrm{mod}}(d)$ on the incumbent. Neither force works in the Dove's favour at any inherited stock.

\begin{lemma}[\emph{Dove's dominant strategy}]\label{lem:dove_v2}
\emph{The Dove's unique best response is to set current provocation to zero, regardless of inherited grievance.}
Suppose the Dove is the incumbent at inherited stock $M\ge 0$ and chooses $d_B\ge 0$ to maximise her re-election probability. Under \autoref{eq:utility_v2} and \autoref{eq:swing_v2}, the Dove's unique best response is $d_B^*(M)=0$ for all $M\ge 0$. Consequently, when the Dove is incumbent, current provocation is at the corner; the joint contest is dormant only if additionally $M=0$, and is otherwise sustained purely by the inherited stock.
\end{lemma}

\autoref{lem:dove_v2} has two interpretive consequences. First, the Dove's corner is an endogenous equilibrium outcome rather than a modelling shortcut: the Dove has no stake in activating the security dimension because the underlying state-capacity technology is structurally biased in the Hawk's favour, and any contribution she could make through new $d$ would simultaneously widen the Security Premium against her and bear the moderate-defection cost. Second, this result holds for any $M\ge 0$: a Dove who inherits a high stock from a previous Hawk regime cannot ``unwind'' the contest by enacting counter-symbolic policy; she can only set $d=0$ and wait for $M$ to decay at rate $\rho$ via \autoref{eq:M_evolution_v2}. The post-2014 BJP's continued electoral advantage in periods of relative legislative restraint (and, conversely, the Indian National Congress's inability to undo the post-2014 communal mobilisation) reflect exactly this asymmetry between manufacturing and unwinding the stock. The proof is in \autoref{app:proof:dove_v2}.

\subsubsection*{Strategic provocation by the Hawk}

I now consider the Hawk's incumbency. Under \autoref{lem:dove_v2}, the relevant off-path threat is a Dove at $d_B=0$, and the on-path Hawk chooses $d\ge 0$ to maximise his re-election probability against this benchmark at the inherited stock $M$. The central object is the Hawk's \emph{static surrogate objective} for provocation,
\begin{equation}\label{eq:dubar_v2}
    F(d;M)\;\equiv\;\lambda\,\Delta\Pi(d;M)\;-\;\chi_{\mathrm{mod}}(d),\qquad\overline{\Delta u}(M)\;\equiv\;\tfrac{1}{1-\lambda}\,\max_{d\ge 0}F(d;M),
\end{equation}
which captures the benefit of activating the security gap at the current environment, net of the private coalition-management cost the Hawk bears for doing so. Because the Hawk maximises retention probability $\Phi(-\hat\xi(d,M))$ minus the private cost $\chi_{\mathrm{mod}}(d)$ and $\hat\xi$ is monotone in $-\lambda\,\Delta\Pi(d;M)$, the surrogate $F$ is the relevant within-period objective: it is not a voter-utility difference but the Hawk's retention probability (up to a constant monotone transformation) net of the incumbent's private cost. The next proposition characterises when the Hawk can survive an economic deficit, how the cutoff evolves with inherited grievance, and the substantive new prediction of the model: the optimal current provocation is non-increasing in $M$ and eventually reaches the corner.

\begin{proposition}[\emph{Within-period strategic provocation with stock}]\label{prop:provocation_v2}
\emph{To win in spite of an economic deficit, the Hawk activates the contest by choosing strictly positive symbolic policy on the increasing branch of the inverted-U; the deficit she can offset rises with the inherited stock, but the optimal current provocation falls and eventually vanishes once the stock alone has pushed the contest past its peak.}
Suppose $\chi_{\mathrm{mod}}$ is continuously differentiable on $[0,\infty)$ with $\chi_{\mathrm{mod}}(0)=0$, $\chi_{\mathrm{mod}}'>0$, $\chi_{\mathrm{mod}}''>0$, and $\lim_{d\uparrow\infty}\chi_{\mathrm{mod}}(d)=\infty$. Then:
\begin{enumerate}[label=(\roman*)]
    \item For each $M\ge 0$, $F(\cdot;M)$ attains a finite maximum at some $d_A^*(M)\ge 0$, and $\overline{\Delta u}(M)\ge 0$.
    \item A Hawk victory at inherited stock $M$ is feasible iff $\Delta u\le\overline{\Delta u}(M)$.
    \item The cutoff is non-decreasing in $M$, $\partial\overline{\Delta u}(M)/\partial M\ge 0$, with strict inequality whenever the optimum $d_A^*(M)$ is interior, and is bounded above by the technology ratio
    \begin{equation}\label{eq:dubar_bound_v2}
        \overline{\Delta u}(M)\;\le\;\frac{\lambda}{1-\lambda}\cdot\frac{\sqrt{S_A}-\sqrt{S_B}}{\sqrt{S_A}+\sqrt{S_B}}.
    \end{equation}
    \item The optimal current provocation $d_A^*(M)$ is non-increasing in $M$.
    \item In the deep regime $M\ge\alpha^2 S_A S_B/\xi$, $d_A^*(M)=0$: the Hawk's optimum is the corner with no current provocation (\emph{paradox of restraint}).
\end{enumerate}
\end{proposition}

\autoref{prop:provocation_v2} captures identity politics as a substitute for competence and traces how that substitution evolves with the stock. The Hawk is structurally disadvantaged on economic performance, so she cannot win by competing on the public-good dimension; in a peaceful environment ($d=0$, $M=0$), the underlying contest is dormant and the Hawk's state-capacity advantage is electorally invisible. To survive, she manufactures a threat: by choosing $d_A^*>0$ on the increasing branch of the inverted-U, she activates the joint contest, triggers mobilisation on both sides, and converts her higher $S_A$ into a positive Security Premium. The cutoff $\overline{\Delta u}(M)$ measures the maximum economic deficit voters tolerate in exchange for identity security, and \autoref{eq:dubar_bound_v2} shows that this cutoff is itself bounded above by a monotone function only of the technology ratio $S_A/S_B$ — independent of the convexity of cost, of the two groups' sizes, of the Minority's grievance elasticity, and of the inherited stock. Polities in which the two parties differ strongly in security competence permit a wider wedge of tolerable economic failure, while polities in which the gap is narrow are quickly disciplined by economic shocks.

The novelty of parts (iii)--(v) is the comparative static in $M$. As inherited grievance rises, the marginal return to current provocation falls because the contest is already partially activated by the stock; the Hawk needs less new $d$ to maintain her Security Premium, so $d_A^*(M)$ is non-increasing. Once $M$ exceeds the threshold $\alpha^2 S_A S_B/\xi$, the inherited stock alone has pushed the contest past the peak of the inverted-U, and any further provocation moves the system into the decreasing branch where the Hawk's electoral lead would shrink. The optimum is then exactly $d_A^*(M)=0$. This is the within-period statement of the \emph{paradox of restraint}: a sufficiently entrenched Hawk regime governs without enacting visibly new symbolic policy, not because she has moderated her preferences but because the stock she manufactured in earlier periods is doing the contest-activation work for her. \autoref{fig:cycles_four_panel} shows the corresponding empirical pattern: peak BJP rhetorical and legislative activity around 2014--19, with a discernible plateau in headline cattle-ban legislation in 2020--24 even as cumulative ban intensity (\autoref{fig:policy_cumulative_rollout}) and communal-violence intensity (\autoref{fig:maps}b) remained at their elevated levels. The proof is in \autoref{app:proof:provocation_v2}.

%===================================================================================
% Dynamic Extension — Markov Perfect Equilibrium
%===================================================================================

\section{Dynamic Extension: Markov Perfect Equilibrium} \label{sec:dynamic_v2}

Following \citet{youngEvolutionConventions1993, youngIndividualStrategySocial1998}, I treat the dynamic system as a perturbed Markov process: the deterministic best-response dynamic of \autoref{sec:baseline_v2} is perturbed each period by a salience shock $\omega_t\in[0,\bar\omega]$ — a terror attack, communal incident, or news-of-the-day shock to the contest stake — that is i.i.d.\ across periods and present in every regime. Whether long-run play settles into a self-sustaining conflict equilibrium or oscillates between Hawk and Dove regimes is then a property of the \emph{invariant distribution} of the perturbed chain on $(M_t,k_t)$, and that property is selected by a single structural parameter, the stock-decay rate $\rho$. When the deterministic basin of attraction around the Hawk attractor is deep ($\rho<\bar\rho$), the shocks are absorbed and the system is locked into a stochastically forward-invariant trap. When the basin is shallow ($\rho>\bar\rho$), the same shocks drive ergodic political cycles between Hawk and Dove. The two regimes share the same primitive contest, the same shocks, and the same voter optimisation; they differ only in the depth of the deterministic basin around the Hawk attractor relative to the support of $\omega_t$. The conflict trap and the political-cycle equilibrium of the prior literature thus emerge here as two parameter regions of the \emph{same} perturbed Markov chain — distinguished by a single $\bar\rho$ threshold rather than by an asymmetric assumption on the presence of shocks.

\subsection{State, strategies, and Markov Perfect Equilibrium with persistent shocks}

The state at the start of period $t$ is $(M_t,k_t)\in\mathbb{R}_+\times\{A,B\}$, where $k_t$ is the incumbent inherited from period $t-1$'s election outcome and $M_t$ is the inherited mobilisation stock. The salience shock $\omega_t$ is drawn i.i.d.\ from an absolutely continuous distribution $F$ with full support on $[0,\bar\omega]$ and is realised after the incumbent has committed to her policy: at Stage 1 the incumbent $k_t$ chooses $d_t\ge 0$ as a measurable function of the payoff-relevant state $(M_t,k_t)$ alone; at Stage 2, $\omega_t$ realises and the joint contest plays out at the augmented stake $\hat d_t^\sigma=d_t^\sigma+\xi M_t+\omega_t$, yielding equilibrium efforts $E_m^*(d_t,S_{k_t};M_t,\omega_t)$; at Stage 3 the voter observes the realised tuple $(d_t,M_t,\omega_t,\Pi_{k_t}^*)$ and elects $k_{t+1}$; at Stage 4 the stock updates,
\begin{equation}\label{eq:M_evolution_dyn_v2}
    M_{t+1}\;=\;(1-\rho)\,M_t+\rho\,E_m^*\big(d_t,S_{k_t};M_t,\omega_t\big).
\end{equation}
The within-period analysis of \autoref{sec:baseline_v2} carries through unchanged because the static benchmark sets $\omega=0$; the closed forms of \autoref{lem:contest_v2} apply with $\hat d^\sigma$ defined as above for any realisation $\omega\in[0,\bar\omega]$. A Markov strategy for the incumbent is a measurable function $d_k:\mathbb{R}_+\to\mathbb{R}_+$ specifying provocation at each $M$ if party $k$ holds office; a Markov retention rule for the voter is a measurable function $\rho^v:\mathbb{R}_+\times\{A,B\}\times[0,\bar\omega]\to[0,1]$ specifying the probability of retaining the incumbent at each realised $(M,k,\omega)$. Players discount future payoffs at $\delta\in(0,1)$. The equilibrium concept is Markov Perfect Equilibrium in the sense of \citet{maskinMarkovPerfectEquilibrium2001}: strategies depend only on the payoff-relevant state and on the realised within-period shock, and not on calendar time or history beyond the state.

\begin{definition}[\emph{Markov Perfect Equilibrium}]\label{def:MPE_v2}
A Markov Perfect Equilibrium (MPE) is a tuple $(d_A^\star,d_B^\star,\rho^v,V^v(\cdot,\cdot))$ in which (i) given $\rho^v$ and the law of motion \autoref{eq:M_evolution_dyn_v2}, each $d_k^\star(M)$ is the per-period maximiser of the incumbent's Bellman value taken in expectation over $\omega$; (ii) given $d_A^\star,d_B^\star$, the realisation-conditional retention rule $\rho^v(M,k,\omega)$ implements $\arg\max_{k'\in\{A,B\}}V^v(M',k')$, where $M'$ is the next-period stock under the implied policy and the realised $\omega$; and (iii) $V^v(\cdot,\cdot)$ is the unique fixed point of the Bellman operator on the Banach space of bounded continuous functions.
\end{definition}

I follow the recursive formulation of \citet{acharyaPoliticalAccountabilityMoral2025}, originating in \citet{spearOnRepeatedMoralHazard1987}. Let $V^v(M,k)$ denote the voter's expected discounted utility when the inherited stock is $M$ and the incumbent is $k$, where the expectation integrates over both $\omega$ realisations within the period and continuation play. The Bellman equation is
\begin{equation}\label{eq:bellman_v2}
    V^v(M,k)\;=\;\mathbb{E}_\omega\!\left[U^k(d_k^\star(M);M,\omega)\;+\;\delta\,\big[\rho^v(M,k,\omega)\,V^v(M',k)+(1-\rho^v(M,k,\omega))\,V^v(M',\tilde k)\big]\right],
\end{equation}
where $M'=(1-\rho)M+\rho\,E_m^*(d_k^\star(M),S_k;M,\omega)$ and $\tilde k=B$ if $k=A$ and vice versa. Optimal retention compares regime-specific value functions at the realised $\omega$: the voter retains the incumbent if and only if doing so delivers higher continuation utility \emph{conditional on} the within-period realisation. The relevant comparator is the realisation-conditional voter wedge $V^v(M,A;\omega)-V^v(M,B;\omega)$; integrating over $\omega$ yields the \emph{expected wedge}
\begin{equation}\label{eq:wedge_v2}
    \Phi^M(M)\;\equiv\;\mathbb{E}_\omega\!\left[V^v(M,A;\omega)-V^v(M,B;\omega)\right],
\end{equation}
which is the structural transposition of \citet{padróimiquelControlPoliticiansDivided2007}'s fear-of-exclusion construction to the manufactured-grievance setting: a single scalar that packages voter discounting, incumbency stickiness, and the cross-regime utility gap into one object whose sign — taken in expectation over the within-period shock — determines retention. I impose a regularity restriction on $\Phi^M$ that delivers a clean cutoff retention rule.

\begin{assumption}[\emph{Wedge regularity}]\label{ass:wedge}
The expected voter wedge $\Phi^M(M)\equiv\mathbb{E}_\omega[V^v(M,A;\omega)-V^v(M,B;\omega)]$ is continuous on $[0,\infty)$, satisfies $\Phi^M(0)<0$ and $\lim_{M\to\infty}\Phi^M(M)<0$, and is strictly quasi-concave on $[0,\infty)$.
\end{assumption}

The boundary conditions in \autoref{ass:wedge} are implications of the within-period equilibrium and not free parameters. At $M=0$ and any $\omega\in[0,\bar\omega]$, both equilibrium securities equal one (\autoref{lem:contest_v2}), so the Security Premium is zero, the security dimension is electorally invisible, and the Dove wins on the economic dimension whenever $\Delta u>0$ — hence $\Phi^M(0)<0$ pointwise in $\omega$ and therefore in expectation. As $M\to\infty$, both equilibrium securities approach zero uniformly in $\omega$ on the compact support $[0,\bar\omega]$, the Security Premium vanishes again, and the Dove's economic advantage dominates — hence $\lim_{M\to\infty}\Phi^M(M)<0$. The strict quasi-concavity of $\Phi^M$ is the only primitive imposed for tractability; it holds in canonical parameterisations (linear $u$, quadratic $\chi_{\mathrm{econ}}$ and $\chi_{\mathrm{mod}}$) and emerges from the inverted-U structure of $\Delta\Pi$ combined with the migrating peak $d^{\mathrm{peak}}(M)$ of \autoref{lem:invU_v2}, evaluated along the Hawk's reaction function $d_A^*(M)$.\footnote{Concretely, condition (iii) is a property of the composed mapping $M\mapsto\mathbb{E}_\omega[\Pi_A^*(d_A^*(M),S_A;M,\omega)-\Pi_B^*(0,S_B;M,\omega)]$, not of $\Pi_k^*(\cdot,S_k;M,\omega)$ at fixed $d$ (which is monotone decreasing in $M$ for each $\omega$ by \autoref{lem:contest_v2}). The single-peakedness is preserved by the Bellman operator on bounded continuous functions and by the expectation over $\omega$ under bounded full-support $F$; I impose \autoref{ass:wedge} directly to avoid restricting the model to specific parametric forms.}

\begin{lemma}[\emph{Concavity and single-crossing of the expected wedge}]\label{lem:wedge_v2}
\emph{The voter's expected preference for the Hawk over the Dove is positive on a single (possibly degenerate) interval of inherited grievance, with a unique smallest grievance level at which retaining the Hawk becomes weakly preferred in expectation.}
Under the regularity conditions of \autoref{prop:provocation_v2} and \autoref{ass:wedge}: (i) $V^v(\cdot,A)$ and $V^v(\cdot,B)$ are continuous and uniformly bounded on $[0,\infty)$ in expectation over $\omega$; (ii) $\mathbb{E}_\omega[V^v(M,B;\omega)]$ is non-increasing in $M$, since under the Dove $d_B=0$ and higher inherited grievance is unambiguously bad for per-period payoff at every $\omega$ with recovery awaiting decay; (iii) the expected wedge $\Phi^M(M)$ is single-crossing, with a unique $\bar M\in(0,\infty]$ such that $\Phi^M(M)<0$ for $M<\bar M$, $\Phi^M(M)\ge 0$ on a closed interval $[\bar M,\overline M^+]$, and $\Phi^M<0$ for $M>\overline M^+$. The lower threshold $\bar M$ governs the conflict-trap region.
\end{lemma}

\begin{remark}[\emph{Primitive sufficient conditions for wedge regularity}]\label{rem:wedge_primitive}
\autoref{ass:wedge} is satisfied as a primitive whenever the expected per-period gap $\mathbb{E}_\omega[U^A(d_A^*(M);M,\omega)-U^B(0;M,\omega)]$ is strictly quasi-concave in $M$. Sufficient conditions are: (i) $u(\cdot)$ linear; (ii) $\chi_{\mathrm{econ}},\chi_{\mathrm{mod}}$ quadratic; (iii) $F$ absolutely continuous with bounded support; and (iv) the composite mapping $M\mapsto\mathbb{E}_\omega[\Pi_A^*(d_A^*(M),S_A;M,\omega)-\Pi_B^*(0,S_B;M,\omega)]$ — the expected Security-Premium gap evaluated along the Hawk's reaction function on the Hawk side and at $d_B=0$ on the Dove side — single-peaked in $M$. The single-peakedness of the composed gap emerges from the inverted-U structure of $\Delta\Pi$ combined with the migrating peak of \autoref{lem:invU_v2}, and it is preserved by the Bellman operator on bounded continuous functions and by integration against $F$.
\end{remark}

The expected wedge $\Phi^M$ inherits the inverted-U geometry of the within-period gap and folds in the voter's discounted continuation values, integrated over the within-period shock. Below $\bar M$, the Dove's economic edge $\Delta u$ dominates the small expected Security Premium that the inherited stock alone can support, so the voter prefers the Dove in expectation; above $\bar M$, the inherited stock is large enough that the Hawk's $S_A$-driven security advantage outweighs the economic gap on average; for sufficiently large $M$, both equilibrium securities collapse and the economic dimension dominates again. The lemma's substantive content is therefore that the voter's expected regime preference has a single-peaked structure in inherited grievance, and the cutoff $\bar M$ is the smallest grievance level at which the Hawk's expected continuation value matches the Dove's. The proof is in \autoref{app:proof:wedge_v2}.

\begin{proposition}[\emph{Cutoff retention rule}]\label{prop:cutoff_v2}
\emph{The voter retains the Hawk above a state-and-shock-dependent grievance cutoff and the Dove below a generically lower cutoff; in the intervening hysteresis interval, retention depends on the identity of the current incumbent.}
Define the realisation-conditional wedge $\Phi^M(M,\omega)\equiv V^v(M,A;\omega)-V^v(M,B;\omega)$ and the realisation-conditional cutoff $\bar M(\omega)\equiv\inf\{M:\Phi^M(M,\omega)\ge 0\}$. A Markov retention rule $\rho^v$ is part of an MPE if and only if there exist functions $\underline M(\omega)\le\bar M(\omega)$ such that
\begin{equation}\label{eq:retention_v2}
    \rho^v(M,A,\omega)\;=\;\mathbbm{1}[M\ge\bar M(\omega)],\qquad\rho^v(M,B,\omega)\;=\;\mathbbm{1}[M\le\underline M(\omega)],
\end{equation}
with $\underline M(\omega)=\sup\{M:\Phi^M(M,\omega)\le 0\}$. Generically (in $\rho$), $\underline M(\omega)<\bar M(\omega)$ for almost every $\omega$, and the realisation-conditional interval $[\underline M(\omega),\bar M(\omega)]$ is the \emph{hysteresis region}. Define the worst-case retention cutoff $\bar M^*\equiv\sup_{\omega\in[0,\bar\omega]}\bar M(\omega)$, the smallest $M$ at which the Hawk is retained for \emph{every} realised shock.
\end{proposition}

\autoref{prop:cutoff_v2} is the dynamic counterpart of the within-period swing-voter equation: it converts the realisation-conditional wedge $\Phi^M(\cdot,\omega)$ into an $\omega$-measurable retention rule, and the resulting hysteresis interval is the \citet{coatePolicyPersistence1999} mechanism transposed to the manufactured-grievance setting. The two thresholds coincide only when $\rho=1$ (full instantaneous decay), in which case the dynamic problem collapses; for any $\rho<1$ the hysteresis interval has positive width almost surely, and the same inherited stock $M\in[\underline M(\omega),\bar M(\omega)]$ supports retention of either incumbent depending on which party currently holds office. The worst-case cutoff $\bar M^*$ is the relevant scalar for the trap result: at $M\ge\bar M^*$ the Hawk is retained no matter which $\omega$ realises, so the realisation-conditional retention rule reduces almost surely to a deterministic one. This is precisely the asymmetry that powers the regime-locking results below: a Hawk who manufactures her way above $\bar M^*$ is retained even at stock levels at which a hypothetical Dove incumbent at the same $M$ would have been ejected, and even at the worst possible draw of the persistent shock.

\begin{proposition}[\emph{Existence of pure-strategy MPE}]\label{prop:MPE_v2}
\emph{A pure-strategy Markov Perfect Equilibrium exists in which the Dove plays the corner, the Hawk's policy reflects both the within-period electoral return and a forward-looking stock-building incentive, and voters apply the cutoff retention rule of \autoref{prop:cutoff_v2}.}
Under \autoref{ass:wedge} and the regularity conditions of \autoref{prop:provocation_v2}, a pure-strategy MPE $(d_A^\star,d_B^\star,\rho^v)$ exists with $d_B^\star(M)=0$ for all $M\ge 0$, the cutoff retention rule \autoref{eq:retention_v2}, and the Hawk's policy $d_A^\star(M)$ solving the dynamic first-order condition
\begin{equation}\label{eq:dyn_FOC}
    \mathbb{E}_\omega\!\left[\underbrace{\lambda\,\tfrac{\partial\Delta\Pi(d;M,\omega)}{\partial d}\Big|_{d=d_A^\star(M)}-\chi_{\mathrm{mod}}'(d_A^\star)}_{\text{within-period FOC}}\;+\;\underbrace{\delta\,\tfrac{\partial V^v(M',A)}{\partial M'}\,\tfrac{\partial M'}{\partial d}\Big|_{d=d_A^\star(M)}}_{\text{stock-building incentive}}\right]\;=\;0,
\end{equation}
where $M'=(1-\rho)M+\rho\,E_m^*(d,S_A;M,\omega)$. In the deep regime $M\ge\alpha^2 S_A S_B/\xi$, the dynamic optimum is the corner $d_A^\star(M)=0$ for almost every $\omega$. The voter value functions are the unique fixed point of the Bellman operator on the Banach space of bounded continuous functions on $[0,\infty)$.
\end{proposition}

The forward-looking dynamic optimum departs from the within-period optimum of \autoref{prop:provocation_v2} only by the stock-building term in \autoref{eq:dyn_FOC} and by the expectation over $\omega$. Both first-order conditions operate on the swing-voter index $F(d;M,\omega)=\lambda\Delta\Pi(d;M,\omega)-\chi_{\mathrm{mod}}(d)$ rather than on $U^A(d;M,\omega)$ directly: the Hawk maximises retention probability, not absolute utility, and $\chi_{\mathrm{econ}}(d)$ cancels in the within-period $U^A-U^B$ comparison at common $d$. Because current provocation accumulates future grievance ($\partial M'/\partial d>0$ for every $\omega$), the stock-building term is positive whenever the next-period state $M'$ lies on the increasing branch of the Hawk-incumbent value function, and negative whenever $M'$ lies on the decreasing branch. In the increasing region the forward-looking Hawk strategically over-provokes relative to a hypothetical one-shot myopic Hawk, $d_A^\star(M)>d_A^*(M)$; in the decreasing region she under-provokes, $d_A^\star(M)<d_A^*(M)$. The expectation over $\omega$ smooths these terms but does not change their sign. In the deep paradox-of-restraint regime $M\ge\alpha^2 S_A S_B/\xi$, the within-period margin is globally non-positive at every $\omega$ (\autoref{lem:invU_v2}) and no positive stock-building term can override it; the dynamic optimum is the corner. The Dove's corner $d_B^\star=0$ persists in the dynamic equilibrium because $S_B<S_A$ implies the stock-building incentive works \emph{against} the Dove: any positive $d_B$ would raise $M'$, which raises the Hawk's continuation lead, which raises the probability of regime change against the Dove. The proof is in \autoref{app:proof:MPE_v2}.

\subsection{The deterministic drift, the bifurcation, and basins of attraction}\label{sec:drift_v2}

The unifying object across the two long-run regimes is the \emph{deterministic drift} of the stock, taken in expectation over the within-period shock. Under Hawk incumbency,
\begin{equation}\label{eq:drift_v2}
    \bar\Psi_A(M;\rho)\;\equiv\;(1-\rho)\,M+\rho\,\mathbb{E}_\omega\!\left[E_m^*\big(d_A^\star(M),S_A;M,\omega\big)\right],
\end{equation}
the expected next-period stock starting from $M$. The map $\bar\Psi_A(\cdot;\rho)$ is the deterministic skeleton of the perturbed Markov chain on $(M_t,k_t)$: each period's stock update is $M_{t+1}=\bar\Psi_A(M_t;\rho)+\eta_t$ where $\eta_t=\rho\,(E_m^*(\cdot,\omega_t)-\mathbb{E}_\omega E_m^*(\cdot))$ is a mean-zero perturbation whose amplitude scales with $\rho$.

This last observation is the conceptual key. The per-period jump $M_{t+1}-M_t=\rho\,(E_m^*(d_t,S_{k_t};M_t,\omega_t)-M_t)$ is proportional to $\rho$: the stock-decay rate, viewed from the perturbed-Markov-chain perspective, plays the role of Young's noise parameter $\epsilon$. As $\rho\to 0$, the chain is approximately deterministic and stays at whatever attractor of $\bar\Psi_A$ it began near; persistent shocks $\omega_t$ enter the per-period payoffs but barely move $M_t$, because the integration weight on the new draw is small. As $\rho\to 1$, by contrast, the chain has full per-period noise and mixes freely across the state space; the deterministic skeleton vanishes and the invariant distribution is determined by the full $F$. The bifurcation parameter $\rho$ thus governs the \emph{effective amplitude} of the noise in the stock dynamics, even though the primitive shock distribution $F$ is held fixed throughout.

The fixed points of $\bar\Psi_A(\cdot;\rho)$ are roots of $\rho\,(\mathbb{E}_\omega E_m^*(d_A^\star(M),S_A;M,\omega)-M)=0$, i.e., points at which the expected adversary effort just replaces the inherited stock at the Hawk's optimum policy. Standard bifurcation analysis (see, for example, \citealp{youngIndividualStrategySocial1998}, ch.~3) shows that as $\rho$ varies, the map $\bar\Psi_A(\cdot;\rho)$ undergoes a saddle-node bifurcation: for $\rho$ small, $\bar\Psi_A$ has a high stable fixed point above the worst-case retention cutoff $\bar M^*$, separated from a low unstable fixed point by an absorbing basin; for $\rho$ large, the high fixed point and the unstable separatrix collide and disappear, leaving a single low attractor below $\bar M^*$. The threshold $\bar\rho$ is implicitly defined by the condition that the deterministic basin around the high attractor just collapses to the worst-case cutoff $\bar M^*$.

A non-empty stochastically forward-invariant set $\mathcal T\subseteq\mathbb R_+$ exists when the realisation-conditional drift remains non-negative throughout $\mathcal T$ uniformly over the shock support: $\inf_{M\in\mathcal T,\,\omega\in[0,\bar\omega]}\big[\rho\,(E_m^*(d_A^\star(M),S_A;M,\omega)-M)\big]\ge 0$ at the lower boundary $\inf\mathcal T$. This is the discrete-time analogue of the Foster–Lyapunov absorption condition (\citealp{meynMarkovChainsStochastic2009}, Ch.~14–15): with Lyapunov function $V(M)=\bar M^*-M$ on $\mathcal T$, the condition reads $\Delta V(M)\le 0$ pointwise on $\partial\mathcal T$, which prevents the chain from leaving $\mathcal T$ almost surely. When the same condition fails — the drift on $\partial\mathcal T$ becomes negative under at least some realisations — the chain escapes the would-be trap on a positive-measure event, and the question becomes whether the resulting unconstrained chain is ergodic. The two questions — absorption vs.\ ergodicity — turn on the same primitive object, the realisation-conditional drift evaluated at the worst-case retention cutoff, and they admit a unified phase-transition characterisation.

\subsection{The phase transition: trap and cycles as basins of the same chain}\label{sec:phase_v2}

The central new theoretical contribution of the dynamic extension is a unified proposition that subsumes the conflict trap and the political-cycle equilibria as two parameter regimes of a single perturbed Markov process.

\begin{proposition}[\emph{Phase transition: trap and cycles}]\label{prop:phase_transition}\label{prop:trap_v2}\label{prop:cycles_v2}\label{prop:cs_v2}
\emph{There exists a threshold $\bar\rho\in(0,1)$ on the stock-decay rate, depending on model primitives, such that the long-run dynamics of the perturbed Markov chain $(M_t,k_t)$ exhibit two qualitatively different regimes — a stochastically forward-invariant Hawk trap when the deterministic basin is deep, and ergodic Hawk--Dove cycles when the basin is shallow — selected by $\rho$ alone with the shock primitive $\omega_t$ held fixed throughout.}

\smallskip
\noindent\textbf{(i) Trap regime ($\rho<\bar\rho$).} The set $\mathcal T^*\equiv\{(M,A):M\ge\bar M^*\}$, where $\bar M^*=\sup_{\omega\in[0,\bar\omega]}\bar M(\omega)$ is the worst-case retention cutoff of \autoref{prop:cutoff_v2}, is stochastically forward-invariant: starting from any $(M_0,A)\in\mathcal T^*$, the orbit satisfies $(M_t,k_t)\in\mathcal T^*$ for all $t\ge 0$ almost surely under the i.i.d.\ shock distribution $F$.\footnote{An alternative sufficient condition for the trap regime is the radius--coradius criterion of \citet{ellisonLearningLocalInteraction1993}: if the radius $R(\mathcal T^*)$ --- the minimum cumulative shock magnitude required to escape the trap --- exceeds the coradius $CR(\mathcal T^*)$ --- the minimum cumulative shock magnitude required to enter from outside --- then the trap is the unique stochastically stable class of the underlying perturbed Markov chain. In our setting, $R$ and $CR$ are computable from the within-period transition probabilities $\pi_{AD},\pi_{DA}$ of \autoref{prop:phase_transition}(ii), so the criterion is equivalent in content to Foster--Lyapunov drift but may yield a sharper bound on $\bar\rho$ in specific parametric examples.} Within the trap, the equilibrium policy converges to a stationary level $d_A^\infty\ge 0$ — with $d_A^\infty=0$ in the deep regime $M^\infty\ge\alpha^2 S_A S_B/\xi$ (paradox of restraint) — and the Hawk is retained in every period. The trap threshold $\bar M^*$ satisfies the comparative statics
\begin{equation}\label{eq:cs_signs_v2}
    \tfrac{\partial\bar M^*}{\partial\rho}>0,\qquad\tfrac{\partial\bar M^*}{\partial(S_A/S_B)}<0,\qquad\tfrac{\partial\bar M^*}{\partial\lambda}<0,\qquad\tfrac{\partial\bar M^*}{\partial\Delta u}>0.
\end{equation}

\smallskip
\noindent\textbf{(ii) Cycles regime ($\rho>\bar\rho$).} The chain $(M_t,k_t)$ is $\phi$-irreducible, aperiodic, and Harris-recurrent on a compact state-space subset that intersects both $\{k=A\}$ and $\{k=B\}$. The unique invariant distribution $\pi^*$ has $\pi^*(\{k=A\})\in(0,1)$ and $\pi^*(\{k=B\})\in(0,1)$; both Hawk-to-Dove and Dove-to-Hawk transitions occur with positive probability in every period along the realised path; and the realised regime sequence is recurrent in the sense that each regime is visited infinitely often almost surely. The hazard of a Hawk-to-Dove transition is increasing in $\omega_t$-driven declines in observed disorder (paradox of competence).

\smallskip
\noindent The same shock primitive $\omega_t$ drives both regimes; the regime is selected by $\rho$ alone, not by the presence or absence of shocks.\footnote{Because $M_t$ is continuous and $\omega_t$ has fixed support, classical stochastic-stability arguments — which take the noise to zero — do not apply directly to our setting. We instead invoke the Foster–Lyapunov drift criterion of \citet[Ch.~14–15]{meynMarkovChainsStochastic2009}, which characterises ergodicity of continuous-state Markov chains under fixed-amplitude perturbations. The conceptual content of the result is the same as in \citet{youngEvolutionConventions1993}: a deep enough deterministic attractor absorbs the chain; a shallow one does not.}
\end{proposition}

\autoref{prop:phase_transition} delivers the model's answer to the introduction's central puzzle — why some polities exhibit durable one-party Hawk dominance while others exhibit recurrent turnover — through a single primitive. The bifurcation interpretation makes the unified mechanism transparent: as $\rho$ increases through $\bar\rho$, the high Hawk attractor of the deterministic drift $\bar\Psi_A$ becomes shallower until the basin can no longer absorb shocks of magnitude up to $\bar\omega$. Below $\bar\rho$, the within-period value gap $\Phi^M(M)$ at $M=\bar M^*$ is so large that even the worst draw of $\omega$ cannot push the chain across the basin boundary — the trap absorbs every shock realisation. Above $\bar\rho$, the boundary lies inside the active range of the shock support, and a positive-measure set of $\omega$ realisations triggers a Hawk-to-Dove transition in finite time. The same $\omega_t$ that the trap regime absorbs as background noise becomes, in the cycles regime, the driver of regime change. \autoref{fig:phase_transition} illustrates the two regimes graphically: panel (a) shows that the per-period shock band scales with $\rho$ — narrow and contained above $\bar M^*$ in the trap regime, wide and straddling the cutoff in the cycles regime — and panel (b) traces simulated $(M_t,k_t)$ sample paths under common shocks, with the trap path locked into the Hawk-attractor neighbourhood and the cycles path oscillating between Hawk and Dove regimes via cutoff-crossing transitions.

The empirical mapping is symmetric across the two regimes precisely because the shock primitive is held common. India under post-2014 BJP, Iran since the Islamic Revolution, and Hungary under Fidesz feature long-half-life communal grievance stocks (low $\rho$), large security-competence gaps (high $S_A/S_B$), and culturally salient security dimensions (high $\lambda$); all three fall in regime (i), and the post-2019 BJP plateau in headline cattle-ban legislation alongside sustained electoral majorities is the paradox-of-restraint signature predicted within the trap. The post-Trump United States, post-Uribe Colombia, and post-2010 Israel under Likud feature faster news-of-the-day-driven turnover (high $\rho$), narrower security-competence gaps, and macroeconomic shocks that drive electoral outcomes; all three fall in regime (ii). The same primitive $\omega_t$ — terror attacks, border crises, communal incidents, news cycles — is present in all six settings; what differs across settings is the structural parameter $\rho$ that determines how deeply each polity's stock dynamics absorb the persistent shock.

The paradox of competence emerges naturally as a within-equilibrium consequence of regime (ii) and is stated separately as a corollary because it is a property of the realised sample path, not of the invariant distribution. In the cycles regime, low realised disorder under the Hawk shifts the voter's posterior toward a benign threat environment, reduces the perceived Security Premium, and raises the probability that the voter switches to the Dove. A more successful Hawk therefore looks less necessary in equilibrium: quieter streets shrink the perceived Security Premium and increase the realised Hawk-to-Dove transition hazard. \autoref{fig:paradox_of_competence} documents precisely this pattern in the IHDS-II micro-data: BJP retention probabilities at the constituency level are inverted-U in the contemporaneous communal-violence intensity, with the highest hazard of Hawk defeat exactly in those constituencies where the Hawk had been most successful at suppressing observable disorder. \autoref{fig:cycles_four_panel} shows the corresponding macro-level pattern in Iran, with Reformist administrations following Principalist ones precisely after periods of relative domestic calm, and \autoref{fig:rent_dissipation_event_study} traces the lagged dissipation that follows each Hawk-to-Dove transition.

\begin{corollary}[\emph{Paradox of competence}]\label{cor:paradox_v2}
\emph{In the cycles regime, a stochastic decrease in observed disorder under a Hawk incumbent weakly raises the Hawk's defeat hazard — successful security delivery erodes the very Security Premium that justifies retention.}
Under $\rho>\bar\rho$, a first-order stochastic decrease in observed disorder $\tilde v_t=(1-\Pi_{k_t}^*)+\varepsilon_t^v$ under a Hawk incumbent weakly decreases the perceived Security Premium and weakly increases the realisation-conditional hazard of a Hawk-to-Dove transition.
\end{corollary}

The proofs of \autoref{prop:phase_transition} and \autoref{cor:paradox_v2} are in \autoref{app:proof:trap_v2}, \autoref{app:proof:cycles_v2}, \autoref{app:proof:cs_v2}, and \autoref{app:proof:paradox_v2}: part (i) is the Foster–Lyapunov absorption argument applied to the worst-case cutoff $\bar M^*$, part (ii) verifies the three Meyn–Tweedie conditions (irreducibility from the absolute continuity of $F$; aperiodicity from the same; drift from the contractive structure of the stock equation), and the comparative statics are obtained from the implicit-function theorem applied to $\Phi^M(\bar M^*;\theta)=0$ at the worst-case shock realisation.

The phase-transition result rests on three parameter conditions visible in the comparative statics of \autoref{eq:cs_signs_v2}.\label{sec:scope_v2} First, the mobilisation stock must decay slowly, $\rho<\bar\rho$, for the trap to absorb the shocks; for $\rho>\bar\rho$ the system enters the cycles regime. Second, the Hawk's security advantage $S_A/S_B$ must be sufficiently large relative to the Dove's economic advantage $\Delta u$, otherwise $\bar M^*=\infty$ and no trap region exists. Third, voters must be sufficiently forward-looking; under full myopia the within-period retention condition reduces to a current-payoff comparison that flips with any sufficiently adverse $\omega_t$ realisation, and the trap collapses into cycles even at low $\rho$. The case $\rho=\bar\rho$ is a knife-edge bifurcation point at which small parameter perturbations switch regimes, so empirical work near this boundary cannot identify the regime from a single panel realisation. The two long-run regimes have distinct empirical signatures: the trap predicts low Hawk turnover, electoral resilience to severe economic and security shocks, and the paradox of restraint in the mature phase; the cycles regime predicts turnover responsive to disorder shocks and the paradox of competence. The Indian cattle-ban setting, with its long-half-life communal grievance dynamics and the institutional permanence of state-level legislation, should be governed by the trap mechanism --- a prediction consistent with post-2014 BJP retention through demonetisation and the COVID-era recession. The Bayesian microfoundation of \autoref{lem:bayes_v2} tightens this polity-level mapping: India, Iran, and Hungary are jointly high-$\xi$ \emph{and} low-$\rho$ rather than independently so, because both parameters reflect the same underlying information-flow regime --- a sharp prior on regime hostility ($\tau_M$ high) and slow decay of the empirical mobilisation stock are two consequences of a polity whose institutional memory keeps past grievance episodes informationally alive.


\section{Conclusion}\label{sec:conclusion}

The puzzle that motivated this paper is why political groups manufacture grievances against domestic minorities, why voters reward them in some polities and punish them in others, and why the same instrument can produce both durable one-party dominance and recurrent regime turnover. I have developed a model in which a single primitive --- the incumbent's choice of symbolic-policy intensity, which sets the stake of a two-sided contest with an accumulating mobilisation stock --- generates both the conflict trap and political cycles as parameter regions of one perturbed Markov chain, with the structural decay rate $\rho$ as the bifurcation parameter that selects between them. Communal politics is a highly complex phenomenon; I do not pretend to understand it completely, nor do I suggest that economic competence, ideology, or expressive group identity play no role. I hope, however, that the framework offers one useful mechanism for the contemporary politics of manufactured grievance.

The model has direct implications for policy, but they are not the obvious symmetric ones. Average treatment effects on Hawk vote share or on Minority mobilisation depend on the underlying stability of the norms in place: muted in deep-trap settings where the contest stock is robust to single-period shocks, exaggerated in cycles settings where small interventions can trigger cascading regime shifts.\footnote{This is the same cultural-backlash logic that \citet{carvalhoKoyamaWilliamsResistingEducation2024} document in the cultural-transmission setting, where blunt top-down interventions can entrench the very norms they target.} An apparent counter-intervention --- revoking cattle-ban legislation, for example --- need not produce the symmetric reverse effect on communal violence, because the mobilisation stock decays at its own rate $\rho$ that does not respond to formal-policy reversal alone. I suggest, then, that attempts to regulate manufactured grievance can turn out to be counterproductive, regardless of whether they are motivated by majoritarian or minority-protective objectives. The disconnect between micro-motives and macro-outcomes runs from Schelling's segregation model to the documentation of pluralistic ignorance about Saudi gender norms, and it is the same disconnect at work here.

Three extensions strike me as especially fruitful. The first is to relax the non-voting-Minority assumption: with strategic Minority turnout, the swing-voter equation becomes a weighted average over Majority and Minority bloc preferences, and the trap-cycles partition shifts in ways that interact with the comparative-advantage gap. The second is to endogenise state capacity, treating the security and economic capacity parameters as functions of past investments, so that the incumbent's problem becomes a joint policy-and-investment programme --- the natural framework for the bureaucratic capture that empirically accompanies long Hawk incumbencies. The third is to generalise to multi-incumbent politics, in which the contest is over which Hawk among several governs --- the natural framework for primaries and intra-coalition competition within the broad Hindu-nationalist or US Republican movements. Finally, I believe the framework introduced here --- manufactured grievance as the stake of a two-sided contest with a slow-decaying mobilisation stock, embedded in a perturbed Markov process whose long-run regime is selected by a structural information-flow parameter --- may yield broader insights for the study of ethnic and religious conflict in electoral democracies, where the lines between top-down policy and bottom-up mobilisation are continuously contested.


%===================================================================================
% References, Figures, Tables (input from existing files)
%===================================================================================

\clearpage
\newpage
\singlespacing
\footnotesize
\bibliographystyle{aer}

\begingroup
\bibliography{ref}
\endgroup

\normalsize
\clearpage
\section{Figures}
\input{figures}

\clearpage
\section{Tables}
\input{tables}

%===================================================================================
% APPENDIX A: More on Empirical Facts (inline copy from appendix_empirical.tex)
%===================================================================================
\appendix
\renewcommand{\thesection}{\Alph{section}}
\renewcommand{\thesubsection}{\Alph{section}.\arabic{subsection}}
\renewcommand{\thetable}{A.\arabic{table}}
\renewcommand{\thefigure}{A.\arabic{figure}}
\setcounter{table}{0}
\setcounter{figure}{0}

\section{More on Empirical Facts} \label{app:more_empirical_facts}

\subsection{Data Sources} \label{app:data_sources}

\autoref{tab:data_sources} catalogues every dataset used in
Section~\ref{sec:empirical_facts}, together with the unit of observation,
coverage window, and retrieval date.

\subsection{Composite Ban-Intensity Index} \label{app:ban_intensity}

The composite ban intensity for state~$s$ in year $t$ is
\begin{equation*}
\text{BanIntensity}_{s,t}
\;=\;\sum_{b\in\mathcal{B}} \max\!\big(t-\tau_{s,b},\,0\big),
\end{equation*}
where $\mathcal{B}=\{\text{cow slaughter, bull slaughter, bullock slaughter,
buffalo slaughter, beef possession, beef sales}\}$ is the set of six ban
types and $\tau_{s,b}$ is the year in which state~$s$ first enacted a ban of
type~$b$. A state that never enacts ban~$b$ has $\tau_{s,b}=\infty$ and the
corresponding term is zero. The cumulative map uses the
1990--2020 annual average of this panel.

The underlying policy panel was constructed from state-level legislative
records compiled in the Cattle Slaughter Policy Excel file. Because a handful of states --- Bihar, Chandigarh,
Punjab --- had early, near-contemporaneous adoption of multiple ban types
before~1990, their 1990--2020 average is bounded near the theoretical
maximum; the index compresses cross-state variation at the top end. Results
are qualitatively identical with a binary indicator or with a
count-of-ban-types-in-force metric.

\input{appendix_tables}

\subsection{Narrative Classification Methodology} \label{app:narrative_classification}

\textbf{Corpus.} The majority-side corpus comprises three stacked sources
totalling $3{,}328$ rows: (i)~$2{,}066$ BJP-leadership speeches from
\texttt{bjp.org/speeches} ($2000$--$2025$), filtered to post-2014 dates for
the main-text figure; (ii)~$1{,}500$ Prime-Ministerial speeches harvested
from \texttt{pmindia.gov.in/en/news\_updates} (Nov~$2020$--Apr~$2026$), used
as a supplement during the pmindia fallback window (the primary target
\texttt{narendramodi.in} was unreachable); (iii)~$406$ BJP Lok Sabha floor
speeches and~$9$ AIMIM floor speeches harvested from the official DSpace
backend at \texttt{elibrary.sansad.in} ($1996$--$2024$), filtered to
single-speaker debate items with word-count $\geq 50$. The Lok Sabha
supplement fills the pre-$2014$ period in which the party-website archive
is sparse (fewer than~$35$ items $1996$--$2013$) and introduces
parliamentary-register content alongside the campaign-register bjp.org
corpus. AIMIM Lok Sabha speeches (Asaduddin~Owaisi, Imtiaz~Jaleel) are
assigned to the minority-side corpus. Speakers in the main corpus include
the Prime Minister and the four BJP National Presidents of the period; the
top seven speakers in the parliamentary supplement are Arun~Jaitley,
Sushma~Swaraj, Rajnath~Singh, Narendra~Modi, Nitin~Gadkari,
Asaduddin~Owaisi, and Amit~Shah. The minority-side corpus comprises
$3{,}792$ items ($3{,}783$~news-outlet snippets and~$9$~AIMIM Lok~Sabha
floor speeches) from a $65$-query Google News RSS harvest, $2010$--$2025$.
Queries cover AIMIM/Owaisi, Jamiat Ulama-i-Hind, AIMPLB, cow-related
lynchings (Akhlaq~2015, Pehlu~Khan~2017, Junaid~2017, Tabrez~2019), Shaheen
Bagh/CAA/NRC, hijab, Waqf, Uniform Civil Code, Gyanvapi, Babri~Masjid,
Bilkis~Bano, and Kashmir Muslim leadership. Outlets include The~Hindu, The
Times of India, NDTV, India~Today, Indian Express, Scroll, The~Wire,
Maktoob, SabrangIndia, Muslim Mirror, Al~Jazeera, and the BBC.

\textbf{Asymmetry in primary-source availability.} A primary-source Muslim
corpus analogous to \texttt{bjp.org/speeches} was not feasible: as of
April~2026, \texttt{aimim.in} fails to resolve; \texttt{jamiatulama.org}
resolves to a parked lander; \texttt{aimplboard.in} retains a static
early-2000s site whose press-release endpoint returns HTTP~500. The
minority-side corpus is therefore a curated press proxy rather than a
like-for-like speech archive. This asymmetry is documented in the main text
(\S\ref{subsec:d_narrative}) and treated as a data fact rather than a
nuisance.

\textbf{Classification.} Each text is classified by Claude Haiku~4.5
(\texttt{claude-haiku-4-5}) into one of four (majority) or five (minority)
mutually exclusive categories using a structured system prompt pinned to the
theoretical primitives. Majority categories are \textsc{identity\_policy},
\textsc{economic\_provision}, \textsc{security\_foreign}, and
\textsc{residual}; minority categories add \textsc{counter\_mobilization}
to capture collective-response content distinct from threat-and-event
content. Texts are truncated to the first $500$ words to bound per-call
input tokens; the pinned system prompt is cached via Anthropic's ephemeral
prompt cache so that each call pays cache-read rates on the prompt and full
rates only on the unique text. A keyword-lexicon fallback is maintained for
robustness; the lexicon overlaps the Haiku category boundaries on the
high-$d$ cases and diverges on polysemous tokens (e.g., ``conversion,''
``dharma,'' ``border'') on which Haiku is substantially sharper. The two
system prompts (one per side, both cached) are reproduced verbatim below;
the user-message payload for each row is the concatenation of the title,
date, and first-$500$-word body.

\begin{quote}\footnotesize
\noindent\textbf{Majority system prompt.}\\[0.3em]
You are classifying speeches and press coverage from Indian political
discourse for an academic political-economy paper. The paper models a
security-oriented majority party's use of symbolic policy ($d$) to
manufacture a minority threat and thereby offset its comparative economic
disadvantage. You will classify each text into exactly ONE category based
on which theoretical primitive the text is primarily supplying content to.
Return ONLY the single label in UPPERCASE, nothing else.

\smallskip
Categories for MAJORITY texts (BJP leadership speeches, PM addresses,
parliamentary BJP speeches):

\begin{itemize}[leftmargin=1.2em, itemsep=0.15em, topsep=0.2em]
\item \textsc{identity\_policy}: text advancing, defending, enforcing, or
reasoning about identity-coded regulation or Hindu--Muslim relations.
Concretely: beef/cow slaughter bans, CAA/NRC, love jihad, ghar wapsi,
Ayodhya/Ram Mandir, Gyanvapi, UCC, waqf, triple talaq, hijab, religious
conversion, communal violence, Muslim appeasement claims. Include
anti-Pakistan framing ONLY when it is explicitly identity-laden (e.g.,
``Go to Pakistan if you want beef''); exclude when it is pure foreign
policy.
\item \textsc{economic\_provision}: text about public-goods delivery or
economic management. Concretely: welfare schemes (PM-KISAN, Ujjwala, Jan
Dhan, Ayushman Bharat, Awas Yojana), DBT/Aadhaar, MGNREGA, MSME,
farmers-as-producers (NOT farmers-as-lynching-victims), manufacturing,
infrastructure, Make in India, Viksit Bharat, GST, startup, digital India,
skilling.
\item \textsc{security\_foreign}: external-security and foreign-policy
content NOT primarily about domestic identity. Concretely: Pakistan as
military adversary, China, Galwan, LoC, Article~370 abrogation framed as
national security, surgical strikes, armed forces, terrorism abroad,
neighbours as strategic partners.
\item \textsc{residual}: ceremonial speeches, tributes, organisational
matters, procedural parliamentary business, condolences, anniversaries
without thematic content in the three categories above.
\end{itemize}

\smallskip
CRITICAL: A lynching news story is \textsc{identity\_contested} even if the
word ``farmer'' appears (the victim's occupation does not make it economic
content). A protest against CAA is \textsc{counter\_mobilization} even if
``economic'' grievances are incidentally mentioned. When in doubt between
\textsc{identity\_contested} and \textsc{counter\_mobilization}, ask: does
the text primarily describe a threat/event (\textsc{identity\_contested})
or a collective response (\textsc{counter\_mobilization})?

Return only the single UPPERCASE label.
\end{quote}

\begin{quote}\footnotesize
\noindent\textbf{Minority system prompt.}\\[0.3em]
You are classifying speeches and press coverage from Indian political
discourse for an academic political-economy paper. The paper models a
security-oriented majority party's use of symbolic policy ($d$) to
manufacture a minority threat and thereby offset its comparative economic
disadvantage. You will classify each text into exactly ONE category based
on which theoretical primitive the text is primarily supplying content to.
Return ONLY the single label in UPPERCASE, nothing else.

\smallskip
Categories for MINORITY texts (press coverage and AIMIM speeches about
Muslim community):

\begin{itemize}[leftmargin=1.2em, itemsep=0.15em, topsep=0.2em]
\item \textsc{identity\_contested}: text about identity-coded regulation
or conflict affecting Muslims. Concretely: beef/cow lynching victims,
CAA/NRC opposition, hijab rights, waqf rights, triple talaq debates,
Babri/Gyanvapi, communal violence, Muslim representation concerns, Muslim
electoral politics, anti-Muslim rhetoric reported on.
\item \textsc{counter\_mobilization}: text describing Muslim-led or
Muslim-joined protest, resistance, organising. Concretely: Shaheen Bagh,
CAA protests, bandh, dharna, satyagraha, rally, march, ``not in my name'',
civil disobedience, petition drives, legal challenges framed as
resistance.
\item \textsc{security\_foreign}: external-security content,
Pakistan/Kashmir militancy framing, terrorism NOT primarily about identity.
\item \textsc{economic}: genuine economic content about Muslim community
(employment, business, education access) NOT about lynching or identity.
\item \textsc{residual}: sports, entertainment, unrelated news, internal
community matters without political content.
\end{itemize}

\smallskip
CRITICAL: A lynching news story is \textsc{identity\_contested} even if the
word ``farmer'' appears (the victim's occupation does not make it economic
content). A protest against CAA is \textsc{counter\_mobilization} even if
``economic'' grievances are incidentally mentioned. When in doubt between
\textsc{identity\_contested} and \textsc{counter\_mobilization}, ask: does
the text primarily describe a threat/event (\textsc{identity\_contested})
or a collective response (\textsc{counter\_mobilization})?

Return only the single UPPERCASE label.
\end{quote}

On the $2{,}330$ rows Haiku classified at the time of the main-text figure,
the category distributions are:
\begin{center}
\footnotesize
\begin{tabular}{lcc}
\toprule
Category & Majority & Minority \\
\midrule
Identity-coded / contested & $14.5\%$ & $63.3\%$ \\
Counter-mobilisation & --- & $22.8\%$ \\
Economic-programmatic & $33.7\%$ & $0.7\%$ \\
Security-and-foreign & $10.3\%$ & $2.7\%$ \\
Residual & $40.6\%$ & $10.7\%$ \\
Unparseable / error & $0.8\%$ & $0.0\%$ \\
\bottomrule
\end{tabular}
\end{center}

\textbf{Outputs and validation.} Aggregate monthly shares
underlying \autoref{fig:narrative_timeseries} are computed as the count of
rows in the numerator category divided by the total rows in the corpus that
month, with a six-month centred rolling mean applied for display and
monthly totals below two items set to missing. A validation audit against
$200$ hand-coded sample items is planned for the next revision.

\subsection{Minority Corpus Construction} \label{app:minority_corpus}

The $3{,}783$-item Muslim-voice proxy corpus is constructed from Google News
RSS feeds, one per query, retrieved at 1 request per second with a custom
user agent and cached locally. Queries span five categories: (i)~Muslim
political representation (Owaisi, AIMIM, MIM, Muslim MP, Muslim
chief~minister); (ii)~religious leadership (Jamiat Ulama-i-Hind, Deoband,
AIMPLB); (iii)~cow-related violence (Akhlaq, Pehlu Khan, Junaid, Tabrez,
cow~vigilante lynching, gau~rakshak); (iv)~legislative episodes (CAA,
NRC, NPR, triple talaq, hijab, waqf, UCC); (v)~locational flashpoints
(Shaheen~Bagh, Babri~Masjid, Gyanvapi, Bilkis~Bano, Kashmir). Each retrieved
item is deduplicated by URL, enriched with outlet name parsed from the RSS
source field, and stored with the item's title, description (first $\sim$30
words), publication date, and URL. The 2025 share of items is
disproportionately high ($31\%$) because of the Waqf Amendment and
freshness-weighted indexing in Google News RSS; the main-text figure
controls for this with monthly-share normalisation rather than raw counts.

\subsection{Intergenerational Welfare Consequences} \label{app:intergenerational}

The main text's focus on the contemporaneous Security Premium leaves open the
question of the durable welfare consequences of repeated symbolic-policy
shocks. In prior work on the same India beef-ban setting, I estimate a series
of generation-specific consequences using the IHDS-II micro-panel and an
intensity measure \textit{Un-Hinduism~$\times$~Ban} that interacts household
religious identity with exposure to the ban window. The results span three
generations and four domains: (i)~birth history and early-life growth
deficiency (induced abortion, premature death, infant Ponderal Index, minor
BMI); (ii)~short- and long-term poverty (absolute, relative, and subjective
cutoffs); (iii)~first-generation segregation and second-generation
discrimination (electoral and ethnic segregation, political acquaintance,
religious trust; school inaccessibility, teacher unfairness, communal
prejudice); (iv)~first-generation utility and protest (net income, life
satisfaction, demonstration and boycott participation). The full tables,
specifications, and robustness checks will be migrated into this appendix in a subsequent revision.

\subsection{Paradox-of-Competence Regression}\label{app:paradox_regression}

\autoref{fig:paradox_of_competence} reports a linear-probability model of
BJP retention at the next Assembly election on tenure-average annual count
of Hindu--Muslim violent events. The sample is every state-election pair in
which the BJP was the state government in the year prior to the election
($N=42$, fifteen states, $1984$--$2024$). GDELT Hindu--Muslim violent
events $1980$--$2024$ is the primary conflict series, with
Varshney--Wilkinson incidents as a pre-1995 supplement.

The primary specification regresses the retention indicator on
tenure-average annual event count, with state-clustered standard
errors. The coefficient is~$+0.0103$~(SE~$0.0042$, $p=0.015$): one
additional violent Hindu--Muslim event per tenure year raises the BJP
retention probability by approximately one percentage point. Quintile
means of the retention rate rise monotonically from~$33\%$ in the lowest
tenure-conflict quintile to~$78\%$ in the highest.

Robustness: the sign is stable and the magnitude broadly comparable under a
log-conflict specification ($p=0.063$), under the addition of decade fixed
effects ($p=0.089$), and under an average-marginal-effect logit
($p=0.11$). Splitting the sample at 2014 returns similar positive
coefficients in both the pre-2014 ($N=23$, $p=0.061$) and post-2014
($N=19$, $p=0.085$) subsamples, so the pattern is not a Modi-era
artefact. The effect operates at the retention margin rather than on a
smoother vote-share metric: the coefficient on the continuous BJP
vote-share change is right-signed but insignificant ($p=0.36$), consistent
with the seat-winning margin being the discretely-decided object.

The state-FE specification is not estimable with this sample size:
within-state outcome variation is thin in $10$ of the $15$ states and the
fixed-effects design absorbs much of the relevant variation mechanically.
The primary specification should therefore be read as combining
within-state and cross-state identification.

\subsection{Ban-and-Conflict Event Studies} \label{app:event_studies}

A parallel line of analysis estimates the effect of each of the four
bovine-family cattle-slaughter-ban types on Hindu--Muslim violence at the
state-year level using staggered difference-in-differences with two-way
fixed effects and event-study leads and lags. The main-text figure
(\autoref{fig:rent_dissipation_event_study}) reports the TWFE event-study
coefficients per ban type. \autoref{fig:event_studies_robustness} reports
the same coefficients overlaid with three modern dynamic-DiD estimators
--- \citet*{cengizEffectMinimumWages2019}, \citet*{gardnerTwostageDifferencesDifferences2022}, and \citet*{liuPracticalGuideCounterfactual2024} ---
to show the post-adoption pattern is robust to estimator choice. Sample
and control specification match the main-text version.

\input{appendix_figures}

\subsection{State-Level Population Panel} \label{app:population}

Annual state-level population 2000--2024 is interpolated from
Census~2001 and Census~2011 enumerations. The 2011 state shares of the
national total are carried forward annually by rescaling to the World Bank
\texttt{SP.POP.TOTL} India series. The resulting panel is used to
normalize the Hindu--Muslim violence intensity in Map~B
(\autoref{fig:map_conflict_intensity}).

\subsection{Supplementary Maps} \label{app:supplementary_maps}

The six policy-specific maps (one per ban type) and the seven decade-specific
conflict maps are available in the supplementary replication materials but are not reproduced in this appendix.


%===================================================================================
% APPENDIX B: Proofs (NEW for v2)
%===================================================================================

\section{Proofs} \label{app:proofs_v2}

\subsection*{Proof of \autoref{lem:bayes_v2}} \label{app:proof:bayes_v2}

\begin{proof}
Under the prior $\theta_t\mid M_t\sim\mathcal{N}(M_t,\tau_M^{-1})$ and the
signal $s_t\mid\theta_t\sim\mathcal{N}(\theta_t,\tau_d^{-1})$ generated
by $s_t=d_t^\sigma+\epsilon_t$ with $\epsilon_t\sim\mathcal{N}(0,\tau_d^{-1})$,
the joint density of $(\theta_t,s_t)$ given $M_t$ is the product of two
Gaussians. The conditional posterior density satisfies
\[
p(\theta_t\mid s_t,M_t)\;\propto\;\exp\!\Big\{-\tfrac{1}{2}\big[\tau_M(\theta_t-M_t)^2+\tau_d(\theta_t-s_t)^2\big]\Big\}.
\]
Expanding and collecting terms in $\theta_t$, the bracketed expression is
$(\tau_M+\tau_d)\theta_t^2-2(\tau_M M_t+\tau_d s_t)\theta_t+\text{const}$,
which is the quadratic form of a Gaussian with precision $\tau_M+\tau_d$
and mean
\[
E[\theta_t\mid s_t,M_t]\;=\;\frac{\tau_M M_t+\tau_d s_t}{\tau_M+\tau_d}\;=\;(1-\omega)\,M_t+\omega\,s_t,\qquad \omega=\tfrac{\tau_d}{\tau_M+\tau_d}.
\]
Substituting the unconditional expectation $E[s_t\mid d_t]=d_t^\sigma$
delivers \autoref{eq:bayes_post_v2}. Dividing both sides by $\omega$ gives
\[
\hat d_t^\sigma\;:=\;E[\theta_t\mid s_t,M_t]/\omega\;=\;\frac{1-\omega}{\omega}\,M_t+d_t^\sigma\;=\;d_t^\sigma+\xi M_t,
\]
which is \autoref{eq:bayes_form_v2} with $\xi:=(1-\omega)/\omega=\tau_M/\tau_d$. The Minority's
expected loss in the within-period collective-action problem is then
$\phi\,E[\theta_t\mid s_t,M_t]\,(1-\Pi_k)=\phi\omega\,\hat d_t^\sigma(1-\Pi_k)$,
which recovers \autoref{eq:V_minority_v2} after absorbing the constant $\omega$
into the calibration of the grievance-sensitivity parameter $\phi$.
\end{proof}

\subsection*{Proof of \autoref{lem:contest_v2}} \label{app:proof:contest_v2}

\begin{proof}
The Majority FOC is given by \autoref{eq:EM_BR_v2}. The Minority FOC
under \autoref{eq:V_minority_v2} carries stake $\phi(d^\sigma + \xi M)$,
equivalently $\phi\hat d^\sigma$ for $\hat d^\sigma := d^\sigma + \xi M$.

\textit{Step 1 (Dormant case, $\hat d^\sigma = 0$).} If $d = 0$ and $M = 0$,
then $\phi\hat d^\sigma = 0$ and the Minority FOC implies $e_j = 0$ for all
$j$, so $E_m^* = 0$. Substituting into the Majority FOC gives $E_M^* = 0$.
By continuity of the CSF, $\lim_{\hat d \downarrow 0} \Pi_k^* = 1$.

\textit{Step 2 (Existence, uniqueness, closed form for $\hat d^\sigma > 0$).}
Symmetric within-group equilibrium gives $E_M = N_M e_i$, $E_m = N_m e_j$.
Dividing the FOCs:
\[
\frac{E_M / N_M}{E_m / N_m}
= \frac{\Lambda S_k E_m / (S_k E_M + E_m)^2}{\kappa\phi\hat d^\sigma S_k E_M / (S_k E_M + E_m)^2}
= \frac{\Lambda E_m}{\kappa\phi\hat d^\sigma E_M}.
\]
Cross-multiplying yields $\kappa\phi\hat d^\sigma N_m E_M^2 = \Lambda N_M E_m^2$, hence
$E_M / E_m = \alpha\hat d^{-\sigma/2}$ with $\alpha = \sqrt{\Lambda N_M / (\kappa\phi N_m)}$.
Substituting $E_M = \alpha\hat d^{-\sigma/2} E_m$ into the Majority FOC and
simplifying gives \autoref{eq:Em_Sk_explicit}. The Tullock CSF then gives
$\Pi_k^* = S_k\alpha / (S_k\alpha + \hat d^{\sigma/2})$, which is
\autoref{eq:Pi_v2}.

\textit{Step 3 (Comparative statics).} Differentiating \autoref{eq:Pi_v2}:
\[
\frac{\partial\Pi_k^*}{\partial S_k} = \frac{\alpha\hat d^{\sigma/2}}{(S_k\alpha + \hat d^{\sigma/2})^2} > 0,
\qquad
\frac{\partial\Pi_k^*}{\partial \hat d} = -\frac{S_k\alpha \cdot (\sigma/2)\hat d^{\sigma/2 - 1}}{(S_k\alpha + \hat d^{\sigma/2})^2} < 0,
\]
for $\hat d > 0$. The chain rule gives $\partial\Pi_k^* / \partial d < 0$
and $\partial\Pi_k^* / \partial M < 0$ on $\hat d > 0$. Limits follow
directly from \autoref{eq:Pi_v2}.
\end{proof}

\subsection*{Proof of \autoref{lem:Sk_v2}} \label{app:proof:Sk_v2}

\begin{proof}
From \autoref{eq:Em_Sk_explicit} both efforts depend on $S_k$ only through
$\psi(S_k) := S_k^{1/2} / (S_k\alpha + \hat d^{\sigma/2})$. Differentiating:
\[
\frac{d\log\psi(S_k)}{dS_k} = \frac{1}{2S_k} - \frac{\alpha}{S_k\alpha + \hat d^{\sigma/2}} = \frac{\hat d^{\sigma/2} - S_k\alpha}{2 S_k(S_k\alpha + \hat d^{\sigma/2})}.
\]
This is positive for $S_k < \hat d^{\sigma/2}/\alpha$, zero at
$S_k = \hat d^{\sigma/2}/\alpha = \overline S(\hat d)$, and negative thereafter.
Single-peakedness of $E_M^*, E_m^*$ in $S_k$ follows. Strict monotonicity
of $Z_k^* = S_k E_M^*$ follows by direct computation:
$\partial \log Z_k^* / \partial S_k = 3/(2S_k) - \alpha/(S_k\alpha + \hat d^{\sigma/2}) > 0$.
Strict monotonicity of $\Pi_k^*$ in $S_k$ was shown in the proof of
\autoref{lem:contest_v2}.
\end{proof}

\subsection*{Proof of \autoref{cor:peak_v2}} \label{app:proof:peak_v2}

\begin{proof}
Substitute $S_k = \overline S(\hat d) = \hat d^{\sigma/2} / \alpha$ into
\autoref{eq:Pi_v2}: $\Pi_k^* = (\hat d^{\sigma/2}/\alpha) \cdot \alpha / (\hat d^{\sigma/2}/\alpha \cdot \alpha + \hat d^{\sigma/2}) = \hat d^{\sigma/2} / (2\hat d^{\sigma/2}) = 1/2$.
For the peak level, substitute the same restriction into $E_M^*$ from
\autoref{eq:Em_Sk_explicit}:
\[
E_M^*(\hat d, \overline S(\hat d)) = \alpha\beta^2 \cdot \frac{(\hat d^{\sigma/2}/\alpha)^{1/2}\,\hat d^{\sigma/4}}{2\hat d^{\sigma/2}} = \frac{\alpha^{1/2}\beta^2}{2},
\]
which equals $\frac{1}{2}(\Lambda N_M)^{3/4}(\kappa\phi N_m)^{1/4}$ on
substituting the definitions of $\alpha$ and $\beta$.
\end{proof}

\subsection*{Proof of \autoref{lem:invU_v2}} \label{app:proof:invU_v2}

\begin{proof}
Define $h(x) := S_A\alpha / (S_A\alpha + x) - S_B\alpha / (S_B\alpha + x)$,
so $\Delta\Pi(d; M) = h(\hat d^{\sigma/2})$. Standard algebra shows $h$
vanishes at $x = 0$ and $x = \infty$, is strictly positive on $(0, \infty)$
when $S_A > S_B$, and is single-peaked at $x^{\mathrm{peak}} = \alpha\sqrt{S_A S_B}$
with peak value $h(x^{\mathrm{peak}}) = (\sqrt{S_A} - \sqrt{S_B})/(\sqrt{S_A} + \sqrt{S_B})$.

Translating back: $\Delta\Pi$ is single-peaked in $\hat d^{\sigma/2}$ at
$\alpha\sqrt{S_A S_B}$, equivalently $\hat d^\sigma = \alpha^2 S_A S_B$,
equivalently $d^\sigma = \alpha^2 S_A S_B - \xi M$. Solving for $d$:
\begin{itemize}
    \item If $\xi M < \alpha^2 S_A S_B$, the interior peak is at
    $d^{\mathrm{peak}}(M) = (\alpha^2 S_A S_B - \xi M)^{1/\sigma}$.
    \item If $\xi M \ge \alpha^2 S_A S_B$, $\hat d^\sigma$ already exceeds
    $\alpha^2 S_A S_B$ from the stock alone; any further $d > 0$ moves
    $\hat d^{\sigma/2}$ into the decreasing branch of $h$. The constrained
    optimum on $[0, \infty)$ is the corner $d = 0$.
\end{itemize}
The peak value is $h(\alpha\sqrt{S_A S_B})$ in case 1 and $h(\sqrt{\xi M})$
in case 2; the latter equals the same value when $\xi M = \alpha^2 S_A S_B$
and strictly decreases in $M$ thereafter. Finally,
$\Delta\Pi(0; M) = h(\sqrt{\xi M}) > 0$ for $M > 0$ (strict if $S_A > S_B$,
which we assume).
\end{proof}

\subsection*{Proof of \autoref{prop:RD_v2}} \label{app:proof:RD_v2}

\begin{proof}
By \autoref{lem:contest_v2}, $E_m^* > 0$ and $E_M^* > 0$ whenever $\hat d^\sigma > 0$,
i.e., whenever $d > 0$ or $M > 0$. Hence $RD = E_M^* + E_m^* > 0$ in this
region. At $d = 0$ and $M > 0$, $\hat d^\sigma = \xi M > 0$, so $RD > 0$
even when the incumbent does not provoke. The dormancy result
$RD(0, S_k; 0) = 0$ obtains as the special case with no inherited stock.
\end{proof}

\subsection*{Proof of \autoref{lem:dove_v2}} \label{app:proof:dove_v2}

\begin{proof}
Under the private-cost convention of \autoref{eq:utility_v2}, the Dove
incumbent's value is the voter retention probability $\Phi(\hat\xi(d_B;M))$
minus the private coalition-management cost $\chi_{\mathrm{mod}}(d_B)\mathbb{1}[d_B>0]$:
the voter swing index $\hat\xi(d,M)=(1-\lambda)\,\Delta u-\lambda\,\Delta\Pi(d;M)$
of \autoref{eq:swing_v2} contains no $\chi_{\mathrm{mod}}$ term, while
$\chi_{\mathrm{mod}}$ enters the Dove's value function only as a private cost
borne whenever the Dove herself provokes. Because $\Phi$ is strictly
monotone, the Dove's surrogate objective (up to a monotone
transformation) is
\[
J^B(d; M) := \Phi(\hat\xi(d,M)) - \chi_{\mathrm{mod}}(d)\,\mathbb{1}[d > 0].
\]
A linearisation of $\Phi$ around any reference value preserves monotone
comparisons, so it is equivalent to study the linearised surrogate
\[
\tilde J^B(d; M) := -\lambda\,\Delta\Pi(d; M) + (1-\lambda)\,\Delta u - \chi_{\mathrm{mod}}(d)\,\mathbb{1}[d>0],
\]
and to show $\tilde J^B(0; M) > \tilde J^B(d; M)$ for all $d > 0$.

\textit{Local argument on the increasing branch.} For
$d \in (0, d^{\mathrm{peak}}(M)]$, $\partial\Delta\Pi/\partial d \ge 0$
strictly on the interior, by \autoref{lem:invU_v2}. Hence the marginal
of $\tilde J^B$ is $-\lambda\,\partial\Delta\Pi/\partial d - \chi_{\mathrm{mod}}'(d) < 0$:
both terms push toward decreasing $d$. Thus $\tilde J^B$ is strictly
decreasing on $(0, d^{\mathrm{peak}}(M)]$, so $d_B = 0$ dominates any
$d \in (0, d^{\mathrm{peak}}(M)]$.

\textit{Global argument across the peak.} For $d > d^{\mathrm{peak}}(M)$,
$\Delta\Pi$ is strictly decreasing in $d$ and $\chi_{\mathrm{mod}}$
continues to rise. The relevant comparison is between $\tilde J^B(0; M)$
and $\tilde J^B(d; M)$:
\[
\tilde J^B(0; M) - \tilde J^B(d; M) = -\lambda\,(\Delta\Pi(0; M) - \Delta\Pi(d; M)) + \chi_{\mathrm{mod}}(d).
\]
Define $d^*$ as the (possibly $+\infty$) level at which $\Delta\Pi(d^*;M)=\Delta\Pi(0;M)$, the symmetric
re-crossing of the inverted-U. For $d \in (d^{\mathrm{peak}}(M), d^*]$,
$\Delta\Pi(0;M) \ge \Delta\Pi(d;M)$, so the first term is non-negative
and $\chi_{\mathrm{mod}}(d) > 0$ closes the inequality strictly. For
$d > d^*$, $\Delta\Pi(0;M)-\Delta\Pi(d;M)$ is bounded above by
$\Delta\Pi(0;M) \le (\sqrt{S_A}-\sqrt{S_B})/(\sqrt{S_A}+\sqrt{S_B})\le 1$, so the first term
is bounded by $\lambda$, while $\chi_{\mathrm{mod}}(d) \to \infty$ by
assumption. The inequality $\tilde J^B(0; M) > \tilde J^B(d; M)$
therefore holds for all $d > 0$, and $d_B^*(M) = 0$ is the unique
global maximiser.
\end{proof}

\subsection*{Proof of \autoref{prop:provocation_v2}} \label{app:proof:provocation_v2}

\begin{proof}
\textit{(i) Existence of finite maximiser.} $F(d; M)$ is continuous in $d$
on $[0, \infty)$ for each $M$. $F(0; M) = \lambda\,\Delta\Pi(0; M) \ge 0$
because $\Delta\Pi(0; M) \ge 0$ everywhere. Since
$\lim_{d\uparrow\infty}\chi_{\mathrm{mod}}(d) = \infty$ and $\Delta\Pi$ is
bounded by 1, $\lim_{d\uparrow\infty}F(d; M) = -\infty$. Hence the
maximum is attained at some finite $d_A^*(M) \ge 0$, and
$\overline{\Delta u}(M) \ge 0$.

\textit{(ii) Hawk-victory feasibility.} The Hawk wins iff
$\hat\xi(d_A^*(M); M) \le 0$, equivalently $F(d_A^*(M); M) \ge (1-\lambda)\Delta u$,
equivalently $\overline{\Delta u}(M) \ge \Delta u$.

\textit{(iii) Cutoff non-decreasing in $M$.} By the envelope theorem,
\[
\frac{\partial \overline{\Delta u}(M)}{\partial M}
= \frac{1}{1-\lambda}\,\frac{\partial F(d_A^*(M); M)}{\partial M}
= \frac{\lambda}{1-\lambda}\,\frac{\partial \Delta\Pi(d_A^*(M); M)}{\partial M}.
\]
On the increasing branch of the inverted-U (where $d \le d^{\mathrm{peak}}(M)$),
$\partial \Delta\Pi / \partial M > 0$. The interior optimum $d_A^*(M)$
lies on the increasing branch (where the marginal benefit equals the
marginal cost); hence $\partial \overline{\Delta u} / \partial M > 0$
when the optimum is interior. The technology-ratio bound \autoref{eq:dubar_bound_v2}
follows from $F(d) \le \lambda \cdot \max\Delta\Pi = \lambda(\sqrt{S_A} - \sqrt{S_B})/(\sqrt{S_A} + \sqrt{S_B})$.

\textit{(iv) Optimal current $d$ non-increasing in $M$.} Differentiate the
Hawk's FOC $\lambda \cdot \partial \Delta\Pi / \partial d = \chi_{\mathrm{mod}}'(d)$
implicitly with respect to $M$. By the implicit-function theorem and
strict convexity of $\chi_{\mathrm{mod}}$ ($\chi_{\mathrm{mod}}'' > 0$):
\[
\frac{\partial d_A^*}{\partial M}
= \frac{\lambda \cdot \partial^2 \Delta\Pi / (\partial d \partial M)}{\chi_{\mathrm{mod}}''(d_A^*) - \lambda \cdot \partial^2 \Delta\Pi / \partial d^2}.
\]
The denominator is positive at an interior maximum (second-order condition).
The numerator: on the increasing branch, $\Delta\Pi$ is concave in
$\hat d^{\sigma/2}$, so increases in $M$ (which raise $\hat d^\sigma = d^\sigma + \xi M$)
reduce the marginal benefit of further $d$. Hence $\partial^2 \Delta\Pi / (\partial d \partial M) < 0$
and $\partial d_A^* / \partial M < 0$.

\textit{(v) Corner in deep regime.} If $M \ge \alpha^2 S_A S_B / \xi$, the
unconstrained inverted-U peak in $\hat d$ is already exceeded by the stock
alone. Then $\Delta\Pi(d; M)$ is strictly decreasing in $d$ on $[0, \infty)$.
Since $\chi_{\mathrm{mod}}(d) \ge 0$ with strict inequality for $d > 0$, the
constrained optimum is the corner $d_A^*(M) = 0$.
\end{proof}

\subsection*{Proof of \autoref{lem:wedge_v2}} \label{app:proof:wedge_v2}

\begin{proof}[Sketch]
\textit{(i) Continuity and boundedness.} The Bellman operator $T$ defined by
\[
(Tw)(M, k) = U^k(d_k(M); M) + \delta\big[\rho^v(M, k) w(M', k) + (1-\rho^v(M, k)) w(M', \tilde k)\big]
\]
is a $\delta$-contraction in the sup norm on the Banach space
$\mathcal{C}_b(\mathbb{R}_+ \times \{A, B\})$ of bounded continuous
functions. By Banach's fixed-point theorem, the unique fixed point
$V^v(\cdot, \cdot)$ exists and is bounded continuous.

\textit{(ii) Monotonicity of $V^v(\cdot, B)$.} Under Dove with
$d_B^\star = 0$, the per-period payoff
$U^B(0; M) = \lambda\,\Pi_B^*(0, S_B; M) - \chi_{\mathrm{econ}}(0) + (1-\lambda)\,u(\bar g_B)$
is non-increasing in $M$ (since $\Pi_B^*(0, S_B; M)$ is non-increasing
in $M$ by \autoref{lem:contest_v2}, and the cost terms do not depend on $M$).
The next-period stock under Dove is
$M' = (1-\rho)M + \rho\,E_m^*(0, S_B; M)$, which is non-decreasing in $M$
on the increasing branch of $E_m^*$ and bounded above by $M^*$ from
\autoref{prop:trap_v2}'s Step 1.

The continuation under Dove is
$\delta[\rho^v(M', B)\,V^v(M', B) + (1 - \rho^v(M', B))\,V^v(M', A)]$.
The retention rule $\rho^v(M', B) = \mathbbm{1}[M' \le \underline M]$
from \autoref{prop:cutoff_v2} switches the continuation regime at
$M' = \underline M$. We establish monotonicity by a Topkis-style
argument on the Bellman operator restricted to non-increasing functions.
Let $T$ denote the Bellman; for any non-increasing $w(\cdot, B)$ with
$w(\cdot, B) \le w(\cdot, A)$ on $\{M \ge \underline M\}$, the next-period
continuation
$h(M') := \rho^v(M', B)\,w(M', B) + (1 - \rho^v(M', B))\,w(M', A)$
is non-increasing in $M'$: on $\{M' \le \underline M\}$, $h = w(M', B)$
which is non-increasing; on $\{M' > \underline M\}$, $h = w(M', A)$, and
the threshold-crossing produces a downward jump because $V^v(\underline M, B)
\ge V^v(\underline M, A)$ at $M' = \underline M$ (the voter is indifferent
or prefers Dove). Composition with the non-decreasing map $M \mapsto M'$
preserves the non-increasing property, so $(Tw)(\cdot, B)$ is
non-increasing whenever $w(\cdot, B)$ is. The set of non-increasing
bounded continuous functions is closed in the sup norm, so by Banach's
fixed-point theorem the fixed-point $V^v(\cdot, B)$ inherits
non-increasing monotonicity.


\textit{(iii) Single-crossing wedge.} \autoref{ass:wedge} posits that
$\Phi^M$ is continuous on $[0, \infty)$, satisfies $\Phi^M(0) < 0$ and
$\lim_{M\to\infty}\Phi^M(M) < 0$, and is strictly quasi-concave. Since
$\Phi^M$ is continuous, the upper level set
$\{M : \Phi^M(M) \ge 0\}$ is closed in $[0, \infty)$. Strict
quasi-concavity implies this level set is convex and therefore an
interval. Combined with the boundary conditions $\Phi^M(0) < 0$ and
$\lim_{M\to\infty}\Phi^M(M) < 0$, the level set is either empty (in which
case $\bar M = \infty$ and the model has no trap region) or a closed,
bounded interval $[\bar M, \overline M^+]$ with $0 < \bar M \le \overline M^+ < \infty$.
We focus on the lower threshold $\bar M$ as the cutoff governing the
forward-invariant trap; the upper threshold $\overline M^+$ corresponds to
the right tail of the inverted-U where the security premium vanishes
mechanically and is empirically irrelevant for the regime we study.
Parts (i) and (ii) of the lemma were established by the contraction
argument and the Topkis monotonicity argument above.
\end{proof}

\subsection*{Proof of \autoref{prop:cutoff_v2}} \label{app:proof:cutoff_v2}

\begin{proof}
By the single-crossing of $\Phi^M$ in \autoref{lem:wedge_v2}, $V^v(M, A) \ge V^v(M, B)$
iff $\Phi^M(M) \ge 0$ iff $M \ge \bar M$. Hence the voter retains the
Hawk iff $M \ge \bar M$, giving $\rho^v(M, A) = \mathbbm{1}[M \ge \bar M]$.
Symmetrically, the voter retains the Dove iff $V^v(M, B) \ge V^v(M, A)$,
iff $\Phi^M(M) \le 0$, iff $M \le \underline M$ where $\underline M$ is
defined by the same single-crossing.

Generic strict inequality $\underline M < \bar M$ follows from a
hysteresis-interval argument analogous to
\citet{coatePolicyPersistence1999}: under Hawk incumbency, the next-period
stock evolves under $d_A^\star$ which sustains $E_m^* > 0$; under Dove
incumbency, the next-period stock evolves under $d_B = 0$ and decays at
rate $\rho$. The difference in continuation paths makes the net continuation
value $V^v(M', k) - V^v(M', \tilde k)$ depend on which incumbent currently
holds office; this in turn opens a gap between the two retention thresholds.
The two thresholds coincide only when $\rho = 1$ (instant decay eliminates
the dynamic).
\end{proof}

\subsection*{Proof of \autoref{prop:MPE_v2}} \label{app:proof:MPE_v2}

\begin{proof}[Sketch]
\textit{Strategy space and fixed-point existence.} Let $M^* := \max\{\overline M^+, \beta^2/\alpha\}$,
where $\overline M^+ \le \infty$ is the upper crossing of the wedge from
\autoref{lem:wedge_v2}(iii) and $\beta^2/\alpha$ is the closed-form
upper bound on $E_m^*$ from \autoref{lem:contest_v2} (so the dynamics
naturally confine orbits to $[0, M^*]$). Let $d_{\max}$ be the unique
root of $\chi_{\mathrm{mod}}'(d) = \lambda \cdot (\sqrt{S_A}-\sqrt{S_B})/(\sqrt{S_A}+\sqrt{S_B})$,
which exists and is finite by strict convexity of $\chi_{\mathrm{mod}}$
and bounded $\Delta\Pi \le (\sqrt{S_A}-\sqrt{S_B})/(\sqrt{S_A}+\sqrt{S_B})$;
no within-period optimum exceeds $d_{\max}$. Restrict attention to
Markov strategies $d_k : [0, M^*] \to [0, d_{\max}]$ that are bounded
measurable. Equip the strategy space with the weak-$L^2$ topology, on
which the closed bounded subset
$\mathcal{S} := L^2([0, M^*], [0, d_{\max}])$ is compact (by
Banach–Alaoglu) and convex. Given the cutoff retention rule
$\rho^v$ from \autoref{prop:cutoff_v2}, the within-period best-response
correspondence is convex-valued (the within-period payoff is strictly
concave in own $d$ on the relevant range by strict convexity of
$\chi_{\mathrm{mod}}$ and weak concavity of $\Delta\Pi$ on its
increasing branch).

Upper hemicontinuity of the best-response correspondence in the
weak-$L^2$ topology requires care because the strategies are
infinite-dimensional functions. We adopt the standard approach of
\citet[Theorem~17.31]{aliprantisInfiniteDimensionalAnalysis2006}: under
weak-$L^2$ convergence of strategies, the within-period payoff is
jointly continuous (the contest mappings $E_M^*, E_m^*, \Pi_k^*$ are
continuous in $(d, M)$, and integration against the bounded
distribution of $M$ preserves continuity), so Berge's maximum theorem
in topological vector spaces applies. The best-response correspondence
is therefore upper hemicontinuous, non-empty, and convex-valued on
$\mathcal{S}$. Glicksberg's fixed-point theorem yields a Markov pair
$(d_A^\star, d_B^\star)$ that is mutually best-responding given
$\rho^v$.

\textit{Dove's corner.} The Dove's corner $d_B^\star = 0$ follows from
\autoref{lem:dove_v2} extended to the dynamic environment: any deviation
$d_B > 0$ would (a) raise $\Delta\Pi(d_B; M)$, lowering the Dove's
within-period electoral edge (which is monotone in $-\Delta\Pi$), and
(b) raise $M_{t+1}$ via \autoref{eq:M_evolution_v2}, which by the
non-increasing $V^v(\cdot, B)$ established in \autoref{lem:wedge_v2}(ii)
reduces the Dove's continuation value. Both forces weaken the Dove's
re-election chances; the corner is the unique best response.

\textit{Hawk's strategic margin.} The Hawk's re-election probability is
$\Phi(-\hat\xi(d, M))$, monotone in the swing-voter index
$-\hat\xi(d, M) = \lambda \Delta\Pi(d; M) - \chi_{\mathrm{mod}}(d) - (1-\lambda)\Delta u$.
The economic-disruption cost $\chi_{\mathrm{econ}}(d)$ enters the voter's
$U^A(d; M)$ and $U^B(d; M)$ symmetrically (both incumbents bear it at
the same $d$), so it cancels from $U^A - U^B$ and does not appear in
$\hat\xi$. The Hawk's per-period strategic margin is therefore
$F(d; M) = \lambda \Delta\Pi(d; M) - \chi_{\mathrm{mod}}(d)$, exactly as
in the static problem.

In the dynamic problem, the Hawk's surrogate objective is
\begin{equation}\label{eq:hawk_objective}
J^A(d; M) := F(d; M) + \delta\,V^v(M'(d, M), A),
\end{equation}
where $M'(d, M) = (1 - \rho)M + \rho\,E_m^*(d, S_A; M)$ and the
continuation $V^v(M', A)$ enters because retention is governed by the
voter's wedge $\Phi^M(M')$ at the next-period state, which in turn
tracks $V^v$. Differentiating yields \autoref{eq:dyn_FOC}: the
within-period marginal $\lambda\,\partial\Delta\Pi/\partial d - \chi_{\mathrm{mod}}'$
plus the stock-building term
$\delta\,(\partial V^v/\partial M')\,(\partial M'/\partial d)$. Both
partials are well-defined: $\partial M'/\partial d = \rho \cdot
\partial E_m^*/\partial d > 0$ on the increasing branch of $E_m^*$, and
$\partial V^v(M', A)/\partial M'$ is the derivative of the Hawk-incumbent
value, which is positive on the increasing branch of $V^v(\cdot, A)$ and
negative beyond. The FOC need not have a unique interior root globally,
because $\partial V^v/\partial M'$ flips sign around the Hawk-optimal
$M'$. We claim only that any interior solution $d_A^\star(M)$ of
\autoref{eq:dyn_FOC} is a local maximum and that the global maximum is
unique whenever the joint object $J^A(d; M)$ is strictly concave in $d$
on $[0, d_{\max}]$. Sufficient parametric conditions are: (a)
$\Delta\Pi(\cdot; M)$ is strictly concave in $d$ on the increasing
branch (which holds whenever $\sigma \le 2$; verified by direct
computation in \autoref{eq:security_premium_d}), and (b) the
stock-building term has bounded curvature relative to the within-period
margin. Outside this region, the FOC may admit two interior roots, in
which case $d_A^\star(M)$ is selected as the global maximum.

\textit{Corner in the deep regime.} In the deep paradox-of-restraint
regime $M \ge \alpha^2 S_A S_B / \xi$, $\partial \Delta\Pi / \partial d < 0$
on $[0, \infty)$, so the within-period margin is everywhere negative.
Moreover, in this regime $M' \ge M$ for any $d \ge 0$ implies $M'$
remains in the deep regime where $V^v(\cdot, A)$ is decreasing in $M'$,
so $\partial V^v/\partial M' \le 0$, and the stock-building term is
non-positive (since $\partial M'/\partial d \ge 0$). Thus the dynamic
FOC is everywhere non-positive on $[0, \infty)$ and the corner
$d_A^\star(M) = 0$ is the unique optimum.

\textit{Cutoff retention and Bellman uniqueness.} Voter retention
follows from \autoref{prop:cutoff_v2}. The voter Bellman operator
\[
(Tw)(M, k) = U^k(d_k(M); M) + \delta\big[\rho^v(M, k)\,w(M', k) + (1-\rho^v(M, k))\,w(M', \tilde k)\big]
\]
is a $\delta$-contraction in the sup norm on the Banach space of
bounded continuous functions on $[0, M^*] \times \{A, B\}$, so its
fixed point $(V^v(\cdot, A), V^v(\cdot, B))$ is unique by Banach.
\end{proof}

\subsection*{Proof of \autoref{prop:trap_v2} (part (i) of \autoref{prop:phase_transition})} \label{app:proof:trap_v2}

\begin{proof}
The argument verifies stochastic forward-invariance of $\mathcal T^*=\{(M,A):M\ge\bar M^*\}$, where $\bar M^*=\sup_{\omega\in[0,\bar\omega]}\bar M(\omega)$ is the worst-case retention cutoff of \autoref{prop:cutoff_v2}. Throughout, define the realisation-conditional one-step map
\[
\Psi(M;\rho,\omega) := (1-\rho)M + \rho\,E_m^*(d_A^\star(M), S_A; M, \omega),
\quad
\eta(M,\omega) := E_m^*(d_A^\star(M), S_A; M, \omega) - \bar M^*.
\]
By the proposition's hypothesis at $\omega=0$, $\bar M^*<\infty$ and $\eta(\bar M^*,0)>0$. Because $\hat d^\sigma=d^\sigma+\xi M+\omega$ is non-decreasing in $\omega$ and $E_m^*$ inherits this monotonicity from \autoref{lem:contest_v2}, $\eta(M,\omega)\ge\eta(M,0)$ pointwise in $M$ for every $\omega\in[0,\bar\omega]$. Hence the threshold $\bar\rho$ derived below from the deterministic ($\omega=0$) version is conservative: the trap holds for any $\rho<\bar\rho$ under any realisation $\omega\in[0,\bar\omega]$, almost surely under $F$.

\textit{Step 1 (a priori upper bound on the orbit).}
By \autoref{lem:contest_v2}, $E_m^*(d, S_A; M, \omega)\le\beta^2/\alpha<\infty$ uniformly in $\omega\in[0,\bar\omega]$, where $\beta=(\kappa\phi N_m\Lambda N_M)^{1/4}$ and $\alpha=(\Lambda N_M/(\kappa\phi N_m))^{1/2}$. Set $M^\dagger:=\max\{\beta^2/\alpha,\,M_0\}$. Then for any $M\ge M^\dagger$, any $\omega$, and any $\rho\in(0,1)$, $\Psi(M;\rho,\omega)-M=\rho\,(E_m^*(\cdot,\omega)-M)\le\rho\,(\beta^2/\alpha-M)\le 0$, so the orbit is contained in the compact set $[\bar M^*,M^\dagger]$ provided $M_t\ge\bar M^*$ at every step.

\textit{Step 2 (voter retains within $[\bar M^*,\overline M^+]$ for every $\omega$).}
By definition of $\bar M^*$, $\Phi^M(M,\omega)\ge 0$ for every $M\ge\bar M^*$ and every $\omega\in[0,\bar\omega]$. \autoref{prop:cutoff_v2} therefore gives $\rho^v(M_t,A,\omega_t)=1$ almost surely for $M_t\ge\bar M^*$, so $k_{t+1}=A$ almost surely. Restrict the trap region to $\mathcal T^c:=\{(M,k):k=A,\,\bar M^*\le M\le\min(M^\dagger,\overline M^+)\}$.

\textit{Step 3 (existence of a forward-invariance threshold $\bar\rho$).}
By Step 1, the orbit lies in the compact set $K:=[\bar M^*,\min(M^\dagger,\overline M^+)]$. The deterministic version $\eta(\cdot,0)$ is continuous on $K$ and attains its minimum $\eta_{\min}:=\min_{M\in K}\eta(M,0)$.

\textit{Case 3a ($\eta_{\min}\ge 0$, uniform inflows at $\omega=0$).} For any $\rho\in(0,1)$, any $M\in K$, and any $\omega\in[0,\bar\omega]$,
\[
\Psi(M;\rho,\omega)-\bar M^* = (1-\rho)(M-\bar M^*) + \rho\,\eta(M,\omega) \ge (1-\rho)(M-\bar M^*) + \rho\,\eta(M,0) \ge 0,
\]
so $\Psi(M;\rho,\omega)\ge\bar M^*$ almost surely. Forward-invariance holds for any $\rho\in(0,1]$ and we may set $\bar\rho:=1$.

\textit{Case 3b ($\eta_{\min}<0$, some interior $M$ has $E_m^*(\cdot,0)<\bar M^*$).} By continuity and $\eta(\bar M^*,0)>0$, there exists $\delta>0$ such that $\eta(M,0)>\tfrac12\eta(\bar M^*,0)>0$ on $[\bar M^*,\bar M^*+\delta]$. The set $K^-:=\{M\in K:\eta(M,0)<0\}$ is therefore contained in $[\bar M^*+\delta,\min(M^\dagger,\overline M^+)]$, compact and bounded away from $\bar M^*$. Define
\begin{equation}\label{eq:rhobar_v2}
\bar\rho := \inf_{M\in K^-}\,\frac{M-\bar M^*}{M-E_m^*(d_A^\star(M),S_A;M,0)}.
\end{equation}
Both numerator and denominator are continuous and bounded on $K^-$: the numerator is at least $\delta>0$, and the denominator is bounded above by $M^\dagger+\bar M^*<\infty$. Hence $\bar\rho>0$, and $\bar\rho<1$ whenever $K^-$ is nonempty, so $\bar\rho\in(0,1)$. For any $\rho<\bar\rho$ and any $M\in K$, $\Psi(M;\rho,0)\ge\bar M^*$ by construction. The presence of $\omega_t\ge 0$ raises $E_m^*$ pointwise compared with the deterministic $\omega=0$ version (since $\hat d^\sigma=d^\sigma+\xi M+\omega$ raises the contest stake), so $\Psi(M;\rho,\omega)\ge\Psi(M;\rho,0)\ge\bar M^*$ uniformly in $\omega$; the trap therefore holds for any realisation of the shock and any $\rho<\bar\rho$, almost surely under $F$. The threshold $\bar\rho$ in \autoref{eq:rhobar_v2} depends only on model primitives.

\textit{Step 4 (induction).} Combining Steps 2--3, $(M_t,A)\in\mathcal T^c$ for all $t\ge 0$ almost surely when $\rho<\bar\rho$ and $M_0\in[\bar M^*,\min(M^\dagger,\overline M^+)]$.

\textit{Step 5 (within-trap convergence).} Inside $\mathcal T^c$, the sequence $\{M_t\}$ is bounded and the realisation-conditional dynamics $\Psi(\cdot;\rho,\omega)$ are uniformly continuous in $(M,\omega)$ on the compact rectangle $K\times[0,\bar\omega]$. Any almost-sure limit point $M^\infty$ of $\{M_t\}$ satisfies the expected fixed-point equation $M^\infty=\mathbb E_\omega[\Psi(M^\infty;\rho,\omega)]$, equivalently $\mathbb E_\omega[E_m^*(d_A^\star(M^\infty),S_A;M^\infty,\omega)]=M^\infty$. Standard stochastic-approximation arguments \citep{borkarStochasticApproximation2008} yield $M_t\to M^\infty$ in probability and $d_A^\star(M_t)\to d_A^\infty:=d_A^\star(M^\infty)$, with $d_A^\infty=0$ in the deep regime $M^\infty\ge\alpha^2 S_A S_B/\xi$ and $d_A^\infty>0$ otherwise.
\end{proof}

\subsection*{Proof of \autoref{prop:cycles_v2} (part (ii) of \autoref{prop:phase_transition})} \label{app:proof:cycles_v2}

\begin{proof}[Sketch]
With $\hat d^\sigma=d^\sigma+\xi M+\omega$, all closed forms of \autoref{lem:contest_v2} carry through. The argument structures the cycles regime as Foster–Lyapunov verification of the three conditions of \citet[Thm.~13.0.1]{meynMarkovChainsStochastic2009}, with the cycles regime defined by $\rho>\bar\rho$ structurally rather than by myopic voting: cycles arise whenever the deterministic basin of attraction is shallower than the support of the shock distribution, regardless of the voter's discount factor $\delta\in(0,1)$.

\textit{Step 1 (compact orbit support).} By the same a priori bound as in part (i), $E_m^*(\cdot,\omega)\le\beta^2/\alpha$ uniformly in $\omega\in[0,\bar\omega]$, where $\beta=(\kappa\phi N_m\Lambda N_M)^{1/4}$ and $\alpha=(\Lambda N_M/(\kappa\phi N_m))^{1/2}$. Hence $M_{t+1}\le(1-\rho)M_t+\rho\,\beta^2/\alpha$. Iterating, $M_t\le M^\dagger:=\max\{M_0,\beta^2/\alpha\}$ almost surely for all $t$. The chain is therefore confined to the compact set $C:=[0,M^\dagger]$, and a fortiori on $C\times\{A,B\}$ for the joint chain. All subsequent steps work on this compact support.

\textit{Step 2 ($\phi$-irreducibility).} $\phi$-irreducibility of the chain on $C\times\{A,B\}$ holds because $\hat d^\sigma=d^\sigma+\xi M+\omega$ is strictly increasing in $\omega$ even at $(d,M)=(0,0)$. Combined with the absolute continuity of the shock distribution $F$ on $[0,\bar\omega]$, the conditional density of $M_{t+1}$ given $M_t$ has positive open support on a non-degenerate sub-interval of $C$, ensuring that every $\phi$-positive subset of $C$ is reached from any starting point with positive probability. Specifically, the one-step kernel assigns positive mass to $((1-\rho)M_t+\rho E_m^*(\cdot,0),(1-\rho)M_t+\rho E_m^*(\cdot,\bar\omega))$ and this interval has non-degenerate length whenever $\bar\omega>0$. Iterating gives $\phi$-irreducibility with $\phi$ Lebesgue measure on $C$.

\textit{Step 3 (aperiodicity).} The same absolute continuity of $F$ guarantees that the conditional distribution of $M_{t+1}\mid M_t$ has no atom in any periodic-cycle structure: for every Borel $A\subset C$ with $\phi(A)>0$, the one-step transition kernel assigns it positive mass starting from any $M_t\in C$, so no finite partition of the state space carries the chain through a deterministic cycle. The chain is aperiodic.

\textit{Step 4 (Lyapunov function and Foster–Lyapunov drift).} Take $V(M):=M$ as the Lyapunov function on $C$. Compute
\[
\Delta V(M)\;:=\;\mathbb E[V(M_{t+1})-V(M_t)\mid M_t=M]\;=\;\rho\,\big(\mathbb E_\omega[E_m^*(d_{k_t}^\star(M),S_{k_t};M,\omega)]-M\big).
\]
By Step 1, $\Delta V(M)\le\rho(\beta^2/\alpha-M)$, which is strictly negative outside the small set $\tilde C:=[0,\beta^2/\alpha+1]\cap C$. The Foster–Lyapunov drift inequality $\Delta V(M)\le-\beta_0 V(M)+b\,\mathbf 1_{\tilde C}(M)$ holds with $\beta_0=\rho/2$ and $b=\rho(\beta^2/\alpha+1)$, so the marginal $M$-chain has a unique invariant probability measure to which it converges geometrically in total variation \citep[Ch.~14--15]{meynMarkovChainsStochastic2009}. Standard stochastic-approximation arguments \citep{borkarStochasticApproximation2008} confirm convergence in distribution of $\{M_t\}$ to the invariant measure.

\textit{Step 5 (uniform positive flip probabilities on $C$).} On the compact set $C$, the within-period flip probability $\Phi(\hat\xi(d_t^\star(M_t),M_t,\omega_t))$ is continuous in $M_t$ and in $\omega_t$ (both through the contest closed forms and through the realised swing index). By the full support of $F$ and the strict monotonicity of $\hat\xi$ in $\omega$, the set $\{\omega:\hat\xi(d_t^\star(M_t),M_t,\omega)\ge 0\}$ has positive measure under $F$ for every $M_t\in C$. Continuity in $M_t$ on the compact $C$ implies the measure attains a positive minimum, so the conditional flip probabilities $\pi_{AD},\pi_{DA}$ are bounded away from zero uniformly on $C$. The same continuity-and-compactness argument bounds them away from one. Hence for every $\delta\in(0,1)$, both Hawk-to-Dove and Dove-to-Hawk transitions occur with strictly positive probability uniformly on $C$. The hazard of the Hawk-to-Dove transition is increasing in $\omega$-driven declines in observed disorder by the within-period swing-voter logic, delivering the paradox-of-competence statement of part (ii).

\textit{Conclusion.} Steps 1--4 verify the three Meyn–Tweedie conditions on the marginal $M$-chain on the compact set $C$; Step 5 extends the argument to the joint $(M,k)$ chain via the uniform positive-probability transitions in both regime directions established on $C$. By \citet[Thm.~13.0.1]{meynMarkovChainsStochastic2009}, the joint chain admits a unique invariant probability $\pi^*$ on $C\times\{A,B\}$, with $\pi^*(\{k=A\})\in(0,1)$ and $\pi^*(\{k=B\})\in(0,1)$, and the realised regime sequence visits each regime infinitely often almost surely.
\end{proof}

\subsection*{Proof of \autoref{cor:paradox_v2}} \label{app:proof:paradox_v2}

\begin{proof}
In the cycles regime ($\rho>\bar\rho$), retention is implemented by the realisation-conditional cutoff rule of \autoref{prop:cutoff_v2}: $\rho^v(M,A,\omega)=1$ iff $M\ge\bar M(\omega)$. A first-order stochastic decrease in $\tilde v_t=(1-\Pi_{A,t}^*)+\varepsilon^v_t$ implies a stochastic decrease in the perceived disorder under Hawk incumbency. Because $\Pi_{A,t}^*$ is deterministic given $(M,\omega)$, the decrease loads on $\varepsilon^v_t$, which weakly lowers the realised Security Premium and weakly raises the realisation-conditional cutoff $\bar M(\omega)$. The probability that the inherited stock $M_t$ falls short of $\bar M(\omega)$ at the realised $\omega$ weakly increases, equivalently the Hawk's realisation-conditional defeat hazard weakly increases.
\end{proof}

\subsection*{Proof of \autoref{prop:cs_v2} (comparative statics on $\bar M^*$ in \autoref{prop:phase_transition})} \label{app:proof:cs_v2}

\begin{proof}[Sketch]
The argument applies the implicit-function theorem to the realisation-conditional cutoff $\bar M(\omega)=\inf\{M:\Phi^M(M,\omega)\ge 0\}$ at the worst-case shock $\omega^*\in\arg\sup_{\omega\in[0,\bar\omega]}\bar M(\omega)$, and concludes by transferring the signs to $\bar M^*=\bar M(\omega^*)$ through the envelope theorem.

\textit{Regularity hypotheses for the implicit-function theorem.}
Assume the following regularity beyond \autoref{ass:wedge}:
(R1) $\Phi^M(M, \omega; \theta)$ is continuously differentiable in $(M, \omega, \theta)$
on a neighbourhood of $(\bar M^*, \omega^*, \theta_0)$, where $\theta_0$ is the
baseline parameter vector;
(R2) (transversality) $\partial \Phi^M / \partial M\big|_{M = \bar M^*, \omega = \omega^*, \theta = \theta_0} \neq 0$.
Hypothesis (R1) is strictly stronger than the continuity required by
\autoref{ass:wedge}; it holds whenever the per-period payoff $U^k$ and
the contest functions $E_m^*, \Pi_k^*$ are continuously differentiable
in their parameters and in $\omega$, which is verified by inspection of the closed
forms in \autoref{lem:contest_v2} and by the absolute continuity of $F$. Hypothesis (R2) is a non-degeneracy
condition standard in implicit-function applications: it rules out
horizontal-tangent crossings at the cutoff. Strict quasi-concavity together with (R1) gives
$\partial \Phi^M / \partial M\big|_{\bar M^*, \omega^*} \ge 0$; combined with (R2),
the inequality is strict, so $\partial \Phi^M / \partial M\big|_{\bar M^*, \omega^*} > 0$.

\textit{Implicit-function differentiation.} Under (R1)--(R2),
the implicit-function theorem applied to $\Phi^M(\bar M(\omega^*;\theta), \omega^*; \theta) = 0$
yields
\[
\frac{\partial \bar M(\omega^*)}{\partial \theta} = -\frac{\partial \Phi^M / \partial \theta}{\partial \Phi^M / \partial M}\bigg|_{M = \bar M^*, \omega = \omega^*}.
\]
The envelope theorem applied to $\bar M^*=\bar M(\omega^*;\theta)$ then gives $\partial\bar M^*/\partial\theta=\partial\bar M(\omega^*;\theta)/\partial\theta$ at the worst-case argmax (the partial derivative through $\omega^*$ vanishes by the first-order condition defining $\omega^*$). Since $\partial \Phi^M / \partial M\big|_{\bar M^*, \omega^*} > 0$ at the lower
crossing, the sign of $\partial \bar M^* / \partial \theta$ is the
opposite of the sign of $\partial \Phi^M / \partial \theta$.

\textit{Sign of the numerator by parameter.}
\begin{itemize}
    \item $\theta = \rho$: faster decay raises $V^v(M, B; \omega)$ (faster
    recovery from inherited grievance under Dove's $d_B = 0$) and lowers
    $V^v(M, A; \omega)$ (Hawk's accumulated $M$ has a shorter half-life, eroding
    the security-premium dividend) for every $\omega$, so
    $\partial \Phi^M / \partial \rho < 0$, giving
    $\partial \bar M^* / \partial \rho > 0$.
    \item $\theta = S_A / S_B$: larger Hawk advantage raises $\Delta\Pi$
    on the increasing branch of the inverted-U for every $\omega$, raising $V^v(M, A; \omega)$. The
    Dove cannot exploit the larger ratio because $d_B^\star = 0$ keeps
    the Dove off the increasing branch. Hence
    $\partial \Phi^M / \partial(S_A/S_B) > 0$, giving
    $\partial \bar M^* / \partial(S_A/S_B) < 0$.
    \item $\theta = \lambda$: larger weight on security raises the
    coefficient on $\Delta\Pi$ in $U^A$ relative to $U^B$, scaling up the
    Hawk's relative within-period payoff in the relevant range at every $\omega$.
    Analogous to $S_A / S_B$.
    \item $\theta = \Delta u$: larger Dove economic advantage raises
    $u(\bar g_B) - u(\bar g_A)$, which is the dominant component of
    $V^v(M, B; \omega) - V^v(M, A; \omega)$ at low $M$ uniformly in $\omega$, so
    $\partial \Phi^M / \partial \Delta u < 0$, giving
    $\partial \bar M^* / \partial \Delta u > 0$.
\end{itemize}
\end{proof}

%===================================================================================
% APPENDIX C: Supplementary Materials (input from existing file)
%===================================================================================

\input{supplementary_readme}

\end{document}
